---
title: "Dimensionality Reduction LDA, KNN PDA 04"
author: "Anthony Clark"
date: "2024-12-03"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
## R Markdown
library(MASS)
library(factoextra)
library(ggplot2)
library(e1071) 
library(class)
library(lattice)
library(caret)
#import data
gene <- read.csv("K8.csv")
```


Data is very large

Variable "Inactive" corresponds to p53 response variable

Categorical variable with two outcomes "inactive" vs "active

reduce data

First subset is 100 features, the next two subsets are 500 and 2000 features


```{r}
gene_red <- gene[1:5000,5310:5409]
matches <- grepl("\\?", gene_red$X0.009.28)
gene_hits <- gene_red[matches,]
gene_noquest <- gene_red[!matches,]
```


DATA CLEANING

Change "char" variables to numeric data type

as numeric lines have been omitted because they are repetitive

```{r}
gene_noquest[,1] <- as.numeric(gene_noquest[,1])
gene_noquest[,2] <- as.numeric(gene_noquest[,2])
gene_noquest[,3] <- as.numeric(gene_noquest[,3])
gene_noquest[,4] <- as.numeric(gene_noquest[,4])
gene_noquest[,5] <- as.numeric(gene_noquest[,5])
gene_noquest[,6] <- as.numeric(gene_noquest[,6])
gene_noquest[,7] <- as.numeric(gene_noquest[,7])
gene_noquest[,8] <- as.numeric(gene_noquest[,8])
gene_noquest[,9] <- as.numeric(gene_noquest[,9])
gene_noquest[,10] <- as.numeric(gene_noquest[,10])
gene_noquest[,11] <- as.numeric(gene_noquest[,11])
gene_noquest[,12] <- as.numeric(gene_noquest[,12])
gene_noquest[,13] <- as.numeric(gene_noquest[,13])
gene_noquest[,14] <- as.numeric(gene_noquest[,14])
gene_noquest[,15] <- as.numeric(gene_noquest[,15])
gene_noquest[,16] <- as.numeric(gene_noquest[,16])
gene_noquest[,17] <- as.numeric(gene_noquest[,17])
gene_noquest[,18] <- as.numeric(gene_noquest[,18])
gene_noquest[,19] <- as.numeric(gene_noquest[,19])
gene_noquest[,20] <- as.numeric(gene_noquest[,20])
gene_noquest[,21] <- as.numeric(gene_noquest[,21])
gene_noquest[,22] <- as.numeric(gene_noquest[,22])
gene_noquest[,23] <- as.numeric(gene_noquest[,23])
gene_noquest[,24] <- as.numeric(gene_noquest[,24])
gene_noquest[,25] <- as.numeric(gene_noquest[,25])
gene_noquest[,26] <- as.numeric(gene_noquest[,26])
gene_noquest[,27] <- as.numeric(gene_noquest[,27])
gene_noquest[,28] <- as.numeric(gene_noquest[,28])
gene_noquest[,29] <- as.numeric(gene_noquest[,29])
gene_noquest[,30] <- as.numeric(gene_noquest[,30])
gene_noquest[,31] <- as.numeric(gene_noquest[,31])
gene_noquest[,32] <- as.numeric(gene_noquest[,32])
gene_noquest[,33] <- as.numeric(gene_noquest[,33])
gene_noquest[,34] <- as.numeric(gene_noquest[,34])
gene_noquest[,35] <- as.numeric(gene_noquest[,35])
gene_noquest[,36] <- as.numeric(gene_noquest[,36])
gene_noquest[,37] <- as.numeric(gene_noquest[,37])
gene_noquest[,38] <- as.numeric(gene_noquest[,38])
gene_noquest[,39] <- as.numeric(gene_noquest[,39])
gene_noquest[,40] <- as.numeric(gene_noquest[,40])
gene_noquest[,41] <- as.numeric(gene_noquest[,41])
gene_noquest[,42] <- as.numeric(gene_noquest[,42])
gene_noquest[,43] <- as.numeric(gene_noquest[,43])
gene_noquest[,44] <- as.numeric(gene_noquest[,44])
gene_noquest[,45] <- as.numeric(gene_noquest[,45])
gene_noquest[,46] <- as.numeric(gene_noquest[,46])
gene_noquest[,47] <- as.numeric(gene_noquest[,47])
gene_noquest[,48] <- as.numeric(gene_noquest[,48])
gene_noquest[,49] <- as.numeric(gene_noquest[,49])
gene_noquest[,50] <- as.numeric(gene_noquest[,50])
gene_noquest[,51] <- as.numeric(gene_noquest[,51])
gene_noquest[,52] <- as.numeric(gene_noquest[,52])
gene_noquest[,53] <- as.numeric(gene_noquest[,53])
gene_noquest[,54] <- as.numeric(gene_noquest[,54])
gene_noquest[,55] <- as.numeric(gene_noquest[,55])
gene_noquest[,56] <- as.numeric(gene_noquest[,56])
gene_noquest[,57] <- as.numeric(gene_noquest[,57])
gene_noquest[,58] <- as.numeric(gene_noquest[,58])
gene_noquest[,59] <- as.numeric(gene_noquest[,59])
gene_noquest[,60] <- as.numeric(gene_noquest[,60])
gene_noquest[,61] <- as.numeric(gene_noquest[,61])
gene_noquest[,62] <- as.numeric(gene_noquest[,62])
gene_noquest[,63] <- as.numeric(gene_noquest[,63])
gene_noquest[,64] <- as.numeric(gene_noquest[,64])
gene_noquest[,65] <- as.numeric(gene_noquest[,65])
gene_noquest[,66] <- as.numeric(gene_noquest[,66])
gene_noquest[,67] <- as.numeric(gene_noquest[,67])
gene_noquest[,68] <- as.numeric(gene_noquest[,68])
gene_noquest[,69] <- as.numeric(gene_noquest[,69])
gene_noquest[,70] <- as.numeric(gene_noquest[,70])
gene_noquest[,71] <- as.numeric(gene_noquest[,71])
gene_noquest[,72] <- as.numeric(gene_noquest[,72])
gene_noquest[,73] <- as.numeric(gene_noquest[,73])
gene_noquest[,74] <- as.numeric(gene_noquest[,74])
gene_noquest[,75] <- as.numeric(gene_noquest[,75])
gene_noquest[,76] <- as.numeric(gene_noquest[,76])
gene_noquest[,77] <- as.numeric(gene_noquest[,77])
gene_noquest[,78] <- as.numeric(gene_noquest[,78])
gene_noquest[,79] <- as.numeric(gene_noquest[,79])
gene_noquest[,80] <- as.numeric(gene_noquest[,80])
gene_noquest[,81] <- as.numeric(gene_noquest[,81])
gene_noquest[,82] <- as.numeric(gene_noquest[,82])
gene_noquest[,83] <- as.numeric(gene_noquest[,83])
gene_noquest[,84] <- as.numeric(gene_noquest[,84])
gene_noquest[,85] <- as.numeric(gene_noquest[,85])
gene_noquest[,86] <- as.numeric(gene_noquest[,86])
gene_noquest[,87] <- as.numeric(gene_noquest[,87])
gene_noquest[,88] <- as.numeric(gene_noquest[,88])
gene_noquest[,89] <- as.numeric(gene_noquest[,89])
gene_noquest[,90] <- as.numeric(gene_noquest[,90])
gene_noquest[,91] <- as.numeric(gene_noquest[,91])
gene_noquest[,92] <- as.numeric(gene_noquest[,92])
gene_noquest[,93] <- as.numeric(gene_noquest[,93])
gene_noquest[,94] <- as.numeric(gene_noquest[,94])
gene_noquest[,95] <- as.numeric(gene_noquest[,95])
gene_noquest[,96] <- as.numeric(gene_noquest[,96])
gene_noquest[,97] <- as.numeric(gene_noquest[,97])
gene_noquest[,98] <- as.numeric(gene_noquest[,98])
gene_noquest[,99] <- as.numeric(gene_noquest[,99])
gene_noquest$inactive <- as.factor(gene_noquest$inactive)

#Remove Na values (missing values)
gene_noNa <- na.omit(gene_noquest)
```

VISUALIZE COLLINEARITY

```{r}

cor(gene_noquest[,53:55])
pairs(gene_noquest[,50:55])
```

TRAINING/TESTING SPLIT (100 features)

```{r}

#split up into testing and training

gene_noquest <- na.omit(gene_noquest)

gene_t <- sample(dim(gene_noquest)[1],4000)
gene_train <- gene_noquest[gene_t,]
gene_test <- gene_noquest[-gene_t,]
```

LINEAR DISCRIMINANT ANALYSIS (100 Features)

```{r}

#z is lda model
#use training data

z <- lda(gene_train$inactive~., data = gene_train)

#predict using testing set


p <- predict(z, gene_test)

#Check that p worked
#Should return three variables
#Class, posterior and x
names(p)

#Check head of p

head(p$class)


#Compute lda error by comparing predictions and test data
lda_error <- mean(p$class == gene_test$inactive)
lda_error
#Gave us really good accuracy, approximately 98%

```

K-NEAREST NEIGHBOR (100 Features)


```{r}

#Create KNN model

#Change inactive from factor to numeric

gene_train$inactive <- as.numeric(gene_train$inactive)
gene_test$inactive <- as.numeric(gene_test$inactive)

test_pred <- knn(
  train = gene_train, 
  test = gene_test,
  cl = gene_train$inactive, 
  k=10
)

#Hold actual values in "actual"
actual <- gene_test$inactive

#Generate confusion matrix to test accuracy of KNN

confusion_matrix_KNN <- table(actual,test_pred)
confusion_matrix_KNN

accuracy <- sum(diag(confusion_matrix_KNN))/length(actual)
sprintf("Accuracy: %.2f%%", accuracy*100)

#The accuracy is actually surprisingly good, 
#but not sure how this would fair with more features? 
```

PRINCIPAL COMPONENT ANALYSIS (100 Features)

```{r}
#Now let's look at principal component analysis

pca <- prcomp(gene_noquest[,-100], scale = TRUE)

#Let's draw a 2D plot using the top 2 
#X contains the princpal components in the model

plot(pca$x[,1], pca$x[,2])

#Look at 2nd PC and 3rd PC

plot(pca$x[,2], pca$x[,3])

#Plot PCA
plot(pca)
plot(pca$x)

```

SCREE PLOT 
#Use standard deviation to create scree plot

```{r}

#Evaluate pca with scree plot 
#variance vs principal component

pca_var <- pca$sdev^2
pca_var_per <- round(pca_var/sum(pca_var)*100, 1)
barplot(pca_var_per, main = "Scree Plot: 100 Feature Dataset", xlab = "Principal Component", ylab = "Percent Variation")

#Make ggplot

pca_data <- data.frame(Sample=rownames(pca$x), X=pca$x[,1], Y = pca$x[,2])
```

TOP 10 GENES (100 Features)

```{r}
#Get loading score based on rotation values of principal component #1

loading_score <- pca$rotation[,1]

#Absolute value to ensure both negative and positive values are included

gene_score <- abs(loading_score)

#Sort genes by absolute value 

gene_score_ranked <- sort(gene_score, decreasing = TRUE)

#Find top 10 genes in principal component #1

top_10_genes <- names(gene_score_ranked[1:10])

#Display top 10 genes

top_10_genes
```

NEW GENE DATA WITH TOP 10 GENES

```{r}

pca$rotation[top_10_genes, 1]

#So according to our principal component analysis
#The top 10 genes for our model are

# "X.0.007.28" "X0.037.12"  "X0.016.30"  "X0.046.8"   "X.0.087.6"  "X0.058.2"  
# "X0.035.19"  "X.0.013.23" "X0.046.7"   "X0.009.28" 

#Let's make a data subset with just the top 10 genes

new_gene = subset(gene_noquest, select = c(X.0.007.28, X0.037.12, X0.016.30, X0.046.8,
                                        X.0.087.6, X0.058.2, X0.035.19, X.0.013.23,
                                        X0.046.7, X0.009.28, inactive))
#Split into train and test data again
#Use gene_pca dataset

gene_pca_t <- sample(dim(new_gene)[1],4000)
train_pca <- new_gene[gene_pca_t,]
test_pca <- new_gene[-gene_pca_t,]
```

LDA and KNN model Post-PCA (100 Features)

```{r}
#Now try lda model

w100 <- lda(train_pca$inactive~., data = train_pca)

#Use the predict function

pr <- predict(w100, test_pca)

lda_error <- mean(pr$class == test_pca$inactive)
lda_error

train_pca$inactive <- as.numeric(train_pca$inactive)
test_pca$inactive <- as.numeric(test_pca$inactive)

test_pred2 <- knn(
  train = train_pca, 
  test = test_pca,
  cl = train_pca$inactive, 
  k=10
)

#Confusion matrix for KNN model
#After pca

actual9 <- test_pca$inactive

confusion_matrix_KNN9 <- table(actual9,test_pred2)
confusion_matrix_KNN9



#The METHOD was improved using PCA
#Could we apply PCA with the top 500 features?
```

REPEAT PROCESS WITH  500 Feature Dataset

DATA CLEANING

```{r}
#Create gene500, dataset with 500 features

gene_500 <- gene[1:10000, 4909:5409]

#Remove missing values
matches1 <- grepl("\\?", gene_500$X0.009.28)
gene_hits_500 <- gene_500[matches1,]
gene_noquest_500 <- gene_500[!matches1,]

#Remove Na

gene500.cleaned <- na.omit(gene_noquest_500)

#Every variable needs to be reformatted as numeric
#Except inactive, which needs to be reformatted as a factor
gene500.cleaned$inactive <- as.factor(gene500.cleaned$inactive)
```

As Numeric List

```{r}
gene500.cleaned[, 1 ] <- as.numeric(gene500.cleaned[, 1 ])
gene500.cleaned[, 2 ] <- as.numeric(gene500.cleaned[, 2 ])
gene500.cleaned[, 3 ] <- as.numeric(gene500.cleaned[, 3 ])
gene500.cleaned[, 4 ] <- as.numeric(gene500.cleaned[, 4 ])
gene500.cleaned[, 5 ] <- as.numeric(gene500.cleaned[, 5 ])
gene500.cleaned[, 6 ] <- as.numeric(gene500.cleaned[, 6 ])
gene500.cleaned[, 7 ] <- as.numeric(gene500.cleaned[, 7 ])
gene500.cleaned[, 8 ] <- as.numeric(gene500.cleaned[, 8 ])
gene500.cleaned[, 9 ] <- as.numeric(gene500.cleaned[, 9 ])
gene500.cleaned[, 10 ] <- as.numeric(gene500.cleaned[, 10 ])
gene500.cleaned[, 11 ] <- as.numeric(gene500.cleaned[, 11 ])
gene500.cleaned[, 12 ] <- as.numeric(gene500.cleaned[, 12 ])
gene500.cleaned[, 13 ] <- as.numeric(gene500.cleaned[, 13 ])
gene500.cleaned[, 14 ] <- as.numeric(gene500.cleaned[, 14 ])
gene500.cleaned[, 15 ] <- as.numeric(gene500.cleaned[, 15 ])
gene500.cleaned[, 16 ] <- as.numeric(gene500.cleaned[, 16 ])
gene500.cleaned[, 17 ] <- as.numeric(gene500.cleaned[, 17 ])
gene500.cleaned[, 18 ] <- as.numeric(gene500.cleaned[, 18 ])
gene500.cleaned[, 19 ] <- as.numeric(gene500.cleaned[, 19 ])
gene500.cleaned[, 20 ] <- as.numeric(gene500.cleaned[, 20 ])
gene500.cleaned[, 21 ] <- as.numeric(gene500.cleaned[, 21 ])
gene500.cleaned[, 22 ] <- as.numeric(gene500.cleaned[, 22 ])
gene500.cleaned[, 23 ] <- as.numeric(gene500.cleaned[, 23 ])
gene500.cleaned[, 24 ] <- as.numeric(gene500.cleaned[, 24 ])
gene500.cleaned[, 25 ] <- as.numeric(gene500.cleaned[, 25 ])
gene500.cleaned[, 26 ] <- as.numeric(gene500.cleaned[, 26 ])
gene500.cleaned[, 27 ] <- as.numeric(gene500.cleaned[, 27 ])
gene500.cleaned[, 28 ] <- as.numeric(gene500.cleaned[, 28 ])
gene500.cleaned[, 29 ] <- as.numeric(gene500.cleaned[, 29 ])
gene500.cleaned[, 30 ] <- as.numeric(gene500.cleaned[, 30 ])
gene500.cleaned[, 31 ] <- as.numeric(gene500.cleaned[, 31 ])
gene500.cleaned[, 32 ] <- as.numeric(gene500.cleaned[, 32 ])
gene500.cleaned[, 33 ] <- as.numeric(gene500.cleaned[, 33 ])
gene500.cleaned[, 34 ] <- as.numeric(gene500.cleaned[, 34 ])
gene500.cleaned[, 35 ] <- as.numeric(gene500.cleaned[, 35 ])
gene500.cleaned[, 36 ] <- as.numeric(gene500.cleaned[, 36 ])
gene500.cleaned[, 37 ] <- as.numeric(gene500.cleaned[, 37 ])
gene500.cleaned[, 38 ] <- as.numeric(gene500.cleaned[, 38 ])
gene500.cleaned[, 39 ] <- as.numeric(gene500.cleaned[, 39 ])
gene500.cleaned[, 40 ] <- as.numeric(gene500.cleaned[, 40 ])
gene500.cleaned[, 41 ] <- as.numeric(gene500.cleaned[, 41 ])
gene500.cleaned[, 42 ] <- as.numeric(gene500.cleaned[, 42 ])
gene500.cleaned[, 43 ] <- as.numeric(gene500.cleaned[, 43 ])
gene500.cleaned[, 44 ] <- as.numeric(gene500.cleaned[, 44 ])
gene500.cleaned[, 45 ] <- as.numeric(gene500.cleaned[, 45 ])
gene500.cleaned[, 46 ] <- as.numeric(gene500.cleaned[, 46 ])
gene500.cleaned[, 47 ] <- as.numeric(gene500.cleaned[, 47 ])
gene500.cleaned[, 48 ] <- as.numeric(gene500.cleaned[, 48 ])
gene500.cleaned[, 49 ] <- as.numeric(gene500.cleaned[, 49 ])
gene500.cleaned[, 50 ] <- as.numeric(gene500.cleaned[, 50 ])
gene500.cleaned[, 51 ] <- as.numeric(gene500.cleaned[, 51 ])
gene500.cleaned[, 52 ] <- as.numeric(gene500.cleaned[, 52 ])
gene500.cleaned[, 53 ] <- as.numeric(gene500.cleaned[, 53 ])
gene500.cleaned[, 54 ] <- as.numeric(gene500.cleaned[, 54 ])
gene500.cleaned[, 55 ] <- as.numeric(gene500.cleaned[, 55 ])
gene500.cleaned[, 56 ] <- as.numeric(gene500.cleaned[, 56 ])
gene500.cleaned[, 57 ] <- as.numeric(gene500.cleaned[, 57 ])
gene500.cleaned[, 58 ] <- as.numeric(gene500.cleaned[, 58 ])
gene500.cleaned[, 59 ] <- as.numeric(gene500.cleaned[, 59 ])
gene500.cleaned[, 60 ] <- as.numeric(gene500.cleaned[, 60 ])
gene500.cleaned[, 61 ] <- as.numeric(gene500.cleaned[, 61 ])
gene500.cleaned[, 62 ] <- as.numeric(gene500.cleaned[, 62 ])
gene500.cleaned[, 63 ] <- as.numeric(gene500.cleaned[, 63 ])
gene500.cleaned[, 64 ] <- as.numeric(gene500.cleaned[, 64 ])
gene500.cleaned[, 65 ] <- as.numeric(gene500.cleaned[, 65 ])
gene500.cleaned[, 66 ] <- as.numeric(gene500.cleaned[, 66 ])
gene500.cleaned[, 67 ] <- as.numeric(gene500.cleaned[, 67 ])
gene500.cleaned[, 68 ] <- as.numeric(gene500.cleaned[, 68 ])
gene500.cleaned[, 69 ] <- as.numeric(gene500.cleaned[, 69 ])
gene500.cleaned[, 70 ] <- as.numeric(gene500.cleaned[, 70 ])
gene500.cleaned[, 71 ] <- as.numeric(gene500.cleaned[, 71 ])
gene500.cleaned[, 72 ] <- as.numeric(gene500.cleaned[, 72 ])
gene500.cleaned[, 73 ] <- as.numeric(gene500.cleaned[, 73 ])
gene500.cleaned[, 74 ] <- as.numeric(gene500.cleaned[, 74 ])
gene500.cleaned[, 75 ] <- as.numeric(gene500.cleaned[, 75 ])
gene500.cleaned[, 76 ] <- as.numeric(gene500.cleaned[, 76 ])
gene500.cleaned[, 77 ] <- as.numeric(gene500.cleaned[, 77 ])
gene500.cleaned[, 78 ] <- as.numeric(gene500.cleaned[, 78 ])
gene500.cleaned[, 79 ] <- as.numeric(gene500.cleaned[, 79 ])
gene500.cleaned[, 80 ] <- as.numeric(gene500.cleaned[, 80 ])
gene500.cleaned[, 81 ] <- as.numeric(gene500.cleaned[, 81 ])
gene500.cleaned[, 82 ] <- as.numeric(gene500.cleaned[, 82 ])
gene500.cleaned[, 83 ] <- as.numeric(gene500.cleaned[, 83 ])
gene500.cleaned[, 84 ] <- as.numeric(gene500.cleaned[, 84 ])
gene500.cleaned[, 85 ] <- as.numeric(gene500.cleaned[, 85 ])
gene500.cleaned[, 86 ] <- as.numeric(gene500.cleaned[, 86 ])
gene500.cleaned[, 87 ] <- as.numeric(gene500.cleaned[, 87 ])
gene500.cleaned[, 88 ] <- as.numeric(gene500.cleaned[, 88 ])
gene500.cleaned[, 89 ] <- as.numeric(gene500.cleaned[, 89 ])
gene500.cleaned[, 90 ] <- as.numeric(gene500.cleaned[, 90 ])
gene500.cleaned[, 91 ] <- as.numeric(gene500.cleaned[, 91 ])
gene500.cleaned[, 92 ] <- as.numeric(gene500.cleaned[, 92 ])
gene500.cleaned[, 93 ] <- as.numeric(gene500.cleaned[, 93 ])
gene500.cleaned[, 94 ] <- as.numeric(gene500.cleaned[, 94 ])
gene500.cleaned[, 95 ] <- as.numeric(gene500.cleaned[, 95 ])
gene500.cleaned[, 96 ] <- as.numeric(gene500.cleaned[, 96 ])
gene500.cleaned[, 97 ] <- as.numeric(gene500.cleaned[, 97 ])
gene500.cleaned[, 98 ] <- as.numeric(gene500.cleaned[, 98 ])
gene500.cleaned[, 99 ] <- as.numeric(gene500.cleaned[, 99 ])
gene500.cleaned[, 100 ] <- as.numeric(gene500.cleaned[, 100 ])
gene500.cleaned[, 101 ] <- as.numeric(gene500.cleaned[, 101 ])
gene500.cleaned[, 102 ] <- as.numeric(gene500.cleaned[, 102 ])
gene500.cleaned[, 103 ] <- as.numeric(gene500.cleaned[, 103 ])
gene500.cleaned[, 104 ] <- as.numeric(gene500.cleaned[, 104 ])
gene500.cleaned[, 105 ] <- as.numeric(gene500.cleaned[, 105 ])
gene500.cleaned[, 106 ] <- as.numeric(gene500.cleaned[, 106 ])
gene500.cleaned[, 107 ] <- as.numeric(gene500.cleaned[, 107 ])
gene500.cleaned[, 108 ] <- as.numeric(gene500.cleaned[, 108 ])
gene500.cleaned[, 109 ] <- as.numeric(gene500.cleaned[, 109 ])
gene500.cleaned[, 110 ] <- as.numeric(gene500.cleaned[, 110 ])
gene500.cleaned[, 111 ] <- as.numeric(gene500.cleaned[, 111 ])
gene500.cleaned[, 112 ] <- as.numeric(gene500.cleaned[, 112 ])
gene500.cleaned[, 113 ] <- as.numeric(gene500.cleaned[, 113 ])
gene500.cleaned[, 114 ] <- as.numeric(gene500.cleaned[, 114 ])
gene500.cleaned[, 115 ] <- as.numeric(gene500.cleaned[, 115 ])
gene500.cleaned[, 116 ] <- as.numeric(gene500.cleaned[, 116 ])
gene500.cleaned[, 117 ] <- as.numeric(gene500.cleaned[, 117 ])
gene500.cleaned[, 118 ] <- as.numeric(gene500.cleaned[, 118 ])
gene500.cleaned[, 119 ] <- as.numeric(gene500.cleaned[, 119 ])
gene500.cleaned[, 120 ] <- as.numeric(gene500.cleaned[, 120 ])
gene500.cleaned[, 121 ] <- as.numeric(gene500.cleaned[, 121 ])
gene500.cleaned[, 122 ] <- as.numeric(gene500.cleaned[, 122 ])
gene500.cleaned[, 123 ] <- as.numeric(gene500.cleaned[, 123 ])
gene500.cleaned[, 124 ] <- as.numeric(gene500.cleaned[, 124 ])
gene500.cleaned[, 125 ] <- as.numeric(gene500.cleaned[, 125 ])
gene500.cleaned[, 126 ] <- as.numeric(gene500.cleaned[, 126 ])
gene500.cleaned[, 127 ] <- as.numeric(gene500.cleaned[, 127 ])
gene500.cleaned[, 128 ] <- as.numeric(gene500.cleaned[, 128 ])
gene500.cleaned[, 129 ] <- as.numeric(gene500.cleaned[, 129 ])
gene500.cleaned[, 130 ] <- as.numeric(gene500.cleaned[, 130 ])
gene500.cleaned[, 131 ] <- as.numeric(gene500.cleaned[, 131 ])
gene500.cleaned[, 132 ] <- as.numeric(gene500.cleaned[, 132 ])
gene500.cleaned[, 133 ] <- as.numeric(gene500.cleaned[, 133 ])
gene500.cleaned[, 134 ] <- as.numeric(gene500.cleaned[, 134 ])
gene500.cleaned[, 135 ] <- as.numeric(gene500.cleaned[, 135 ])
gene500.cleaned[, 136 ] <- as.numeric(gene500.cleaned[, 136 ])
gene500.cleaned[, 137 ] <- as.numeric(gene500.cleaned[, 137 ])
gene500.cleaned[, 138 ] <- as.numeric(gene500.cleaned[, 138 ])
gene500.cleaned[, 139 ] <- as.numeric(gene500.cleaned[, 139 ])
gene500.cleaned[, 140 ] <- as.numeric(gene500.cleaned[, 140 ])
gene500.cleaned[, 141 ] <- as.numeric(gene500.cleaned[, 141 ])
gene500.cleaned[, 142 ] <- as.numeric(gene500.cleaned[, 142 ])
gene500.cleaned[, 143 ] <- as.numeric(gene500.cleaned[, 143 ])
gene500.cleaned[, 144 ] <- as.numeric(gene500.cleaned[, 144 ])
gene500.cleaned[, 145 ] <- as.numeric(gene500.cleaned[, 145 ])
gene500.cleaned[, 146 ] <- as.numeric(gene500.cleaned[, 146 ])
gene500.cleaned[, 147 ] <- as.numeric(gene500.cleaned[, 147 ])
gene500.cleaned[, 148 ] <- as.numeric(gene500.cleaned[, 148 ])
gene500.cleaned[, 149 ] <- as.numeric(gene500.cleaned[, 149 ])
gene500.cleaned[, 150 ] <- as.numeric(gene500.cleaned[, 150 ])
gene500.cleaned[, 151 ] <- as.numeric(gene500.cleaned[, 151 ])
gene500.cleaned[, 152 ] <- as.numeric(gene500.cleaned[, 152 ])
gene500.cleaned[, 153 ] <- as.numeric(gene500.cleaned[, 153 ])
gene500.cleaned[, 154 ] <- as.numeric(gene500.cleaned[, 154 ])
gene500.cleaned[, 155 ] <- as.numeric(gene500.cleaned[, 155 ])
gene500.cleaned[, 156 ] <- as.numeric(gene500.cleaned[, 156 ])
gene500.cleaned[, 157 ] <- as.numeric(gene500.cleaned[, 157 ])
gene500.cleaned[, 158 ] <- as.numeric(gene500.cleaned[, 158 ])
gene500.cleaned[, 159 ] <- as.numeric(gene500.cleaned[, 159 ])
gene500.cleaned[, 160 ] <- as.numeric(gene500.cleaned[, 160 ])
gene500.cleaned[, 161 ] <- as.numeric(gene500.cleaned[, 161 ])
gene500.cleaned[, 162 ] <- as.numeric(gene500.cleaned[, 162 ])
gene500.cleaned[, 163 ] <- as.numeric(gene500.cleaned[, 163 ])
gene500.cleaned[, 164 ] <- as.numeric(gene500.cleaned[, 164 ])
gene500.cleaned[, 165 ] <- as.numeric(gene500.cleaned[, 165 ])
gene500.cleaned[, 166 ] <- as.numeric(gene500.cleaned[, 166 ])
gene500.cleaned[, 167 ] <- as.numeric(gene500.cleaned[, 167 ])
gene500.cleaned[, 168 ] <- as.numeric(gene500.cleaned[, 168 ])
gene500.cleaned[, 169 ] <- as.numeric(gene500.cleaned[, 169 ])
gene500.cleaned[, 170 ] <- as.numeric(gene500.cleaned[, 170 ])
gene500.cleaned[, 171 ] <- as.numeric(gene500.cleaned[, 171 ])
gene500.cleaned[, 172 ] <- as.numeric(gene500.cleaned[, 172 ])
gene500.cleaned[, 173 ] <- as.numeric(gene500.cleaned[, 173 ])
gene500.cleaned[, 174 ] <- as.numeric(gene500.cleaned[, 174 ])
gene500.cleaned[, 175 ] <- as.numeric(gene500.cleaned[, 175 ])
gene500.cleaned[, 176 ] <- as.numeric(gene500.cleaned[, 176 ])
gene500.cleaned[, 177 ] <- as.numeric(gene500.cleaned[, 177 ])
gene500.cleaned[, 178 ] <- as.numeric(gene500.cleaned[, 178 ])
gene500.cleaned[, 179 ] <- as.numeric(gene500.cleaned[, 179 ])
gene500.cleaned[, 180 ] <- as.numeric(gene500.cleaned[, 180 ])
gene500.cleaned[, 181 ] <- as.numeric(gene500.cleaned[, 181 ])
gene500.cleaned[, 182 ] <- as.numeric(gene500.cleaned[, 182 ])
gene500.cleaned[, 183 ] <- as.numeric(gene500.cleaned[, 183 ])
gene500.cleaned[, 184 ] <- as.numeric(gene500.cleaned[, 184 ])
gene500.cleaned[, 185 ] <- as.numeric(gene500.cleaned[, 185 ])
gene500.cleaned[, 186 ] <- as.numeric(gene500.cleaned[, 186 ])
gene500.cleaned[, 187 ] <- as.numeric(gene500.cleaned[, 187 ])
gene500.cleaned[, 188 ] <- as.numeric(gene500.cleaned[, 188 ])
gene500.cleaned[, 189 ] <- as.numeric(gene500.cleaned[, 189 ])
gene500.cleaned[, 190 ] <- as.numeric(gene500.cleaned[, 190 ])
gene500.cleaned[, 191 ] <- as.numeric(gene500.cleaned[, 191 ])
gene500.cleaned[, 192 ] <- as.numeric(gene500.cleaned[, 192 ])
gene500.cleaned[, 193 ] <- as.numeric(gene500.cleaned[, 193 ])
gene500.cleaned[, 194 ] <- as.numeric(gene500.cleaned[, 194 ])
gene500.cleaned[, 195 ] <- as.numeric(gene500.cleaned[, 195 ])
gene500.cleaned[, 196 ] <- as.numeric(gene500.cleaned[, 196 ])
gene500.cleaned[, 197 ] <- as.numeric(gene500.cleaned[, 197 ])
gene500.cleaned[, 198 ] <- as.numeric(gene500.cleaned[, 198 ])
gene500.cleaned[, 199 ] <- as.numeric(gene500.cleaned[, 199 ])
gene500.cleaned[, 200 ] <- as.numeric(gene500.cleaned[, 200 ])
gene500.cleaned[, 201 ] <- as.numeric(gene500.cleaned[, 201 ])
gene500.cleaned[, 202 ] <- as.numeric(gene500.cleaned[, 202 ])
gene500.cleaned[, 203 ] <- as.numeric(gene500.cleaned[, 203 ])
gene500.cleaned[, 204 ] <- as.numeric(gene500.cleaned[, 204 ])
gene500.cleaned[, 205 ] <- as.numeric(gene500.cleaned[, 205 ])
gene500.cleaned[, 206 ] <- as.numeric(gene500.cleaned[, 206 ])
gene500.cleaned[, 207 ] <- as.numeric(gene500.cleaned[, 207 ])
gene500.cleaned[, 208 ] <- as.numeric(gene500.cleaned[, 208 ])
gene500.cleaned[, 209 ] <- as.numeric(gene500.cleaned[, 209 ])
gene500.cleaned[, 210 ] <- as.numeric(gene500.cleaned[, 210 ])
gene500.cleaned[, 211 ] <- as.numeric(gene500.cleaned[, 211 ])
gene500.cleaned[, 212 ] <- as.numeric(gene500.cleaned[, 212 ])
gene500.cleaned[, 213 ] <- as.numeric(gene500.cleaned[, 213 ])
gene500.cleaned[, 214 ] <- as.numeric(gene500.cleaned[, 214 ])
gene500.cleaned[, 215 ] <- as.numeric(gene500.cleaned[, 215 ])
gene500.cleaned[, 216 ] <- as.numeric(gene500.cleaned[, 216 ])
gene500.cleaned[, 217 ] <- as.numeric(gene500.cleaned[, 217 ])
gene500.cleaned[, 218 ] <- as.numeric(gene500.cleaned[, 218 ])
gene500.cleaned[, 219 ] <- as.numeric(gene500.cleaned[, 219 ])
gene500.cleaned[, 220 ] <- as.numeric(gene500.cleaned[, 220 ])
gene500.cleaned[, 221 ] <- as.numeric(gene500.cleaned[, 221 ])
gene500.cleaned[, 222 ] <- as.numeric(gene500.cleaned[, 222 ])
gene500.cleaned[, 223 ] <- as.numeric(gene500.cleaned[, 223 ])
gene500.cleaned[, 224 ] <- as.numeric(gene500.cleaned[, 224 ])
gene500.cleaned[, 225 ] <- as.numeric(gene500.cleaned[, 225 ])
gene500.cleaned[, 226 ] <- as.numeric(gene500.cleaned[, 226 ])
gene500.cleaned[, 227 ] <- as.numeric(gene500.cleaned[, 227 ])
gene500.cleaned[, 228 ] <- as.numeric(gene500.cleaned[, 228 ])
gene500.cleaned[, 229 ] <- as.numeric(gene500.cleaned[, 229 ])
gene500.cleaned[, 230 ] <- as.numeric(gene500.cleaned[, 230 ])
gene500.cleaned[, 231 ] <- as.numeric(gene500.cleaned[, 231 ])
gene500.cleaned[, 232 ] <- as.numeric(gene500.cleaned[, 232 ])
gene500.cleaned[, 233 ] <- as.numeric(gene500.cleaned[, 233 ])
gene500.cleaned[, 234 ] <- as.numeric(gene500.cleaned[, 234 ])
gene500.cleaned[, 235 ] <- as.numeric(gene500.cleaned[, 235 ])
gene500.cleaned[, 236 ] <- as.numeric(gene500.cleaned[, 236 ])
gene500.cleaned[, 237 ] <- as.numeric(gene500.cleaned[, 237 ])
gene500.cleaned[, 238 ] <- as.numeric(gene500.cleaned[, 238 ])
gene500.cleaned[, 239 ] <- as.numeric(gene500.cleaned[, 239 ])
gene500.cleaned[, 240 ] <- as.numeric(gene500.cleaned[, 240 ])
gene500.cleaned[, 241 ] <- as.numeric(gene500.cleaned[, 241 ])
gene500.cleaned[, 242 ] <- as.numeric(gene500.cleaned[, 242 ])
gene500.cleaned[, 243 ] <- as.numeric(gene500.cleaned[, 243 ])
gene500.cleaned[, 244 ] <- as.numeric(gene500.cleaned[, 244 ])
gene500.cleaned[, 245 ] <- as.numeric(gene500.cleaned[, 245 ])
gene500.cleaned[, 246 ] <- as.numeric(gene500.cleaned[, 246 ])
gene500.cleaned[, 247 ] <- as.numeric(gene500.cleaned[, 247 ])
gene500.cleaned[, 248 ] <- as.numeric(gene500.cleaned[, 248 ])
gene500.cleaned[, 249 ] <- as.numeric(gene500.cleaned[, 249 ])
gene500.cleaned[, 250 ] <- as.numeric(gene500.cleaned[, 250 ])
gene500.cleaned[, 251 ] <- as.numeric(gene500.cleaned[, 251 ])
gene500.cleaned[, 252 ] <- as.numeric(gene500.cleaned[, 252 ])
gene500.cleaned[, 253 ] <- as.numeric(gene500.cleaned[, 253 ])
gene500.cleaned[, 254 ] <- as.numeric(gene500.cleaned[, 254 ])
gene500.cleaned[, 255 ] <- as.numeric(gene500.cleaned[, 255 ])
gene500.cleaned[, 256 ] <- as.numeric(gene500.cleaned[, 256 ])
gene500.cleaned[, 257 ] <- as.numeric(gene500.cleaned[, 257 ])
gene500.cleaned[, 258 ] <- as.numeric(gene500.cleaned[, 258 ])
gene500.cleaned[, 259 ] <- as.numeric(gene500.cleaned[, 259 ])
gene500.cleaned[, 260 ] <- as.numeric(gene500.cleaned[, 260 ])
gene500.cleaned[, 261 ] <- as.numeric(gene500.cleaned[, 261 ])
gene500.cleaned[, 262 ] <- as.numeric(gene500.cleaned[, 262 ])
gene500.cleaned[, 263 ] <- as.numeric(gene500.cleaned[, 263 ])
gene500.cleaned[, 264 ] <- as.numeric(gene500.cleaned[, 264 ])
gene500.cleaned[, 265 ] <- as.numeric(gene500.cleaned[, 265 ])
gene500.cleaned[, 266 ] <- as.numeric(gene500.cleaned[, 266 ])
gene500.cleaned[, 267 ] <- as.numeric(gene500.cleaned[, 267 ])
gene500.cleaned[, 268 ] <- as.numeric(gene500.cleaned[, 268 ])
gene500.cleaned[, 269 ] <- as.numeric(gene500.cleaned[, 269 ])
gene500.cleaned[, 270 ] <- as.numeric(gene500.cleaned[, 270 ])
gene500.cleaned[, 271 ] <- as.numeric(gene500.cleaned[, 271 ])
gene500.cleaned[, 272 ] <- as.numeric(gene500.cleaned[, 272 ])
gene500.cleaned[, 273 ] <- as.numeric(gene500.cleaned[, 273 ])
gene500.cleaned[, 274 ] <- as.numeric(gene500.cleaned[, 274 ])
gene500.cleaned[, 275 ] <- as.numeric(gene500.cleaned[, 275 ])
gene500.cleaned[, 276 ] <- as.numeric(gene500.cleaned[, 276 ])
gene500.cleaned[, 277 ] <- as.numeric(gene500.cleaned[, 277 ])
gene500.cleaned[, 278 ] <- as.numeric(gene500.cleaned[, 278 ])
gene500.cleaned[, 279 ] <- as.numeric(gene500.cleaned[, 279 ])
gene500.cleaned[, 280 ] <- as.numeric(gene500.cleaned[, 280 ])
gene500.cleaned[, 281 ] <- as.numeric(gene500.cleaned[, 281 ])
gene500.cleaned[, 282 ] <- as.numeric(gene500.cleaned[, 282 ])
gene500.cleaned[, 283 ] <- as.numeric(gene500.cleaned[, 283 ])
gene500.cleaned[, 284 ] <- as.numeric(gene500.cleaned[, 284 ])
gene500.cleaned[, 285 ] <- as.numeric(gene500.cleaned[, 285 ])
gene500.cleaned[, 286 ] <- as.numeric(gene500.cleaned[, 286 ])
gene500.cleaned[, 287 ] <- as.numeric(gene500.cleaned[, 287 ])
gene500.cleaned[, 288 ] <- as.numeric(gene500.cleaned[, 288 ])
gene500.cleaned[, 289 ] <- as.numeric(gene500.cleaned[, 289 ])
gene500.cleaned[, 290 ] <- as.numeric(gene500.cleaned[, 290 ])
gene500.cleaned[, 291 ] <- as.numeric(gene500.cleaned[, 291 ])
gene500.cleaned[, 292 ] <- as.numeric(gene500.cleaned[, 292 ])
gene500.cleaned[, 293 ] <- as.numeric(gene500.cleaned[, 293 ])
gene500.cleaned[, 294 ] <- as.numeric(gene500.cleaned[, 294 ])
gene500.cleaned[, 295 ] <- as.numeric(gene500.cleaned[, 295 ])
gene500.cleaned[, 296 ] <- as.numeric(gene500.cleaned[, 296 ])
gene500.cleaned[, 297 ] <- as.numeric(gene500.cleaned[, 297 ])
gene500.cleaned[, 298 ] <- as.numeric(gene500.cleaned[, 298 ])
gene500.cleaned[, 299 ] <- as.numeric(gene500.cleaned[, 299 ])
gene500.cleaned[, 300 ] <- as.numeric(gene500.cleaned[, 300 ])
gene500.cleaned[, 301 ] <- as.numeric(gene500.cleaned[, 301 ])
gene500.cleaned[, 302 ] <- as.numeric(gene500.cleaned[, 302 ])
gene500.cleaned[, 303 ] <- as.numeric(gene500.cleaned[, 303 ])
gene500.cleaned[, 304 ] <- as.numeric(gene500.cleaned[, 304 ])
gene500.cleaned[, 305 ] <- as.numeric(gene500.cleaned[, 305 ])
gene500.cleaned[, 306 ] <- as.numeric(gene500.cleaned[, 306 ])
gene500.cleaned[, 307 ] <- as.numeric(gene500.cleaned[, 307 ])
gene500.cleaned[, 308 ] <- as.numeric(gene500.cleaned[, 308 ])
gene500.cleaned[, 309 ] <- as.numeric(gene500.cleaned[, 309 ])
gene500.cleaned[, 310 ] <- as.numeric(gene500.cleaned[, 310 ])
gene500.cleaned[, 311 ] <- as.numeric(gene500.cleaned[, 311 ])
gene500.cleaned[, 312 ] <- as.numeric(gene500.cleaned[, 312 ])
gene500.cleaned[, 313 ] <- as.numeric(gene500.cleaned[, 313 ])
gene500.cleaned[, 314 ] <- as.numeric(gene500.cleaned[, 314 ])
gene500.cleaned[, 315 ] <- as.numeric(gene500.cleaned[, 315 ])
gene500.cleaned[, 316 ] <- as.numeric(gene500.cleaned[, 316 ])
gene500.cleaned[, 317 ] <- as.numeric(gene500.cleaned[, 317 ])
gene500.cleaned[, 318 ] <- as.numeric(gene500.cleaned[, 318 ])
gene500.cleaned[, 319 ] <- as.numeric(gene500.cleaned[, 319 ])
gene500.cleaned[, 320 ] <- as.numeric(gene500.cleaned[, 320 ])
gene500.cleaned[, 321 ] <- as.numeric(gene500.cleaned[, 321 ])
gene500.cleaned[, 322 ] <- as.numeric(gene500.cleaned[, 322 ])
gene500.cleaned[, 323 ] <- as.numeric(gene500.cleaned[, 323 ])
gene500.cleaned[, 324 ] <- as.numeric(gene500.cleaned[, 324 ])
gene500.cleaned[, 325 ] <- as.numeric(gene500.cleaned[, 325 ])
gene500.cleaned[, 326 ] <- as.numeric(gene500.cleaned[, 326 ])
gene500.cleaned[, 327 ] <- as.numeric(gene500.cleaned[, 327 ])
gene500.cleaned[, 328 ] <- as.numeric(gene500.cleaned[, 328 ])
gene500.cleaned[, 329 ] <- as.numeric(gene500.cleaned[, 329 ])
gene500.cleaned[, 330 ] <- as.numeric(gene500.cleaned[, 330 ])
gene500.cleaned[, 331 ] <- as.numeric(gene500.cleaned[, 331 ])
gene500.cleaned[, 332 ] <- as.numeric(gene500.cleaned[, 332 ])
gene500.cleaned[, 333 ] <- as.numeric(gene500.cleaned[, 333 ])
gene500.cleaned[, 334 ] <- as.numeric(gene500.cleaned[, 334 ])
gene500.cleaned[, 335 ] <- as.numeric(gene500.cleaned[, 335 ])
gene500.cleaned[, 336 ] <- as.numeric(gene500.cleaned[, 336 ])
gene500.cleaned[, 337 ] <- as.numeric(gene500.cleaned[, 337 ])
gene500.cleaned[, 338 ] <- as.numeric(gene500.cleaned[, 338 ])
gene500.cleaned[, 339 ] <- as.numeric(gene500.cleaned[, 339 ])
gene500.cleaned[, 340 ] <- as.numeric(gene500.cleaned[, 340 ])
gene500.cleaned[, 341 ] <- as.numeric(gene500.cleaned[, 341 ])
gene500.cleaned[, 342 ] <- as.numeric(gene500.cleaned[, 342 ])
gene500.cleaned[, 343 ] <- as.numeric(gene500.cleaned[, 343 ])
gene500.cleaned[, 344 ] <- as.numeric(gene500.cleaned[, 344 ])
gene500.cleaned[, 345 ] <- as.numeric(gene500.cleaned[, 345 ])
gene500.cleaned[, 346 ] <- as.numeric(gene500.cleaned[, 346 ])
gene500.cleaned[, 347 ] <- as.numeric(gene500.cleaned[, 347 ])
gene500.cleaned[, 348 ] <- as.numeric(gene500.cleaned[, 348 ])
gene500.cleaned[, 349 ] <- as.numeric(gene500.cleaned[, 349 ])
gene500.cleaned[, 350 ] <- as.numeric(gene500.cleaned[, 350 ])
gene500.cleaned[, 351 ] <- as.numeric(gene500.cleaned[, 351 ])
gene500.cleaned[, 352 ] <- as.numeric(gene500.cleaned[, 352 ])
gene500.cleaned[, 353 ] <- as.numeric(gene500.cleaned[, 353 ])
gene500.cleaned[, 354 ] <- as.numeric(gene500.cleaned[, 354 ])
gene500.cleaned[, 355 ] <- as.numeric(gene500.cleaned[, 355 ])
gene500.cleaned[, 356 ] <- as.numeric(gene500.cleaned[, 356 ])
gene500.cleaned[, 357 ] <- as.numeric(gene500.cleaned[, 357 ])
gene500.cleaned[, 358 ] <- as.numeric(gene500.cleaned[, 358 ])
gene500.cleaned[, 359 ] <- as.numeric(gene500.cleaned[, 359 ])
gene500.cleaned[, 360 ] <- as.numeric(gene500.cleaned[, 360 ])
gene500.cleaned[, 361 ] <- as.numeric(gene500.cleaned[, 361 ])
gene500.cleaned[, 362 ] <- as.numeric(gene500.cleaned[, 362 ])
gene500.cleaned[, 363 ] <- as.numeric(gene500.cleaned[, 363 ])
gene500.cleaned[, 364 ] <- as.numeric(gene500.cleaned[, 364 ])
gene500.cleaned[, 365 ] <- as.numeric(gene500.cleaned[, 365 ])
gene500.cleaned[, 366 ] <- as.numeric(gene500.cleaned[, 366 ])
gene500.cleaned[, 367 ] <- as.numeric(gene500.cleaned[, 367 ])
gene500.cleaned[, 368 ] <- as.numeric(gene500.cleaned[, 368 ])
gene500.cleaned[, 369 ] <- as.numeric(gene500.cleaned[, 369 ])
gene500.cleaned[, 370 ] <- as.numeric(gene500.cleaned[, 370 ])
gene500.cleaned[, 371 ] <- as.numeric(gene500.cleaned[, 371 ])
gene500.cleaned[, 372 ] <- as.numeric(gene500.cleaned[, 372 ])
gene500.cleaned[, 373 ] <- as.numeric(gene500.cleaned[, 373 ])
gene500.cleaned[, 374 ] <- as.numeric(gene500.cleaned[, 374 ])
gene500.cleaned[, 375 ] <- as.numeric(gene500.cleaned[, 375 ])
gene500.cleaned[, 376 ] <- as.numeric(gene500.cleaned[, 376 ])
gene500.cleaned[, 377 ] <- as.numeric(gene500.cleaned[, 377 ])
gene500.cleaned[, 378 ] <- as.numeric(gene500.cleaned[, 378 ])
gene500.cleaned[, 379 ] <- as.numeric(gene500.cleaned[, 379 ])
gene500.cleaned[, 380 ] <- as.numeric(gene500.cleaned[, 380 ])
gene500.cleaned[, 381 ] <- as.numeric(gene500.cleaned[, 381 ])
gene500.cleaned[, 382 ] <- as.numeric(gene500.cleaned[, 382 ])
gene500.cleaned[, 383 ] <- as.numeric(gene500.cleaned[, 383 ])
gene500.cleaned[, 384 ] <- as.numeric(gene500.cleaned[, 384 ])
gene500.cleaned[, 385 ] <- as.numeric(gene500.cleaned[, 385 ])
gene500.cleaned[, 386 ] <- as.numeric(gene500.cleaned[, 386 ])
gene500.cleaned[, 387 ] <- as.numeric(gene500.cleaned[, 387 ])
gene500.cleaned[, 388 ] <- as.numeric(gene500.cleaned[, 388 ])
gene500.cleaned[, 389 ] <- as.numeric(gene500.cleaned[, 389 ])
gene500.cleaned[, 390 ] <- as.numeric(gene500.cleaned[, 390 ])
gene500.cleaned[, 391 ] <- as.numeric(gene500.cleaned[, 391 ])
gene500.cleaned[, 392 ] <- as.numeric(gene500.cleaned[, 392 ])
gene500.cleaned[, 393 ] <- as.numeric(gene500.cleaned[, 393 ])
gene500.cleaned[, 394 ] <- as.numeric(gene500.cleaned[, 394 ])
gene500.cleaned[, 395 ] <- as.numeric(gene500.cleaned[, 395 ])
gene500.cleaned[, 396 ] <- as.numeric(gene500.cleaned[, 396 ])
gene500.cleaned[, 397 ] <- as.numeric(gene500.cleaned[, 397 ])
gene500.cleaned[, 398 ] <- as.numeric(gene500.cleaned[, 398 ])
gene500.cleaned[, 399 ] <- as.numeric(gene500.cleaned[, 399 ])
gene500.cleaned[, 400 ] <- as.numeric(gene500.cleaned[, 400 ])
gene500.cleaned[, 401 ] <- as.numeric(gene500.cleaned[, 401 ])
gene500.cleaned[, 402 ] <- as.numeric(gene500.cleaned[, 402 ])
gene500.cleaned[, 403 ] <- as.numeric(gene500.cleaned[, 403 ])
gene500.cleaned[, 404 ] <- as.numeric(gene500.cleaned[, 404 ])
gene500.cleaned[, 405 ] <- as.numeric(gene500.cleaned[, 405 ])
gene500.cleaned[, 406 ] <- as.numeric(gene500.cleaned[, 406 ])
gene500.cleaned[, 407 ] <- as.numeric(gene500.cleaned[, 407 ])
gene500.cleaned[, 408 ] <- as.numeric(gene500.cleaned[, 408 ])
gene500.cleaned[, 409 ] <- as.numeric(gene500.cleaned[, 409 ])
gene500.cleaned[, 410 ] <- as.numeric(gene500.cleaned[, 410 ])
gene500.cleaned[, 411 ] <- as.numeric(gene500.cleaned[, 411 ])
gene500.cleaned[, 412 ] <- as.numeric(gene500.cleaned[, 412 ])
gene500.cleaned[, 413 ] <- as.numeric(gene500.cleaned[, 413 ])
gene500.cleaned[, 414 ] <- as.numeric(gene500.cleaned[, 414 ])
gene500.cleaned[, 415 ] <- as.numeric(gene500.cleaned[, 415 ])
gene500.cleaned[, 416 ] <- as.numeric(gene500.cleaned[, 416 ])
gene500.cleaned[, 417 ] <- as.numeric(gene500.cleaned[, 417 ])
gene500.cleaned[, 418 ] <- as.numeric(gene500.cleaned[, 418 ])
gene500.cleaned[, 419 ] <- as.numeric(gene500.cleaned[, 419 ])
gene500.cleaned[, 420 ] <- as.numeric(gene500.cleaned[, 420 ])
gene500.cleaned[, 421 ] <- as.numeric(gene500.cleaned[, 421 ])
gene500.cleaned[, 422 ] <- as.numeric(gene500.cleaned[, 422 ])
gene500.cleaned[, 423 ] <- as.numeric(gene500.cleaned[, 423 ])
gene500.cleaned[, 424 ] <- as.numeric(gene500.cleaned[, 424 ])
gene500.cleaned[, 425 ] <- as.numeric(gene500.cleaned[, 425 ])
gene500.cleaned[, 426 ] <- as.numeric(gene500.cleaned[, 426 ])
gene500.cleaned[, 427 ] <- as.numeric(gene500.cleaned[, 427 ])
gene500.cleaned[, 428 ] <- as.numeric(gene500.cleaned[, 428 ])
gene500.cleaned[, 429 ] <- as.numeric(gene500.cleaned[, 429 ])
gene500.cleaned[, 430 ] <- as.numeric(gene500.cleaned[, 430 ])
gene500.cleaned[, 431 ] <- as.numeric(gene500.cleaned[, 431 ])
gene500.cleaned[, 432 ] <- as.numeric(gene500.cleaned[, 432 ])
gene500.cleaned[, 433 ] <- as.numeric(gene500.cleaned[, 433 ])
gene500.cleaned[, 434 ] <- as.numeric(gene500.cleaned[, 434 ])
gene500.cleaned[, 435 ] <- as.numeric(gene500.cleaned[, 435 ])
gene500.cleaned[, 436 ] <- as.numeric(gene500.cleaned[, 436 ])
gene500.cleaned[, 437 ] <- as.numeric(gene500.cleaned[, 437 ])
gene500.cleaned[, 438 ] <- as.numeric(gene500.cleaned[, 438 ])
gene500.cleaned[, 439 ] <- as.numeric(gene500.cleaned[, 439 ])
gene500.cleaned[, 440 ] <- as.numeric(gene500.cleaned[, 440 ])
gene500.cleaned[, 441 ] <- as.numeric(gene500.cleaned[, 441 ])
gene500.cleaned[, 442 ] <- as.numeric(gene500.cleaned[, 442 ])
gene500.cleaned[, 443 ] <- as.numeric(gene500.cleaned[, 443 ])
gene500.cleaned[, 444 ] <- as.numeric(gene500.cleaned[, 444 ])
gene500.cleaned[, 445 ] <- as.numeric(gene500.cleaned[, 445 ])
gene500.cleaned[, 446 ] <- as.numeric(gene500.cleaned[, 446 ])
gene500.cleaned[, 447 ] <- as.numeric(gene500.cleaned[, 447 ])
gene500.cleaned[, 448 ] <- as.numeric(gene500.cleaned[, 448 ])
gene500.cleaned[, 449 ] <- as.numeric(gene500.cleaned[, 449 ])
gene500.cleaned[, 450 ] <- as.numeric(gene500.cleaned[, 450 ])
gene500.cleaned[, 451 ] <- as.numeric(gene500.cleaned[, 451 ])
gene500.cleaned[, 452 ] <- as.numeric(gene500.cleaned[, 452 ])
gene500.cleaned[, 453 ] <- as.numeric(gene500.cleaned[, 453 ])
gene500.cleaned[, 454 ] <- as.numeric(gene500.cleaned[, 454 ])
gene500.cleaned[, 455 ] <- as.numeric(gene500.cleaned[, 455 ])
gene500.cleaned[, 456 ] <- as.numeric(gene500.cleaned[, 456 ])
gene500.cleaned[, 457 ] <- as.numeric(gene500.cleaned[, 457 ])
gene500.cleaned[, 458 ] <- as.numeric(gene500.cleaned[, 458 ])
gene500.cleaned[, 459 ] <- as.numeric(gene500.cleaned[, 459 ])
gene500.cleaned[, 460 ] <- as.numeric(gene500.cleaned[, 460 ])
gene500.cleaned[, 461 ] <- as.numeric(gene500.cleaned[, 461 ])
gene500.cleaned[, 462 ] <- as.numeric(gene500.cleaned[, 462 ])
gene500.cleaned[, 463 ] <- as.numeric(gene500.cleaned[, 463 ])
gene500.cleaned[, 464 ] <- as.numeric(gene500.cleaned[, 464 ])
gene500.cleaned[, 465 ] <- as.numeric(gene500.cleaned[, 465 ])
gene500.cleaned[, 466 ] <- as.numeric(gene500.cleaned[, 466 ])
gene500.cleaned[, 467 ] <- as.numeric(gene500.cleaned[, 467 ])
gene500.cleaned[, 468 ] <- as.numeric(gene500.cleaned[, 468 ])
gene500.cleaned[, 469 ] <- as.numeric(gene500.cleaned[, 469 ])
gene500.cleaned[, 470 ] <- as.numeric(gene500.cleaned[, 470 ])
gene500.cleaned[, 471 ] <- as.numeric(gene500.cleaned[, 471 ])
gene500.cleaned[, 472 ] <- as.numeric(gene500.cleaned[, 472 ])
gene500.cleaned[, 473 ] <- as.numeric(gene500.cleaned[, 473 ])
gene500.cleaned[, 474 ] <- as.numeric(gene500.cleaned[, 474 ])
gene500.cleaned[, 475 ] <- as.numeric(gene500.cleaned[, 475 ])
gene500.cleaned[, 476 ] <- as.numeric(gene500.cleaned[, 476 ])
gene500.cleaned[, 477 ] <- as.numeric(gene500.cleaned[, 477 ])
gene500.cleaned[, 478 ] <- as.numeric(gene500.cleaned[, 478 ])
gene500.cleaned[, 479 ] <- as.numeric(gene500.cleaned[, 479 ])
gene500.cleaned[, 480 ] <- as.numeric(gene500.cleaned[, 480 ])
gene500.cleaned[, 481 ] <- as.numeric(gene500.cleaned[, 481 ])
gene500.cleaned[, 482 ] <- as.numeric(gene500.cleaned[, 482 ])
gene500.cleaned[, 483 ] <- as.numeric(gene500.cleaned[, 483 ])
gene500.cleaned[, 484 ] <- as.numeric(gene500.cleaned[, 484 ])
gene500.cleaned[, 485 ] <- as.numeric(gene500.cleaned[, 485 ])
gene500.cleaned[, 486 ] <- as.numeric(gene500.cleaned[, 486 ])
gene500.cleaned[, 487 ] <- as.numeric(gene500.cleaned[, 487 ])
gene500.cleaned[, 488 ] <- as.numeric(gene500.cleaned[, 488 ])
gene500.cleaned[, 489 ] <- as.numeric(gene500.cleaned[, 489 ])
gene500.cleaned[, 490 ] <- as.numeric(gene500.cleaned[, 490 ])
gene500.cleaned[, 491 ] <- as.numeric(gene500.cleaned[, 491 ])
gene500.cleaned[, 492 ] <- as.numeric(gene500.cleaned[, 492 ])
gene500.cleaned[, 493 ] <- as.numeric(gene500.cleaned[, 493 ])
gene500.cleaned[, 494 ] <- as.numeric(gene500.cleaned[, 494 ])
gene500.cleaned[, 495 ] <- as.numeric(gene500.cleaned[, 495 ])
gene500.cleaned[, 496 ] <- as.numeric(gene500.cleaned[, 496 ])
gene500.cleaned[, 497 ] <- as.numeric(gene500.cleaned[, 497 ])
gene500.cleaned[, 498 ] <- as.numeric(gene500.cleaned[, 498 ])
gene500.cleaned[, 499 ] <- as.numeric(gene500.cleaned[, 499 ])
gene500.cleaned[, 500 ] <- as.numeric(gene500.cleaned[, 500 ])
```
#Confirm inactive
gene500_train$inactive
#First look at LDA and KNN before PCA
```

TRAINING/TESTING SPLIT (500 Features)

```{r}

#Split into test train data
gene500_t <- sample(dim(gene500.cleaned)[1],8000)
gene500_train <- gene500.cleaned[gene500_t,]
gene500_test <- gene500.cleaned[-gene500_t,]
```

LINEAR DISCRIMINAT ANALYSIS (500 Features)

```{r}

#z500 is lda model with 500 features

z500 <- lda(gene500_train$inactive~., data = gene500_train)

#use z500 to make predictions
p500 <- predict(z500, gene500_test)


#Compute lda error by comparing predictions and test data
lda500_error <- mean(p500$class == gene500_test$inactive)
lda500_error
#Gave us really good accuracy 98%
```

K-NEAREST NEIGHBORS (500 Features)

Hyperparameter tuning used to find optimal K between 1 and 10

```{r}
#KNN needs "inactive" as numeric (0, 1)

gene500_train$inactive <- as.numeric(gene500_train$inactive)
gene500_test$inactive <- as.numeric(gene500_test$inactive)

test500_pred <- knn(
  train = gene500_train, 
  test = gene500_test,
  cl = gene500_train$inactive, 
  k=8
)

#Confusion matrix to test accuracy

actual500 <- gene500_test$inactive

confusion_matrix_KNN500 <- table(actual500,test500_pred)
confusion_matrix_KNN500

accuracy500 <- sum(diag(confusion_matrix_KNN500))/length(actual500)
sprintf("Accuracy: %.2f%%", accuracy500*100)
```

PRINCIPAL COMPONENT ANALYSIS (500 Features)

```{r}

#Create PCA model
pca500 <- prcomp(gene500.cleaned[,-501], scale = TRUE)


#Let's draw a 2D plot using the top 2 
#X contains the principal components in the model

plot(pca500$x[,1], pca500$x[,2])

#Look at 2nd PC and 3rd PC

plot(pca500$x[,2], pca500$x[,3])
```

```{r}
plot(pca500)
plot(pca500$x)
```

#Usevariance to create scree plot

```{r}
pca500_var <- pca500$sdev^2
pca500_var_per <- round(pca500_var/sum(pca500_var)*100, 1)
barplot(pca500_var_per, main = "Scree Plot", xlab = "Principal Component", ylab = "Percent Variation")

```

FIND TOP 10 GENES (500 Features)

```{r}
#Get loading score

loading_score500 <- pca500$rotation[,1]
gene500_score <- abs(loading_score500)

gene_score_ranked500 <- sort(gene500_score, decreasing = TRUE)

top_10_genes500 <- names(gene_score_ranked500[1:5])

top_10_genes500

pca500$rotation[top_10_genes500, 1]


#Repeat LDA and KNN for gene500 dataset

new_gene500 = subset(gene500.cleaned, select = c(X0.022.11, X0.021.18, X0.02.4, X0.025.15, X0.021.19, X.0.037.21, X.0.066.8, X0.016.30, X0.008.23, X.0.034.16, inactive))



#Split into train and test data again
#Use gene_pca dataset

gene500_pca_t <- sample(dim(new_gene500)[1],8000)
train500_pca <- new_gene500[gene500_pca_t,]
test500_pca <- new_gene500[-gene500_pca_t,]
```

LDA AND KNN WITH TOP 10 GENES

```{r}
#Now try lda model

w500_afterpca <- lda(train500_pca$inactive~., data = train500_pca)

#Use the predict function

pr500_afterpca <- predict(w500_afterpca, test500_pca)

lda_error_500_afterpca <- mean(pr500_afterpca$class == test500_pca$inactive)
lda_error_500_afterpca

#Retry KNN model

train500_pca$inactive <- as.numeric(train500_pca$inactive)
test500_pca$inactive <- as.numeric(test500_pca$inactive)

#Hyperparameter testing yielded K = 10

test500_pred_afterpca <- knn(
  train = train500_pca, 
  test = test500_pca,
  cl = train500_pca$inactive, 
  k=10
)

actual500_pca <- test500_pca$inactive

confusion_matrix_KNN_pca <- table(actual500_pca,test500_pred_afterpca)
confusion_matrix_KNN_pca

accuracy500 <- sum(diag(confusion_matrix_KNN_pca))/length(actual500_pca)
sprintf("Accuracy: %.2f%%", accuracy500*100)
```

DATASET with 2000 FEATURES

DATA CLEANING 

*as.numeric rows excluded for presentation sake

```{r}

gene_5408 <- gene[1:10000, 3408:5409]

#Remove missing values
matches5408 <- grepl("\\?", gene_5408$X0.009.28)
gene_hits_5408 <- gene_5408[matches5408,]
gene_noquest_5408 <- gene_5408[!matches5408,]

#Remove Na

gene5408.cleaned <- na.omit(gene_noquest_5408)

#Every variable needs to be reformatted as numeric
gene5408.cleaned$inactive <- as.factor(gene5408.cleaned$inactive)
```

```{r}
gene5408.cleaned[,  1 ] <- as.numeric(gene5408.cleaned[, 1 ])
gene5408.cleaned[,  2 ] <- as.numeric(gene5408.cleaned[, 2 ])
gene5408.cleaned[,  3 ] <- as.numeric(gene5408.cleaned[, 3 ])
gene5408.cleaned[,  4 ] <- as.numeric(gene5408.cleaned[, 4 ])
gene5408.cleaned[,  5 ] <- as.numeric(gene5408.cleaned[, 5 ])
gene5408.cleaned[,  6 ] <- as.numeric(gene5408.cleaned[, 6 ])
gene5408.cleaned[,  7 ] <- as.numeric(gene5408.cleaned[, 7 ])
gene5408.cleaned[,  8 ] <- as.numeric(gene5408.cleaned[, 8 ])
gene5408.cleaned[,  9 ] <- as.numeric(gene5408.cleaned[, 9 ])
gene5408.cleaned[,  10 ] <- as.numeric(gene5408.cleaned[, 10 ])
gene5408.cleaned[,  11 ] <- as.numeric(gene5408.cleaned[, 11 ])
gene5408.cleaned[,  12 ] <- as.numeric(gene5408.cleaned[, 12 ])
gene5408.cleaned[,  13 ] <- as.numeric(gene5408.cleaned[, 13 ])
gene5408.cleaned[,  14 ] <- as.numeric(gene5408.cleaned[, 14 ])
gene5408.cleaned[,  15 ] <- as.numeric(gene5408.cleaned[, 15 ])
gene5408.cleaned[,  16 ] <- as.numeric(gene5408.cleaned[, 16 ])
gene5408.cleaned[,  17 ] <- as.numeric(gene5408.cleaned[, 17 ])
gene5408.cleaned[,  18 ] <- as.numeric(gene5408.cleaned[, 18 ])
gene5408.cleaned[,  19 ] <- as.numeric(gene5408.cleaned[, 19 ])
gene5408.cleaned[,  20 ] <- as.numeric(gene5408.cleaned[, 20 ])
gene5408.cleaned[,  21 ] <- as.numeric(gene5408.cleaned[, 21 ])
gene5408.cleaned[,  22 ] <- as.numeric(gene5408.cleaned[, 22 ])
gene5408.cleaned[,  23 ] <- as.numeric(gene5408.cleaned[, 23 ])
gene5408.cleaned[,  24 ] <- as.numeric(gene5408.cleaned[, 24 ])
gene5408.cleaned[,  25 ] <- as.numeric(gene5408.cleaned[, 25 ])
gene5408.cleaned[,  26 ] <- as.numeric(gene5408.cleaned[, 26 ])
gene5408.cleaned[,  27 ] <- as.numeric(gene5408.cleaned[, 27 ])
gene5408.cleaned[,  28 ] <- as.numeric(gene5408.cleaned[, 28 ])
gene5408.cleaned[,  29 ] <- as.numeric(gene5408.cleaned[, 29 ])
gene5408.cleaned[,  30 ] <- as.numeric(gene5408.cleaned[, 30 ])
gene5408.cleaned[,  31 ] <- as.numeric(gene5408.cleaned[, 31 ])
gene5408.cleaned[,  32 ] <- as.numeric(gene5408.cleaned[, 32 ])
gene5408.cleaned[,  33 ] <- as.numeric(gene5408.cleaned[, 33 ])
gene5408.cleaned[,  34 ] <- as.numeric(gene5408.cleaned[, 34 ])
gene5408.cleaned[,  35 ] <- as.numeric(gene5408.cleaned[, 35 ])
gene5408.cleaned[,  36 ] <- as.numeric(gene5408.cleaned[, 36 ])
gene5408.cleaned[,  37 ] <- as.numeric(gene5408.cleaned[, 37 ])
gene5408.cleaned[,  38 ] <- as.numeric(gene5408.cleaned[, 38 ])
gene5408.cleaned[,  39 ] <- as.numeric(gene5408.cleaned[, 39 ])
gene5408.cleaned[,  40 ] <- as.numeric(gene5408.cleaned[, 40 ])
gene5408.cleaned[,  41 ] <- as.numeric(gene5408.cleaned[, 41 ])
gene5408.cleaned[,  42 ] <- as.numeric(gene5408.cleaned[, 42 ])
gene5408.cleaned[,  43 ] <- as.numeric(gene5408.cleaned[, 43 ])
gene5408.cleaned[,  44 ] <- as.numeric(gene5408.cleaned[, 44 ])
gene5408.cleaned[,  45 ] <- as.numeric(gene5408.cleaned[, 45 ])
gene5408.cleaned[,  46 ] <- as.numeric(gene5408.cleaned[, 46 ])
gene5408.cleaned[,  47 ] <- as.numeric(gene5408.cleaned[, 47 ])
gene5408.cleaned[,  48 ] <- as.numeric(gene5408.cleaned[, 48 ])
gene5408.cleaned[,  49 ] <- as.numeric(gene5408.cleaned[, 49 ])
gene5408.cleaned[,  50 ] <- as.numeric(gene5408.cleaned[, 50 ])
gene5408.cleaned[,  51 ] <- as.numeric(gene5408.cleaned[, 51 ])
gene5408.cleaned[,  52 ] <- as.numeric(gene5408.cleaned[, 52 ])
gene5408.cleaned[,  53 ] <- as.numeric(gene5408.cleaned[, 53 ])
gene5408.cleaned[,  54 ] <- as.numeric(gene5408.cleaned[, 54 ])
gene5408.cleaned[,  55 ] <- as.numeric(gene5408.cleaned[, 55 ])
gene5408.cleaned[,  56 ] <- as.numeric(gene5408.cleaned[, 56 ])
gene5408.cleaned[,  57 ] <- as.numeric(gene5408.cleaned[, 57 ])
gene5408.cleaned[,  58 ] <- as.numeric(gene5408.cleaned[, 58 ])
gene5408.cleaned[,  59 ] <- as.numeric(gene5408.cleaned[, 59 ])
gene5408.cleaned[,  60 ] <- as.numeric(gene5408.cleaned[, 60 ])
gene5408.cleaned[,  61 ] <- as.numeric(gene5408.cleaned[, 61 ])
gene5408.cleaned[,  62 ] <- as.numeric(gene5408.cleaned[, 62 ])
gene5408.cleaned[,  63 ] <- as.numeric(gene5408.cleaned[, 63 ])
gene5408.cleaned[,  64 ] <- as.numeric(gene5408.cleaned[, 64 ])
gene5408.cleaned[,  65 ] <- as.numeric(gene5408.cleaned[, 65 ])
gene5408.cleaned[,  66 ] <- as.numeric(gene5408.cleaned[, 66 ])
gene5408.cleaned[,  67 ] <- as.numeric(gene5408.cleaned[, 67 ])
gene5408.cleaned[,  68 ] <- as.numeric(gene5408.cleaned[, 68 ])
gene5408.cleaned[,  69 ] <- as.numeric(gene5408.cleaned[, 69 ])
gene5408.cleaned[,  70 ] <- as.numeric(gene5408.cleaned[, 70 ])
gene5408.cleaned[,  71 ] <- as.numeric(gene5408.cleaned[, 71 ])
gene5408.cleaned[,  72 ] <- as.numeric(gene5408.cleaned[, 72 ])
gene5408.cleaned[,  73 ] <- as.numeric(gene5408.cleaned[, 73 ])
gene5408.cleaned[,  74 ] <- as.numeric(gene5408.cleaned[, 74 ])
gene5408.cleaned[,  75 ] <- as.numeric(gene5408.cleaned[, 75 ])
gene5408.cleaned[,  76 ] <- as.numeric(gene5408.cleaned[, 76 ])
gene5408.cleaned[,  77 ] <- as.numeric(gene5408.cleaned[, 77 ])
gene5408.cleaned[,  78 ] <- as.numeric(gene5408.cleaned[, 78 ])
gene5408.cleaned[,  79 ] <- as.numeric(gene5408.cleaned[, 79 ])
gene5408.cleaned[,  80 ] <- as.numeric(gene5408.cleaned[, 80 ])
gene5408.cleaned[,  81 ] <- as.numeric(gene5408.cleaned[, 81 ])
gene5408.cleaned[,  82 ] <- as.numeric(gene5408.cleaned[, 82 ])
gene5408.cleaned[,  83 ] <- as.numeric(gene5408.cleaned[, 83 ])
gene5408.cleaned[,  84 ] <- as.numeric(gene5408.cleaned[, 84 ])
gene5408.cleaned[,  85 ] <- as.numeric(gene5408.cleaned[, 85 ])
gene5408.cleaned[,  86 ] <- as.numeric(gene5408.cleaned[, 86 ])
gene5408.cleaned[,  87 ] <- as.numeric(gene5408.cleaned[, 87 ])
gene5408.cleaned[,  88 ] <- as.numeric(gene5408.cleaned[, 88 ])
gene5408.cleaned[,  89 ] <- as.numeric(gene5408.cleaned[, 89 ])
gene5408.cleaned[,  90 ] <- as.numeric(gene5408.cleaned[, 90 ])
gene5408.cleaned[,  91 ] <- as.numeric(gene5408.cleaned[, 91 ])
gene5408.cleaned[,  92 ] <- as.numeric(gene5408.cleaned[, 92 ])
gene5408.cleaned[,  93 ] <- as.numeric(gene5408.cleaned[, 93 ])
gene5408.cleaned[,  94 ] <- as.numeric(gene5408.cleaned[, 94 ])
gene5408.cleaned[,  95 ] <- as.numeric(gene5408.cleaned[, 95 ])
gene5408.cleaned[,  96 ] <- as.numeric(gene5408.cleaned[, 96 ])
gene5408.cleaned[,  97 ] <- as.numeric(gene5408.cleaned[, 97 ])
gene5408.cleaned[,  98 ] <- as.numeric(gene5408.cleaned[, 98 ])
gene5408.cleaned[,  99 ] <- as.numeric(gene5408.cleaned[, 99 ])
gene5408.cleaned[,  100 ] <- as.numeric(gene5408.cleaned[, 100 ])
gene5408.cleaned[,  101 ] <- as.numeric(gene5408.cleaned[, 101 ])
gene5408.cleaned[,  102 ] <- as.numeric(gene5408.cleaned[, 102 ])
gene5408.cleaned[,  103 ] <- as.numeric(gene5408.cleaned[, 103 ])
gene5408.cleaned[,  104 ] <- as.numeric(gene5408.cleaned[, 104 ])
gene5408.cleaned[,  105 ] <- as.numeric(gene5408.cleaned[, 105 ])
gene5408.cleaned[,  106 ] <- as.numeric(gene5408.cleaned[, 106 ])
gene5408.cleaned[,  107 ] <- as.numeric(gene5408.cleaned[, 107 ])
gene5408.cleaned[,  108 ] <- as.numeric(gene5408.cleaned[, 108 ])
gene5408.cleaned[,  109 ] <- as.numeric(gene5408.cleaned[, 109 ])
gene5408.cleaned[,  110 ] <- as.numeric(gene5408.cleaned[, 110 ])
gene5408.cleaned[,  111 ] <- as.numeric(gene5408.cleaned[, 111 ])
gene5408.cleaned[,  112 ] <- as.numeric(gene5408.cleaned[, 112 ])
gene5408.cleaned[,  113 ] <- as.numeric(gene5408.cleaned[, 113 ])
gene5408.cleaned[,  114 ] <- as.numeric(gene5408.cleaned[, 114 ])
gene5408.cleaned[,  115 ] <- as.numeric(gene5408.cleaned[, 115 ])
gene5408.cleaned[,  116 ] <- as.numeric(gene5408.cleaned[, 116 ])
gene5408.cleaned[,  117 ] <- as.numeric(gene5408.cleaned[, 117 ])
gene5408.cleaned[,  118 ] <- as.numeric(gene5408.cleaned[, 118 ])
gene5408.cleaned[,  119 ] <- as.numeric(gene5408.cleaned[, 119 ])
gene5408.cleaned[,  120 ] <- as.numeric(gene5408.cleaned[, 120 ])
gene5408.cleaned[,  121 ] <- as.numeric(gene5408.cleaned[, 121 ])
gene5408.cleaned[,  122 ] <- as.numeric(gene5408.cleaned[, 122 ])
gene5408.cleaned[,  123 ] <- as.numeric(gene5408.cleaned[, 123 ])
gene5408.cleaned[,  124 ] <- as.numeric(gene5408.cleaned[, 124 ])
gene5408.cleaned[,  125 ] <- as.numeric(gene5408.cleaned[, 125 ])
gene5408.cleaned[,  126 ] <- as.numeric(gene5408.cleaned[, 126 ])
gene5408.cleaned[,  127 ] <- as.numeric(gene5408.cleaned[, 127 ])
gene5408.cleaned[,  128 ] <- as.numeric(gene5408.cleaned[, 128 ])
gene5408.cleaned[,  129 ] <- as.numeric(gene5408.cleaned[, 129 ])
gene5408.cleaned[,  130 ] <- as.numeric(gene5408.cleaned[, 130 ])
gene5408.cleaned[,  131 ] <- as.numeric(gene5408.cleaned[, 131 ])
gene5408.cleaned[,  132 ] <- as.numeric(gene5408.cleaned[, 132 ])
gene5408.cleaned[,  133 ] <- as.numeric(gene5408.cleaned[, 133 ])
gene5408.cleaned[,  134 ] <- as.numeric(gene5408.cleaned[, 134 ])
gene5408.cleaned[,  135 ] <- as.numeric(gene5408.cleaned[, 135 ])
gene5408.cleaned[,  136 ] <- as.numeric(gene5408.cleaned[, 136 ])
gene5408.cleaned[,  137 ] <- as.numeric(gene5408.cleaned[, 137 ])
gene5408.cleaned[,  138 ] <- as.numeric(gene5408.cleaned[, 138 ])
gene5408.cleaned[,  139 ] <- as.numeric(gene5408.cleaned[, 139 ])
gene5408.cleaned[,  140 ] <- as.numeric(gene5408.cleaned[, 140 ])
gene5408.cleaned[,  141 ] <- as.numeric(gene5408.cleaned[, 141 ])
gene5408.cleaned[,  142 ] <- as.numeric(gene5408.cleaned[, 142 ])
gene5408.cleaned[,  143 ] <- as.numeric(gene5408.cleaned[, 143 ])
gene5408.cleaned[,  144 ] <- as.numeric(gene5408.cleaned[, 144 ])
gene5408.cleaned[,  145 ] <- as.numeric(gene5408.cleaned[, 145 ])
gene5408.cleaned[,  146 ] <- as.numeric(gene5408.cleaned[, 146 ])
gene5408.cleaned[,  147 ] <- as.numeric(gene5408.cleaned[, 147 ])
gene5408.cleaned[,  148 ] <- as.numeric(gene5408.cleaned[, 148 ])
gene5408.cleaned[,  149 ] <- as.numeric(gene5408.cleaned[, 149 ])
gene5408.cleaned[,  150 ] <- as.numeric(gene5408.cleaned[, 150 ])
gene5408.cleaned[,  151 ] <- as.numeric(gene5408.cleaned[, 151 ])
gene5408.cleaned[,  152 ] <- as.numeric(gene5408.cleaned[, 152 ])
gene5408.cleaned[,  153 ] <- as.numeric(gene5408.cleaned[, 153 ])
gene5408.cleaned[,  154 ] <- as.numeric(gene5408.cleaned[, 154 ])
gene5408.cleaned[,  155 ] <- as.numeric(gene5408.cleaned[, 155 ])
gene5408.cleaned[,  156 ] <- as.numeric(gene5408.cleaned[, 156 ])
gene5408.cleaned[,  157 ] <- as.numeric(gene5408.cleaned[, 157 ])
gene5408.cleaned[,  158 ] <- as.numeric(gene5408.cleaned[, 158 ])
gene5408.cleaned[,  159 ] <- as.numeric(gene5408.cleaned[, 159 ])
gene5408.cleaned[,  160 ] <- as.numeric(gene5408.cleaned[, 160 ])
gene5408.cleaned[,  161 ] <- as.numeric(gene5408.cleaned[, 161 ])
gene5408.cleaned[,  162 ] <- as.numeric(gene5408.cleaned[, 162 ])
gene5408.cleaned[,  163 ] <- as.numeric(gene5408.cleaned[, 163 ])
gene5408.cleaned[,  164 ] <- as.numeric(gene5408.cleaned[, 164 ])
gene5408.cleaned[,  165 ] <- as.numeric(gene5408.cleaned[, 165 ])
gene5408.cleaned[,  166 ] <- as.numeric(gene5408.cleaned[, 166 ])
gene5408.cleaned[,  167 ] <- as.numeric(gene5408.cleaned[, 167 ])
gene5408.cleaned[,  168 ] <- as.numeric(gene5408.cleaned[, 168 ])
gene5408.cleaned[,  169 ] <- as.numeric(gene5408.cleaned[, 169 ])
gene5408.cleaned[,  170 ] <- as.numeric(gene5408.cleaned[, 170 ])
gene5408.cleaned[,  171 ] <- as.numeric(gene5408.cleaned[, 171 ])
gene5408.cleaned[,  172 ] <- as.numeric(gene5408.cleaned[, 172 ])
gene5408.cleaned[,  173 ] <- as.numeric(gene5408.cleaned[, 173 ])
gene5408.cleaned[,  174 ] <- as.numeric(gene5408.cleaned[, 174 ])
gene5408.cleaned[,  175 ] <- as.numeric(gene5408.cleaned[, 175 ])
gene5408.cleaned[,  176 ] <- as.numeric(gene5408.cleaned[, 176 ])
gene5408.cleaned[,  177 ] <- as.numeric(gene5408.cleaned[, 177 ])
gene5408.cleaned[,  178 ] <- as.numeric(gene5408.cleaned[, 178 ])
gene5408.cleaned[,  179 ] <- as.numeric(gene5408.cleaned[, 179 ])
gene5408.cleaned[,  180 ] <- as.numeric(gene5408.cleaned[, 180 ])
gene5408.cleaned[,  181 ] <- as.numeric(gene5408.cleaned[, 181 ])
gene5408.cleaned[,  182 ] <- as.numeric(gene5408.cleaned[, 182 ])
gene5408.cleaned[,  183 ] <- as.numeric(gene5408.cleaned[, 183 ])
gene5408.cleaned[,  184 ] <- as.numeric(gene5408.cleaned[, 184 ])
gene5408.cleaned[,  185 ] <- as.numeric(gene5408.cleaned[, 185 ])
gene5408.cleaned[,  186 ] <- as.numeric(gene5408.cleaned[, 186 ])
gene5408.cleaned[,  187 ] <- as.numeric(gene5408.cleaned[, 187 ])
gene5408.cleaned[,  188 ] <- as.numeric(gene5408.cleaned[, 188 ])
gene5408.cleaned[,  189 ] <- as.numeric(gene5408.cleaned[, 189 ])
gene5408.cleaned[,  190 ] <- as.numeric(gene5408.cleaned[, 190 ])
gene5408.cleaned[,  191 ] <- as.numeric(gene5408.cleaned[, 191 ])
gene5408.cleaned[,  192 ] <- as.numeric(gene5408.cleaned[, 192 ])
gene5408.cleaned[,  193 ] <- as.numeric(gene5408.cleaned[, 193 ])
gene5408.cleaned[,  194 ] <- as.numeric(gene5408.cleaned[, 194 ])
gene5408.cleaned[,  195 ] <- as.numeric(gene5408.cleaned[, 195 ])
gene5408.cleaned[,  196 ] <- as.numeric(gene5408.cleaned[, 196 ])
gene5408.cleaned[,  197 ] <- as.numeric(gene5408.cleaned[, 197 ])
gene5408.cleaned[,  198 ] <- as.numeric(gene5408.cleaned[, 198 ])
gene5408.cleaned[,  199 ] <- as.numeric(gene5408.cleaned[, 199 ])
gene5408.cleaned[,  200 ] <- as.numeric(gene5408.cleaned[, 200 ])
gene5408.cleaned[,  201 ] <- as.numeric(gene5408.cleaned[, 201 ])
gene5408.cleaned[,  202 ] <- as.numeric(gene5408.cleaned[, 202 ])
gene5408.cleaned[,  203 ] <- as.numeric(gene5408.cleaned[, 203 ])
gene5408.cleaned[,  204 ] <- as.numeric(gene5408.cleaned[, 204 ])
gene5408.cleaned[,  205 ] <- as.numeric(gene5408.cleaned[, 205 ])
gene5408.cleaned[,  206 ] <- as.numeric(gene5408.cleaned[, 206 ])
gene5408.cleaned[,  207 ] <- as.numeric(gene5408.cleaned[, 207 ])
gene5408.cleaned[,  208 ] <- as.numeric(gene5408.cleaned[, 208 ])
gene5408.cleaned[,  209 ] <- as.numeric(gene5408.cleaned[, 209 ])
gene5408.cleaned[,  210 ] <- as.numeric(gene5408.cleaned[, 210 ])
gene5408.cleaned[,  211 ] <- as.numeric(gene5408.cleaned[, 211 ])
gene5408.cleaned[,  212 ] <- as.numeric(gene5408.cleaned[, 212 ])
gene5408.cleaned[,  213 ] <- as.numeric(gene5408.cleaned[, 213 ])
gene5408.cleaned[,  214 ] <- as.numeric(gene5408.cleaned[, 214 ])
gene5408.cleaned[,  215 ] <- as.numeric(gene5408.cleaned[, 215 ])
gene5408.cleaned[,  216 ] <- as.numeric(gene5408.cleaned[, 216 ])
gene5408.cleaned[,  217 ] <- as.numeric(gene5408.cleaned[, 217 ])
gene5408.cleaned[,  218 ] <- as.numeric(gene5408.cleaned[, 218 ])
gene5408.cleaned[,  219 ] <- as.numeric(gene5408.cleaned[, 219 ])
gene5408.cleaned[,  220 ] <- as.numeric(gene5408.cleaned[, 220 ])
gene5408.cleaned[,  221 ] <- as.numeric(gene5408.cleaned[, 221 ])
gene5408.cleaned[,  222 ] <- as.numeric(gene5408.cleaned[, 222 ])
gene5408.cleaned[,  223 ] <- as.numeric(gene5408.cleaned[, 223 ])
gene5408.cleaned[,  224 ] <- as.numeric(gene5408.cleaned[, 224 ])
gene5408.cleaned[,  225 ] <- as.numeric(gene5408.cleaned[, 225 ])
gene5408.cleaned[,  226 ] <- as.numeric(gene5408.cleaned[, 226 ])
gene5408.cleaned[,  227 ] <- as.numeric(gene5408.cleaned[, 227 ])
gene5408.cleaned[,  228 ] <- as.numeric(gene5408.cleaned[, 228 ])
gene5408.cleaned[,  229 ] <- as.numeric(gene5408.cleaned[, 229 ])
gene5408.cleaned[,  230 ] <- as.numeric(gene5408.cleaned[, 230 ])
gene5408.cleaned[,  231 ] <- as.numeric(gene5408.cleaned[, 231 ])
gene5408.cleaned[,  232 ] <- as.numeric(gene5408.cleaned[, 232 ])
gene5408.cleaned[,  233 ] <- as.numeric(gene5408.cleaned[, 233 ])
gene5408.cleaned[,  234 ] <- as.numeric(gene5408.cleaned[, 234 ])
gene5408.cleaned[,  235 ] <- as.numeric(gene5408.cleaned[, 235 ])
gene5408.cleaned[,  236 ] <- as.numeric(gene5408.cleaned[, 236 ])
gene5408.cleaned[,  237 ] <- as.numeric(gene5408.cleaned[, 237 ])
gene5408.cleaned[,  238 ] <- as.numeric(gene5408.cleaned[, 238 ])
gene5408.cleaned[,  239 ] <- as.numeric(gene5408.cleaned[, 239 ])
gene5408.cleaned[,  240 ] <- as.numeric(gene5408.cleaned[, 240 ])
gene5408.cleaned[,  241 ] <- as.numeric(gene5408.cleaned[, 241 ])
gene5408.cleaned[,  242 ] <- as.numeric(gene5408.cleaned[, 242 ])
gene5408.cleaned[,  243 ] <- as.numeric(gene5408.cleaned[, 243 ])
gene5408.cleaned[,  244 ] <- as.numeric(gene5408.cleaned[, 244 ])
gene5408.cleaned[,  245 ] <- as.numeric(gene5408.cleaned[, 245 ])
gene5408.cleaned[,  246 ] <- as.numeric(gene5408.cleaned[, 246 ])
gene5408.cleaned[,  247 ] <- as.numeric(gene5408.cleaned[, 247 ])
gene5408.cleaned[,  248 ] <- as.numeric(gene5408.cleaned[, 248 ])
gene5408.cleaned[,  249 ] <- as.numeric(gene5408.cleaned[, 249 ])
gene5408.cleaned[,  250 ] <- as.numeric(gene5408.cleaned[, 250 ])
gene5408.cleaned[,  251 ] <- as.numeric(gene5408.cleaned[, 251 ])
gene5408.cleaned[,  252 ] <- as.numeric(gene5408.cleaned[, 252 ])
gene5408.cleaned[,  253 ] <- as.numeric(gene5408.cleaned[, 253 ])
gene5408.cleaned[,  254 ] <- as.numeric(gene5408.cleaned[, 254 ])
gene5408.cleaned[,  255 ] <- as.numeric(gene5408.cleaned[, 255 ])
gene5408.cleaned[,  256 ] <- as.numeric(gene5408.cleaned[, 256 ])
gene5408.cleaned[,  257 ] <- as.numeric(gene5408.cleaned[, 257 ])
gene5408.cleaned[,  258 ] <- as.numeric(gene5408.cleaned[, 258 ])
gene5408.cleaned[,  259 ] <- as.numeric(gene5408.cleaned[, 259 ])
gene5408.cleaned[,  260 ] <- as.numeric(gene5408.cleaned[, 260 ])
gene5408.cleaned[,  261 ] <- as.numeric(gene5408.cleaned[, 261 ])
gene5408.cleaned[,  262 ] <- as.numeric(gene5408.cleaned[, 262 ])
gene5408.cleaned[,  263 ] <- as.numeric(gene5408.cleaned[, 263 ])
gene5408.cleaned[,  264 ] <- as.numeric(gene5408.cleaned[, 264 ])
gene5408.cleaned[,  265 ] <- as.numeric(gene5408.cleaned[, 265 ])
gene5408.cleaned[,  266 ] <- as.numeric(gene5408.cleaned[, 266 ])
gene5408.cleaned[,  267 ] <- as.numeric(gene5408.cleaned[, 267 ])
gene5408.cleaned[,  268 ] <- as.numeric(gene5408.cleaned[, 268 ])
gene5408.cleaned[,  269 ] <- as.numeric(gene5408.cleaned[, 269 ])
gene5408.cleaned[,  270 ] <- as.numeric(gene5408.cleaned[, 270 ])
gene5408.cleaned[,  271 ] <- as.numeric(gene5408.cleaned[, 271 ])
gene5408.cleaned[,  272 ] <- as.numeric(gene5408.cleaned[, 272 ])
gene5408.cleaned[,  273 ] <- as.numeric(gene5408.cleaned[, 273 ])
gene5408.cleaned[,  274 ] <- as.numeric(gene5408.cleaned[, 274 ])
gene5408.cleaned[,  275 ] <- as.numeric(gene5408.cleaned[, 275 ])
gene5408.cleaned[,  276 ] <- as.numeric(gene5408.cleaned[, 276 ])
gene5408.cleaned[,  277 ] <- as.numeric(gene5408.cleaned[, 277 ])
gene5408.cleaned[,  278 ] <- as.numeric(gene5408.cleaned[, 278 ])
gene5408.cleaned[,  279 ] <- as.numeric(gene5408.cleaned[, 279 ])
gene5408.cleaned[,  280 ] <- as.numeric(gene5408.cleaned[, 280 ])
gene5408.cleaned[,  281 ] <- as.numeric(gene5408.cleaned[, 281 ])
gene5408.cleaned[,  282 ] <- as.numeric(gene5408.cleaned[, 282 ])
gene5408.cleaned[,  283 ] <- as.numeric(gene5408.cleaned[, 283 ])
gene5408.cleaned[,  284 ] <- as.numeric(gene5408.cleaned[, 284 ])
gene5408.cleaned[,  285 ] <- as.numeric(gene5408.cleaned[, 285 ])
gene5408.cleaned[,  286 ] <- as.numeric(gene5408.cleaned[, 286 ])
gene5408.cleaned[,  287 ] <- as.numeric(gene5408.cleaned[, 287 ])
gene5408.cleaned[,  288 ] <- as.numeric(gene5408.cleaned[, 288 ])
gene5408.cleaned[,  289 ] <- as.numeric(gene5408.cleaned[, 289 ])
gene5408.cleaned[,  290 ] <- as.numeric(gene5408.cleaned[, 290 ])
gene5408.cleaned[,  291 ] <- as.numeric(gene5408.cleaned[, 291 ])
gene5408.cleaned[,  292 ] <- as.numeric(gene5408.cleaned[, 292 ])
gene5408.cleaned[,  293 ] <- as.numeric(gene5408.cleaned[, 293 ])
gene5408.cleaned[,  294 ] <- as.numeric(gene5408.cleaned[, 294 ])
gene5408.cleaned[,  295 ] <- as.numeric(gene5408.cleaned[, 295 ])
gene5408.cleaned[,  296 ] <- as.numeric(gene5408.cleaned[, 296 ])
gene5408.cleaned[,  297 ] <- as.numeric(gene5408.cleaned[, 297 ])
gene5408.cleaned[,  298 ] <- as.numeric(gene5408.cleaned[, 298 ])
gene5408.cleaned[,  299 ] <- as.numeric(gene5408.cleaned[, 299 ])
gene5408.cleaned[,  300 ] <- as.numeric(gene5408.cleaned[, 300 ])
gene5408.cleaned[,  301 ] <- as.numeric(gene5408.cleaned[, 301 ])
gene5408.cleaned[,  302 ] <- as.numeric(gene5408.cleaned[, 302 ])
gene5408.cleaned[,  303 ] <- as.numeric(gene5408.cleaned[, 303 ])
gene5408.cleaned[,  304 ] <- as.numeric(gene5408.cleaned[, 304 ])
gene5408.cleaned[,  305 ] <- as.numeric(gene5408.cleaned[, 305 ])
gene5408.cleaned[,  306 ] <- as.numeric(gene5408.cleaned[, 306 ])
gene5408.cleaned[,  307 ] <- as.numeric(gene5408.cleaned[, 307 ])
gene5408.cleaned[,  308 ] <- as.numeric(gene5408.cleaned[, 308 ])
gene5408.cleaned[,  309 ] <- as.numeric(gene5408.cleaned[, 309 ])
gene5408.cleaned[,  310 ] <- as.numeric(gene5408.cleaned[, 310 ])
gene5408.cleaned[,  311 ] <- as.numeric(gene5408.cleaned[, 311 ])
gene5408.cleaned[,  312 ] <- as.numeric(gene5408.cleaned[, 312 ])
gene5408.cleaned[,  313 ] <- as.numeric(gene5408.cleaned[, 313 ])
gene5408.cleaned[,  314 ] <- as.numeric(gene5408.cleaned[, 314 ])
gene5408.cleaned[,  315 ] <- as.numeric(gene5408.cleaned[, 315 ])
gene5408.cleaned[,  316 ] <- as.numeric(gene5408.cleaned[, 316 ])
gene5408.cleaned[,  317 ] <- as.numeric(gene5408.cleaned[, 317 ])
gene5408.cleaned[,  318 ] <- as.numeric(gene5408.cleaned[, 318 ])
gene5408.cleaned[,  319 ] <- as.numeric(gene5408.cleaned[, 319 ])
gene5408.cleaned[,  320 ] <- as.numeric(gene5408.cleaned[, 320 ])
gene5408.cleaned[,  321 ] <- as.numeric(gene5408.cleaned[, 321 ])
gene5408.cleaned[,  322 ] <- as.numeric(gene5408.cleaned[, 322 ])
gene5408.cleaned[,  323 ] <- as.numeric(gene5408.cleaned[, 323 ])
gene5408.cleaned[,  324 ] <- as.numeric(gene5408.cleaned[, 324 ])
gene5408.cleaned[,  325 ] <- as.numeric(gene5408.cleaned[, 325 ])
gene5408.cleaned[,  326 ] <- as.numeric(gene5408.cleaned[, 326 ])
gene5408.cleaned[,  327 ] <- as.numeric(gene5408.cleaned[, 327 ])
gene5408.cleaned[,  328 ] <- as.numeric(gene5408.cleaned[, 328 ])
gene5408.cleaned[,  329 ] <- as.numeric(gene5408.cleaned[, 329 ])
gene5408.cleaned[,  330 ] <- as.numeric(gene5408.cleaned[, 330 ])
gene5408.cleaned[,  331 ] <- as.numeric(gene5408.cleaned[, 331 ])
gene5408.cleaned[,  332 ] <- as.numeric(gene5408.cleaned[, 332 ])
gene5408.cleaned[,  333 ] <- as.numeric(gene5408.cleaned[, 333 ])
gene5408.cleaned[,  334 ] <- as.numeric(gene5408.cleaned[, 334 ])
gene5408.cleaned[,  335 ] <- as.numeric(gene5408.cleaned[, 335 ])
gene5408.cleaned[,  336 ] <- as.numeric(gene5408.cleaned[, 336 ])
gene5408.cleaned[,  337 ] <- as.numeric(gene5408.cleaned[, 337 ])
gene5408.cleaned[,  338 ] <- as.numeric(gene5408.cleaned[, 338 ])
gene5408.cleaned[,  339 ] <- as.numeric(gene5408.cleaned[, 339 ])
gene5408.cleaned[,  340 ] <- as.numeric(gene5408.cleaned[, 340 ])
gene5408.cleaned[,  341 ] <- as.numeric(gene5408.cleaned[, 341 ])
gene5408.cleaned[,  342 ] <- as.numeric(gene5408.cleaned[, 342 ])
gene5408.cleaned[,  343 ] <- as.numeric(gene5408.cleaned[, 343 ])
gene5408.cleaned[,  344 ] <- as.numeric(gene5408.cleaned[, 344 ])
gene5408.cleaned[,  345 ] <- as.numeric(gene5408.cleaned[, 345 ])
gene5408.cleaned[,  346 ] <- as.numeric(gene5408.cleaned[, 346 ])
gene5408.cleaned[,  347 ] <- as.numeric(gene5408.cleaned[, 347 ])
gene5408.cleaned[,  348 ] <- as.numeric(gene5408.cleaned[, 348 ])
gene5408.cleaned[,  349 ] <- as.numeric(gene5408.cleaned[, 349 ])
gene5408.cleaned[,  350 ] <- as.numeric(gene5408.cleaned[, 350 ])
gene5408.cleaned[,  351 ] <- as.numeric(gene5408.cleaned[, 351 ])
gene5408.cleaned[,  352 ] <- as.numeric(gene5408.cleaned[, 352 ])
gene5408.cleaned[,  353 ] <- as.numeric(gene5408.cleaned[, 353 ])
gene5408.cleaned[,  354 ] <- as.numeric(gene5408.cleaned[, 354 ])
gene5408.cleaned[,  355 ] <- as.numeric(gene5408.cleaned[, 355 ])
gene5408.cleaned[,  356 ] <- as.numeric(gene5408.cleaned[, 356 ])
gene5408.cleaned[,  357 ] <- as.numeric(gene5408.cleaned[, 357 ])
gene5408.cleaned[,  358 ] <- as.numeric(gene5408.cleaned[, 358 ])
gene5408.cleaned[,  359 ] <- as.numeric(gene5408.cleaned[, 359 ])
gene5408.cleaned[,  360 ] <- as.numeric(gene5408.cleaned[, 360 ])
gene5408.cleaned[,  361 ] <- as.numeric(gene5408.cleaned[, 361 ])
gene5408.cleaned[,  362 ] <- as.numeric(gene5408.cleaned[, 362 ])
gene5408.cleaned[,  363 ] <- as.numeric(gene5408.cleaned[, 363 ])
gene5408.cleaned[,  364 ] <- as.numeric(gene5408.cleaned[, 364 ])
gene5408.cleaned[,  365 ] <- as.numeric(gene5408.cleaned[, 365 ])
gene5408.cleaned[,  366 ] <- as.numeric(gene5408.cleaned[, 366 ])
gene5408.cleaned[,  367 ] <- as.numeric(gene5408.cleaned[, 367 ])
gene5408.cleaned[,  368 ] <- as.numeric(gene5408.cleaned[, 368 ])
gene5408.cleaned[,  369 ] <- as.numeric(gene5408.cleaned[, 369 ])
gene5408.cleaned[,  370 ] <- as.numeric(gene5408.cleaned[, 370 ])
gene5408.cleaned[,  371 ] <- as.numeric(gene5408.cleaned[, 371 ])
gene5408.cleaned[,  372 ] <- as.numeric(gene5408.cleaned[, 372 ])
gene5408.cleaned[,  373 ] <- as.numeric(gene5408.cleaned[, 373 ])
gene5408.cleaned[,  374 ] <- as.numeric(gene5408.cleaned[, 374 ])
gene5408.cleaned[,  375 ] <- as.numeric(gene5408.cleaned[, 375 ])
gene5408.cleaned[,  376 ] <- as.numeric(gene5408.cleaned[, 376 ])
gene5408.cleaned[,  377 ] <- as.numeric(gene5408.cleaned[, 377 ])
gene5408.cleaned[,  378 ] <- as.numeric(gene5408.cleaned[, 378 ])
gene5408.cleaned[,  379 ] <- as.numeric(gene5408.cleaned[, 379 ])
gene5408.cleaned[,  380 ] <- as.numeric(gene5408.cleaned[, 380 ])
gene5408.cleaned[,  381 ] <- as.numeric(gene5408.cleaned[, 381 ])
gene5408.cleaned[,  382 ] <- as.numeric(gene5408.cleaned[, 382 ])
gene5408.cleaned[,  383 ] <- as.numeric(gene5408.cleaned[, 383 ])
gene5408.cleaned[,  384 ] <- as.numeric(gene5408.cleaned[, 384 ])
gene5408.cleaned[,  385 ] <- as.numeric(gene5408.cleaned[, 385 ])
gene5408.cleaned[,  386 ] <- as.numeric(gene5408.cleaned[, 386 ])
gene5408.cleaned[,  387 ] <- as.numeric(gene5408.cleaned[, 387 ])
gene5408.cleaned[,  388 ] <- as.numeric(gene5408.cleaned[, 388 ])
gene5408.cleaned[,  389 ] <- as.numeric(gene5408.cleaned[, 389 ])
gene5408.cleaned[,  390 ] <- as.numeric(gene5408.cleaned[, 390 ])
gene5408.cleaned[,  391 ] <- as.numeric(gene5408.cleaned[, 391 ])
gene5408.cleaned[,  392 ] <- as.numeric(gene5408.cleaned[, 392 ])
gene5408.cleaned[,  393 ] <- as.numeric(gene5408.cleaned[, 393 ])
gene5408.cleaned[,  394 ] <- as.numeric(gene5408.cleaned[, 394 ])
gene5408.cleaned[,  395 ] <- as.numeric(gene5408.cleaned[, 395 ])
gene5408.cleaned[,  396 ] <- as.numeric(gene5408.cleaned[, 396 ])
gene5408.cleaned[,  397 ] <- as.numeric(gene5408.cleaned[, 397 ])
gene5408.cleaned[,  398 ] <- as.numeric(gene5408.cleaned[, 398 ])
gene5408.cleaned[,  399 ] <- as.numeric(gene5408.cleaned[, 399 ])
gene5408.cleaned[,  400 ] <- as.numeric(gene5408.cleaned[, 400 ])
gene5408.cleaned[,  401 ] <- as.numeric(gene5408.cleaned[, 401 ])
gene5408.cleaned[,  402 ] <- as.numeric(gene5408.cleaned[, 402 ])
gene5408.cleaned[,  403 ] <- as.numeric(gene5408.cleaned[, 403 ])
gene5408.cleaned[,  404 ] <- as.numeric(gene5408.cleaned[, 404 ])
gene5408.cleaned[,  405 ] <- as.numeric(gene5408.cleaned[, 405 ])
gene5408.cleaned[,  406 ] <- as.numeric(gene5408.cleaned[, 406 ])
gene5408.cleaned[,  407 ] <- as.numeric(gene5408.cleaned[, 407 ])
gene5408.cleaned[,  408 ] <- as.numeric(gene5408.cleaned[, 408 ])
gene5408.cleaned[,  409 ] <- as.numeric(gene5408.cleaned[, 409 ])
gene5408.cleaned[,  410 ] <- as.numeric(gene5408.cleaned[, 410 ])
gene5408.cleaned[,  411 ] <- as.numeric(gene5408.cleaned[, 411 ])
gene5408.cleaned[,  412 ] <- as.numeric(gene5408.cleaned[, 412 ])
gene5408.cleaned[,  413 ] <- as.numeric(gene5408.cleaned[, 413 ])
gene5408.cleaned[,  414 ] <- as.numeric(gene5408.cleaned[, 414 ])
gene5408.cleaned[,  415 ] <- as.numeric(gene5408.cleaned[, 415 ])
gene5408.cleaned[,  416 ] <- as.numeric(gene5408.cleaned[, 416 ])
gene5408.cleaned[,  417 ] <- as.numeric(gene5408.cleaned[, 417 ])
gene5408.cleaned[,  418 ] <- as.numeric(gene5408.cleaned[, 418 ])
gene5408.cleaned[,  419 ] <- as.numeric(gene5408.cleaned[, 419 ])
gene5408.cleaned[,  420 ] <- as.numeric(gene5408.cleaned[, 420 ])
gene5408.cleaned[,  421 ] <- as.numeric(gene5408.cleaned[, 421 ])
gene5408.cleaned[,  422 ] <- as.numeric(gene5408.cleaned[, 422 ])
gene5408.cleaned[,  423 ] <- as.numeric(gene5408.cleaned[, 423 ])
gene5408.cleaned[,  424 ] <- as.numeric(gene5408.cleaned[, 424 ])
gene5408.cleaned[,  425 ] <- as.numeric(gene5408.cleaned[, 425 ])
gene5408.cleaned[,  426 ] <- as.numeric(gene5408.cleaned[, 426 ])
gene5408.cleaned[,  427 ] <- as.numeric(gene5408.cleaned[, 427 ])
gene5408.cleaned[,  428 ] <- as.numeric(gene5408.cleaned[, 428 ])
gene5408.cleaned[,  429 ] <- as.numeric(gene5408.cleaned[, 429 ])
gene5408.cleaned[,  430 ] <- as.numeric(gene5408.cleaned[, 430 ])
gene5408.cleaned[,  431 ] <- as.numeric(gene5408.cleaned[, 431 ])
gene5408.cleaned[,  432 ] <- as.numeric(gene5408.cleaned[, 432 ])
gene5408.cleaned[,  433 ] <- as.numeric(gene5408.cleaned[, 433 ])
gene5408.cleaned[,  434 ] <- as.numeric(gene5408.cleaned[, 434 ])
gene5408.cleaned[,  435 ] <- as.numeric(gene5408.cleaned[, 435 ])
gene5408.cleaned[,  436 ] <- as.numeric(gene5408.cleaned[, 436 ])
gene5408.cleaned[,  437 ] <- as.numeric(gene5408.cleaned[, 437 ])
gene5408.cleaned[,  438 ] <- as.numeric(gene5408.cleaned[, 438 ])
gene5408.cleaned[,  439 ] <- as.numeric(gene5408.cleaned[, 439 ])
gene5408.cleaned[,  440 ] <- as.numeric(gene5408.cleaned[, 440 ])
gene5408.cleaned[,  441 ] <- as.numeric(gene5408.cleaned[, 441 ])
gene5408.cleaned[,  442 ] <- as.numeric(gene5408.cleaned[, 442 ])
gene5408.cleaned[,  443 ] <- as.numeric(gene5408.cleaned[, 443 ])
gene5408.cleaned[,  444 ] <- as.numeric(gene5408.cleaned[, 444 ])
gene5408.cleaned[,  445 ] <- as.numeric(gene5408.cleaned[, 445 ])
gene5408.cleaned[,  446 ] <- as.numeric(gene5408.cleaned[, 446 ])
gene5408.cleaned[,  447 ] <- as.numeric(gene5408.cleaned[, 447 ])
gene5408.cleaned[,  448 ] <- as.numeric(gene5408.cleaned[, 448 ])
gene5408.cleaned[,  449 ] <- as.numeric(gene5408.cleaned[, 449 ])
gene5408.cleaned[,  450 ] <- as.numeric(gene5408.cleaned[, 450 ])
gene5408.cleaned[,  451 ] <- as.numeric(gene5408.cleaned[, 451 ])
gene5408.cleaned[,  452 ] <- as.numeric(gene5408.cleaned[, 452 ])
gene5408.cleaned[,  453 ] <- as.numeric(gene5408.cleaned[, 453 ])
gene5408.cleaned[,  454 ] <- as.numeric(gene5408.cleaned[, 454 ])
gene5408.cleaned[,  455 ] <- as.numeric(gene5408.cleaned[, 455 ])
gene5408.cleaned[,  456 ] <- as.numeric(gene5408.cleaned[, 456 ])
gene5408.cleaned[,  457 ] <- as.numeric(gene5408.cleaned[, 457 ])
gene5408.cleaned[,  458 ] <- as.numeric(gene5408.cleaned[, 458 ])
gene5408.cleaned[,  459 ] <- as.numeric(gene5408.cleaned[, 459 ])
gene5408.cleaned[,  460 ] <- as.numeric(gene5408.cleaned[, 460 ])
gene5408.cleaned[,  461 ] <- as.numeric(gene5408.cleaned[, 461 ])
gene5408.cleaned[,  462 ] <- as.numeric(gene5408.cleaned[, 462 ])
gene5408.cleaned[,  463 ] <- as.numeric(gene5408.cleaned[, 463 ])
gene5408.cleaned[,  464 ] <- as.numeric(gene5408.cleaned[, 464 ])
gene5408.cleaned[,  465 ] <- as.numeric(gene5408.cleaned[, 465 ])
gene5408.cleaned[,  466 ] <- as.numeric(gene5408.cleaned[, 466 ])
gene5408.cleaned[,  467 ] <- as.numeric(gene5408.cleaned[, 467 ])
gene5408.cleaned[,  468 ] <- as.numeric(gene5408.cleaned[, 468 ])
gene5408.cleaned[,  469 ] <- as.numeric(gene5408.cleaned[, 469 ])
gene5408.cleaned[,  470 ] <- as.numeric(gene5408.cleaned[, 470 ])
gene5408.cleaned[,  471 ] <- as.numeric(gene5408.cleaned[, 471 ])
gene5408.cleaned[,  472 ] <- as.numeric(gene5408.cleaned[, 472 ])
gene5408.cleaned[,  473 ] <- as.numeric(gene5408.cleaned[, 473 ])
gene5408.cleaned[,  474 ] <- as.numeric(gene5408.cleaned[, 474 ])
gene5408.cleaned[,  475 ] <- as.numeric(gene5408.cleaned[, 475 ])
gene5408.cleaned[,  476 ] <- as.numeric(gene5408.cleaned[, 476 ])
gene5408.cleaned[,  477 ] <- as.numeric(gene5408.cleaned[, 477 ])
gene5408.cleaned[,  478 ] <- as.numeric(gene5408.cleaned[, 478 ])
gene5408.cleaned[,  479 ] <- as.numeric(gene5408.cleaned[, 479 ])
gene5408.cleaned[,  480 ] <- as.numeric(gene5408.cleaned[, 480 ])
gene5408.cleaned[,  481 ] <- as.numeric(gene5408.cleaned[, 481 ])
gene5408.cleaned[,  482 ] <- as.numeric(gene5408.cleaned[, 482 ])
gene5408.cleaned[,  483 ] <- as.numeric(gene5408.cleaned[, 483 ])
gene5408.cleaned[,  484 ] <- as.numeric(gene5408.cleaned[, 484 ])
gene5408.cleaned[,  485 ] <- as.numeric(gene5408.cleaned[, 485 ])
gene5408.cleaned[,  486 ] <- as.numeric(gene5408.cleaned[, 486 ])
gene5408.cleaned[,  487 ] <- as.numeric(gene5408.cleaned[, 487 ])
gene5408.cleaned[,  488 ] <- as.numeric(gene5408.cleaned[, 488 ])
gene5408.cleaned[,  489 ] <- as.numeric(gene5408.cleaned[, 489 ])
gene5408.cleaned[,  490 ] <- as.numeric(gene5408.cleaned[, 490 ])
gene5408.cleaned[,  491 ] <- as.numeric(gene5408.cleaned[, 491 ])
gene5408.cleaned[,  492 ] <- as.numeric(gene5408.cleaned[, 492 ])
gene5408.cleaned[,  493 ] <- as.numeric(gene5408.cleaned[, 493 ])
gene5408.cleaned[,  494 ] <- as.numeric(gene5408.cleaned[, 494 ])
gene5408.cleaned[,  495 ] <- as.numeric(gene5408.cleaned[, 495 ])
gene5408.cleaned[,  496 ] <- as.numeric(gene5408.cleaned[, 496 ])
gene5408.cleaned[,  497 ] <- as.numeric(gene5408.cleaned[, 497 ])
gene5408.cleaned[,  498 ] <- as.numeric(gene5408.cleaned[, 498 ])
gene5408.cleaned[,  499 ] <- as.numeric(gene5408.cleaned[, 499 ])
gene5408.cleaned[,  500 ] <- as.numeric(gene5408.cleaned[, 500 ])
gene5408.cleaned[,  501 ] <- as.numeric(gene5408.cleaned[, 501 ])
gene5408.cleaned[,  502 ] <- as.numeric(gene5408.cleaned[, 502 ])
gene5408.cleaned[,  503 ] <- as.numeric(gene5408.cleaned[, 503 ])
gene5408.cleaned[,  504 ] <- as.numeric(gene5408.cleaned[, 504 ])
gene5408.cleaned[,  505 ] <- as.numeric(gene5408.cleaned[, 505 ])
gene5408.cleaned[,  506 ] <- as.numeric(gene5408.cleaned[, 506 ])
gene5408.cleaned[,  507 ] <- as.numeric(gene5408.cleaned[, 507 ])
gene5408.cleaned[,  508 ] <- as.numeric(gene5408.cleaned[, 508 ])
gene5408.cleaned[,  509 ] <- as.numeric(gene5408.cleaned[, 509 ])
gene5408.cleaned[,  510 ] <- as.numeric(gene5408.cleaned[, 510 ])
gene5408.cleaned[,  511 ] <- as.numeric(gene5408.cleaned[, 511 ])
gene5408.cleaned[,  512 ] <- as.numeric(gene5408.cleaned[, 512 ])
gene5408.cleaned[,  513 ] <- as.numeric(gene5408.cleaned[, 513 ])
gene5408.cleaned[,  514 ] <- as.numeric(gene5408.cleaned[, 514 ])
gene5408.cleaned[,  515 ] <- as.numeric(gene5408.cleaned[, 515 ])
gene5408.cleaned[,  516 ] <- as.numeric(gene5408.cleaned[, 516 ])
gene5408.cleaned[,  517 ] <- as.numeric(gene5408.cleaned[, 517 ])
gene5408.cleaned[,  518 ] <- as.numeric(gene5408.cleaned[, 518 ])
gene5408.cleaned[,  519 ] <- as.numeric(gene5408.cleaned[, 519 ])
gene5408.cleaned[,  520 ] <- as.numeric(gene5408.cleaned[, 520 ])
gene5408.cleaned[,  521 ] <- as.numeric(gene5408.cleaned[, 521 ])
gene5408.cleaned[,  522 ] <- as.numeric(gene5408.cleaned[, 522 ])
gene5408.cleaned[,  523 ] <- as.numeric(gene5408.cleaned[, 523 ])
gene5408.cleaned[,  524 ] <- as.numeric(gene5408.cleaned[, 524 ])
gene5408.cleaned[,  525 ] <- as.numeric(gene5408.cleaned[, 525 ])
gene5408.cleaned[,  526 ] <- as.numeric(gene5408.cleaned[, 526 ])
gene5408.cleaned[,  527 ] <- as.numeric(gene5408.cleaned[, 527 ])
gene5408.cleaned[,  528 ] <- as.numeric(gene5408.cleaned[, 528 ])
gene5408.cleaned[,  529 ] <- as.numeric(gene5408.cleaned[, 529 ])
gene5408.cleaned[,  530 ] <- as.numeric(gene5408.cleaned[, 530 ])
gene5408.cleaned[,  531 ] <- as.numeric(gene5408.cleaned[, 531 ])
gene5408.cleaned[,  532 ] <- as.numeric(gene5408.cleaned[, 532 ])
gene5408.cleaned[,  533 ] <- as.numeric(gene5408.cleaned[, 533 ])
gene5408.cleaned[,  534 ] <- as.numeric(gene5408.cleaned[, 534 ])
gene5408.cleaned[,  535 ] <- as.numeric(gene5408.cleaned[, 535 ])
gene5408.cleaned[,  536 ] <- as.numeric(gene5408.cleaned[, 536 ])
gene5408.cleaned[,  537 ] <- as.numeric(gene5408.cleaned[, 537 ])
gene5408.cleaned[,  538 ] <- as.numeric(gene5408.cleaned[, 538 ])
gene5408.cleaned[,  539 ] <- as.numeric(gene5408.cleaned[, 539 ])
gene5408.cleaned[,  540 ] <- as.numeric(gene5408.cleaned[, 540 ])
gene5408.cleaned[,  541 ] <- as.numeric(gene5408.cleaned[, 541 ])
gene5408.cleaned[,  542 ] <- as.numeric(gene5408.cleaned[, 542 ])
gene5408.cleaned[,  543 ] <- as.numeric(gene5408.cleaned[, 543 ])
gene5408.cleaned[,  544 ] <- as.numeric(gene5408.cleaned[, 544 ])
gene5408.cleaned[,  545 ] <- as.numeric(gene5408.cleaned[, 545 ])
gene5408.cleaned[,  546 ] <- as.numeric(gene5408.cleaned[, 546 ])
gene5408.cleaned[,  547 ] <- as.numeric(gene5408.cleaned[, 547 ])
gene5408.cleaned[,  548 ] <- as.numeric(gene5408.cleaned[, 548 ])
gene5408.cleaned[,  549 ] <- as.numeric(gene5408.cleaned[, 549 ])
gene5408.cleaned[,  550 ] <- as.numeric(gene5408.cleaned[, 550 ])
gene5408.cleaned[,  551 ] <- as.numeric(gene5408.cleaned[, 551 ])
gene5408.cleaned[,  552 ] <- as.numeric(gene5408.cleaned[, 552 ])
gene5408.cleaned[,  553 ] <- as.numeric(gene5408.cleaned[, 553 ])
gene5408.cleaned[,  554 ] <- as.numeric(gene5408.cleaned[, 554 ])
gene5408.cleaned[,  555 ] <- as.numeric(gene5408.cleaned[, 555 ])
gene5408.cleaned[,  556 ] <- as.numeric(gene5408.cleaned[, 556 ])
gene5408.cleaned[,  557 ] <- as.numeric(gene5408.cleaned[, 557 ])
gene5408.cleaned[,  558 ] <- as.numeric(gene5408.cleaned[, 558 ])
gene5408.cleaned[,  559 ] <- as.numeric(gene5408.cleaned[, 559 ])
gene5408.cleaned[,  560 ] <- as.numeric(gene5408.cleaned[, 560 ])
gene5408.cleaned[,  561 ] <- as.numeric(gene5408.cleaned[, 561 ])
gene5408.cleaned[,  562 ] <- as.numeric(gene5408.cleaned[, 562 ])
gene5408.cleaned[,  563 ] <- as.numeric(gene5408.cleaned[, 563 ])
gene5408.cleaned[,  564 ] <- as.numeric(gene5408.cleaned[, 564 ])
gene5408.cleaned[,  565 ] <- as.numeric(gene5408.cleaned[, 565 ])
gene5408.cleaned[,  566 ] <- as.numeric(gene5408.cleaned[, 566 ])
gene5408.cleaned[,  567 ] <- as.numeric(gene5408.cleaned[, 567 ])
gene5408.cleaned[,  568 ] <- as.numeric(gene5408.cleaned[, 568 ])
gene5408.cleaned[,  569 ] <- as.numeric(gene5408.cleaned[, 569 ])
gene5408.cleaned[,  570 ] <- as.numeric(gene5408.cleaned[, 570 ])
gene5408.cleaned[,  571 ] <- as.numeric(gene5408.cleaned[, 571 ])
gene5408.cleaned[,  572 ] <- as.numeric(gene5408.cleaned[, 572 ])
gene5408.cleaned[,  573 ] <- as.numeric(gene5408.cleaned[, 573 ])
gene5408.cleaned[,  574 ] <- as.numeric(gene5408.cleaned[, 574 ])
gene5408.cleaned[,  575 ] <- as.numeric(gene5408.cleaned[, 575 ])
gene5408.cleaned[,  576 ] <- as.numeric(gene5408.cleaned[, 576 ])
gene5408.cleaned[,  577 ] <- as.numeric(gene5408.cleaned[, 577 ])
gene5408.cleaned[,  578 ] <- as.numeric(gene5408.cleaned[, 578 ])
gene5408.cleaned[,  579 ] <- as.numeric(gene5408.cleaned[, 579 ])
gene5408.cleaned[,  580 ] <- as.numeric(gene5408.cleaned[, 580 ])
gene5408.cleaned[,  581 ] <- as.numeric(gene5408.cleaned[, 581 ])
gene5408.cleaned[,  582 ] <- as.numeric(gene5408.cleaned[, 582 ])
gene5408.cleaned[,  583 ] <- as.numeric(gene5408.cleaned[, 583 ])
gene5408.cleaned[,  584 ] <- as.numeric(gene5408.cleaned[, 584 ])
gene5408.cleaned[,  585 ] <- as.numeric(gene5408.cleaned[, 585 ])
gene5408.cleaned[,  586 ] <- as.numeric(gene5408.cleaned[, 586 ])
gene5408.cleaned[,  587 ] <- as.numeric(gene5408.cleaned[, 587 ])
gene5408.cleaned[,  588 ] <- as.numeric(gene5408.cleaned[, 588 ])
gene5408.cleaned[,  589 ] <- as.numeric(gene5408.cleaned[, 589 ])
gene5408.cleaned[,  590 ] <- as.numeric(gene5408.cleaned[, 590 ])
gene5408.cleaned[,  591 ] <- as.numeric(gene5408.cleaned[, 591 ])
gene5408.cleaned[,  592 ] <- as.numeric(gene5408.cleaned[, 592 ])
gene5408.cleaned[,  593 ] <- as.numeric(gene5408.cleaned[, 593 ])
gene5408.cleaned[,  594 ] <- as.numeric(gene5408.cleaned[, 594 ])
gene5408.cleaned[,  595 ] <- as.numeric(gene5408.cleaned[, 595 ])
gene5408.cleaned[,  596 ] <- as.numeric(gene5408.cleaned[, 596 ])
gene5408.cleaned[,  597 ] <- as.numeric(gene5408.cleaned[, 597 ])
gene5408.cleaned[,  598 ] <- as.numeric(gene5408.cleaned[, 598 ])
gene5408.cleaned[,  599 ] <- as.numeric(gene5408.cleaned[, 599 ])
gene5408.cleaned[,  600 ] <- as.numeric(gene5408.cleaned[, 600 ])
gene5408.cleaned[,  601 ] <- as.numeric(gene5408.cleaned[, 601 ])
gene5408.cleaned[,  602 ] <- as.numeric(gene5408.cleaned[, 602 ])
gene5408.cleaned[,  603 ] <- as.numeric(gene5408.cleaned[, 603 ])
gene5408.cleaned[,  604 ] <- as.numeric(gene5408.cleaned[, 604 ])
gene5408.cleaned[,  605 ] <- as.numeric(gene5408.cleaned[, 605 ])
gene5408.cleaned[,  606 ] <- as.numeric(gene5408.cleaned[, 606 ])
gene5408.cleaned[,  607 ] <- as.numeric(gene5408.cleaned[, 607 ])
gene5408.cleaned[,  608 ] <- as.numeric(gene5408.cleaned[, 608 ])
gene5408.cleaned[,  609 ] <- as.numeric(gene5408.cleaned[, 609 ])
gene5408.cleaned[,  610 ] <- as.numeric(gene5408.cleaned[, 610 ])
gene5408.cleaned[,  611 ] <- as.numeric(gene5408.cleaned[, 611 ])
gene5408.cleaned[,  612 ] <- as.numeric(gene5408.cleaned[, 612 ])
gene5408.cleaned[,  613 ] <- as.numeric(gene5408.cleaned[, 613 ])
gene5408.cleaned[,  614 ] <- as.numeric(gene5408.cleaned[, 614 ])
gene5408.cleaned[,  615 ] <- as.numeric(gene5408.cleaned[, 615 ])
gene5408.cleaned[,  616 ] <- as.numeric(gene5408.cleaned[, 616 ])
gene5408.cleaned[,  617 ] <- as.numeric(gene5408.cleaned[, 617 ])
gene5408.cleaned[,  618 ] <- as.numeric(gene5408.cleaned[, 618 ])
gene5408.cleaned[,  619 ] <- as.numeric(gene5408.cleaned[, 619 ])
gene5408.cleaned[,  620 ] <- as.numeric(gene5408.cleaned[, 620 ])
gene5408.cleaned[,  621 ] <- as.numeric(gene5408.cleaned[, 621 ])
gene5408.cleaned[,  622 ] <- as.numeric(gene5408.cleaned[, 622 ])
gene5408.cleaned[,  623 ] <- as.numeric(gene5408.cleaned[, 623 ])
gene5408.cleaned[,  624 ] <- as.numeric(gene5408.cleaned[, 624 ])
gene5408.cleaned[,  625 ] <- as.numeric(gene5408.cleaned[, 625 ])
gene5408.cleaned[,  626 ] <- as.numeric(gene5408.cleaned[, 626 ])
gene5408.cleaned[,  627 ] <- as.numeric(gene5408.cleaned[, 627 ])
gene5408.cleaned[,  628 ] <- as.numeric(gene5408.cleaned[, 628 ])
gene5408.cleaned[,  629 ] <- as.numeric(gene5408.cleaned[, 629 ])
gene5408.cleaned[,  630 ] <- as.numeric(gene5408.cleaned[, 630 ])
gene5408.cleaned[,  631 ] <- as.numeric(gene5408.cleaned[, 631 ])
gene5408.cleaned[,  632 ] <- as.numeric(gene5408.cleaned[, 632 ])
gene5408.cleaned[,  633 ] <- as.numeric(gene5408.cleaned[, 633 ])
gene5408.cleaned[,  634 ] <- as.numeric(gene5408.cleaned[, 634 ])
gene5408.cleaned[,  635 ] <- as.numeric(gene5408.cleaned[, 635 ])
gene5408.cleaned[,  636 ] <- as.numeric(gene5408.cleaned[, 636 ])
gene5408.cleaned[,  637 ] <- as.numeric(gene5408.cleaned[, 637 ])
gene5408.cleaned[,  638 ] <- as.numeric(gene5408.cleaned[, 638 ])
gene5408.cleaned[,  639 ] <- as.numeric(gene5408.cleaned[, 639 ])
gene5408.cleaned[,  640 ] <- as.numeric(gene5408.cleaned[, 640 ])
gene5408.cleaned[,  641 ] <- as.numeric(gene5408.cleaned[, 641 ])
gene5408.cleaned[,  642 ] <- as.numeric(gene5408.cleaned[, 642 ])
gene5408.cleaned[,  643 ] <- as.numeric(gene5408.cleaned[, 643 ])
gene5408.cleaned[,  644 ] <- as.numeric(gene5408.cleaned[, 644 ])
gene5408.cleaned[,  645 ] <- as.numeric(gene5408.cleaned[, 645 ])
gene5408.cleaned[,  646 ] <- as.numeric(gene5408.cleaned[, 646 ])
gene5408.cleaned[,  647 ] <- as.numeric(gene5408.cleaned[, 647 ])
gene5408.cleaned[,  648 ] <- as.numeric(gene5408.cleaned[, 648 ])
gene5408.cleaned[,  649 ] <- as.numeric(gene5408.cleaned[, 649 ])
gene5408.cleaned[,  650 ] <- as.numeric(gene5408.cleaned[, 650 ])
gene5408.cleaned[,  651 ] <- as.numeric(gene5408.cleaned[, 651 ])
gene5408.cleaned[,  652 ] <- as.numeric(gene5408.cleaned[, 652 ])
gene5408.cleaned[,  653 ] <- as.numeric(gene5408.cleaned[, 653 ])
gene5408.cleaned[,  654 ] <- as.numeric(gene5408.cleaned[, 654 ])
gene5408.cleaned[,  655 ] <- as.numeric(gene5408.cleaned[, 655 ])
gene5408.cleaned[,  656 ] <- as.numeric(gene5408.cleaned[, 656 ])
gene5408.cleaned[,  657 ] <- as.numeric(gene5408.cleaned[, 657 ])
gene5408.cleaned[,  658 ] <- as.numeric(gene5408.cleaned[, 658 ])
gene5408.cleaned[,  659 ] <- as.numeric(gene5408.cleaned[, 659 ])
gene5408.cleaned[,  660 ] <- as.numeric(gene5408.cleaned[, 660 ])
gene5408.cleaned[,  661 ] <- as.numeric(gene5408.cleaned[, 661 ])
gene5408.cleaned[,  662 ] <- as.numeric(gene5408.cleaned[, 662 ])
gene5408.cleaned[,  663 ] <- as.numeric(gene5408.cleaned[, 663 ])
gene5408.cleaned[,  664 ] <- as.numeric(gene5408.cleaned[, 664 ])
gene5408.cleaned[,  665 ] <- as.numeric(gene5408.cleaned[, 665 ])
gene5408.cleaned[,  666 ] <- as.numeric(gene5408.cleaned[, 666 ])
gene5408.cleaned[,  667 ] <- as.numeric(gene5408.cleaned[, 667 ])
gene5408.cleaned[,  668 ] <- as.numeric(gene5408.cleaned[, 668 ])
gene5408.cleaned[,  669 ] <- as.numeric(gene5408.cleaned[, 669 ])
gene5408.cleaned[,  670 ] <- as.numeric(gene5408.cleaned[, 670 ])
gene5408.cleaned[,  671 ] <- as.numeric(gene5408.cleaned[, 671 ])
gene5408.cleaned[,  672 ] <- as.numeric(gene5408.cleaned[, 672 ])
gene5408.cleaned[,  673 ] <- as.numeric(gene5408.cleaned[, 673 ])
gene5408.cleaned[,  674 ] <- as.numeric(gene5408.cleaned[, 674 ])
gene5408.cleaned[,  675 ] <- as.numeric(gene5408.cleaned[, 675 ])
gene5408.cleaned[,  676 ] <- as.numeric(gene5408.cleaned[, 676 ])
gene5408.cleaned[,  677 ] <- as.numeric(gene5408.cleaned[, 677 ])
gene5408.cleaned[,  678 ] <- as.numeric(gene5408.cleaned[, 678 ])
gene5408.cleaned[,  679 ] <- as.numeric(gene5408.cleaned[, 679 ])
gene5408.cleaned[,  680 ] <- as.numeric(gene5408.cleaned[, 680 ])
gene5408.cleaned[,  681 ] <- as.numeric(gene5408.cleaned[, 681 ])
gene5408.cleaned[,  682 ] <- as.numeric(gene5408.cleaned[, 682 ])
gene5408.cleaned[,  683 ] <- as.numeric(gene5408.cleaned[, 683 ])
gene5408.cleaned[,  684 ] <- as.numeric(gene5408.cleaned[, 684 ])
gene5408.cleaned[,  685 ] <- as.numeric(gene5408.cleaned[, 685 ])
gene5408.cleaned[,  686 ] <- as.numeric(gene5408.cleaned[, 686 ])
gene5408.cleaned[,  687 ] <- as.numeric(gene5408.cleaned[, 687 ])
gene5408.cleaned[,  688 ] <- as.numeric(gene5408.cleaned[, 688 ])
gene5408.cleaned[,  689 ] <- as.numeric(gene5408.cleaned[, 689 ])
gene5408.cleaned[,  690 ] <- as.numeric(gene5408.cleaned[, 690 ])
gene5408.cleaned[,  691 ] <- as.numeric(gene5408.cleaned[, 691 ])
gene5408.cleaned[,  692 ] <- as.numeric(gene5408.cleaned[, 692 ])
gene5408.cleaned[,  693 ] <- as.numeric(gene5408.cleaned[, 693 ])
gene5408.cleaned[,  694 ] <- as.numeric(gene5408.cleaned[, 694 ])
gene5408.cleaned[,  695 ] <- as.numeric(gene5408.cleaned[, 695 ])
gene5408.cleaned[,  696 ] <- as.numeric(gene5408.cleaned[, 696 ])
gene5408.cleaned[,  697 ] <- as.numeric(gene5408.cleaned[, 697 ])
gene5408.cleaned[,  698 ] <- as.numeric(gene5408.cleaned[, 698 ])
gene5408.cleaned[,  699 ] <- as.numeric(gene5408.cleaned[, 699 ])
gene5408.cleaned[,  700 ] <- as.numeric(gene5408.cleaned[, 700 ])
gene5408.cleaned[,  701 ] <- as.numeric(gene5408.cleaned[, 701 ])
gene5408.cleaned[,  702 ] <- as.numeric(gene5408.cleaned[, 702 ])
gene5408.cleaned[,  703 ] <- as.numeric(gene5408.cleaned[, 703 ])
gene5408.cleaned[,  704 ] <- as.numeric(gene5408.cleaned[, 704 ])
gene5408.cleaned[,  705 ] <- as.numeric(gene5408.cleaned[, 705 ])
gene5408.cleaned[,  706 ] <- as.numeric(gene5408.cleaned[, 706 ])
gene5408.cleaned[,  707 ] <- as.numeric(gene5408.cleaned[, 707 ])
gene5408.cleaned[,  708 ] <- as.numeric(gene5408.cleaned[, 708 ])
gene5408.cleaned[,  709 ] <- as.numeric(gene5408.cleaned[, 709 ])
gene5408.cleaned[,  710 ] <- as.numeric(gene5408.cleaned[, 710 ])
gene5408.cleaned[,  711 ] <- as.numeric(gene5408.cleaned[, 711 ])
gene5408.cleaned[,  712 ] <- as.numeric(gene5408.cleaned[, 712 ])
gene5408.cleaned[,  713 ] <- as.numeric(gene5408.cleaned[, 713 ])
gene5408.cleaned[,  714 ] <- as.numeric(gene5408.cleaned[, 714 ])
gene5408.cleaned[,  715 ] <- as.numeric(gene5408.cleaned[, 715 ])
gene5408.cleaned[,  716 ] <- as.numeric(gene5408.cleaned[, 716 ])
gene5408.cleaned[,  717 ] <- as.numeric(gene5408.cleaned[, 717 ])
gene5408.cleaned[,  718 ] <- as.numeric(gene5408.cleaned[, 718 ])
gene5408.cleaned[,  719 ] <- as.numeric(gene5408.cleaned[, 719 ])
gene5408.cleaned[,  720 ] <- as.numeric(gene5408.cleaned[, 720 ])
gene5408.cleaned[,  721 ] <- as.numeric(gene5408.cleaned[, 721 ])
gene5408.cleaned[,  722 ] <- as.numeric(gene5408.cleaned[, 722 ])
gene5408.cleaned[,  723 ] <- as.numeric(gene5408.cleaned[, 723 ])
gene5408.cleaned[,  724 ] <- as.numeric(gene5408.cleaned[, 724 ])
gene5408.cleaned[,  725 ] <- as.numeric(gene5408.cleaned[, 725 ])
gene5408.cleaned[,  726 ] <- as.numeric(gene5408.cleaned[, 726 ])
gene5408.cleaned[,  727 ] <- as.numeric(gene5408.cleaned[, 727 ])
gene5408.cleaned[,  728 ] <- as.numeric(gene5408.cleaned[, 728 ])
gene5408.cleaned[,  729 ] <- as.numeric(gene5408.cleaned[, 729 ])
gene5408.cleaned[,  730 ] <- as.numeric(gene5408.cleaned[, 730 ])
gene5408.cleaned[,  731 ] <- as.numeric(gene5408.cleaned[, 731 ])
gene5408.cleaned[,  732 ] <- as.numeric(gene5408.cleaned[, 732 ])
gene5408.cleaned[,  733 ] <- as.numeric(gene5408.cleaned[, 733 ])
gene5408.cleaned[,  734 ] <- as.numeric(gene5408.cleaned[, 734 ])
gene5408.cleaned[,  735 ] <- as.numeric(gene5408.cleaned[, 735 ])
gene5408.cleaned[,  736 ] <- as.numeric(gene5408.cleaned[, 736 ])
gene5408.cleaned[,  737 ] <- as.numeric(gene5408.cleaned[, 737 ])
gene5408.cleaned[,  738 ] <- as.numeric(gene5408.cleaned[, 738 ])
gene5408.cleaned[,  739 ] <- as.numeric(gene5408.cleaned[, 739 ])
gene5408.cleaned[,  740 ] <- as.numeric(gene5408.cleaned[, 740 ])
gene5408.cleaned[,  741 ] <- as.numeric(gene5408.cleaned[, 741 ])
gene5408.cleaned[,  742 ] <- as.numeric(gene5408.cleaned[, 742 ])
gene5408.cleaned[,  743 ] <- as.numeric(gene5408.cleaned[, 743 ])
gene5408.cleaned[,  744 ] <- as.numeric(gene5408.cleaned[, 744 ])
gene5408.cleaned[,  745 ] <- as.numeric(gene5408.cleaned[, 745 ])
gene5408.cleaned[,  746 ] <- as.numeric(gene5408.cleaned[, 746 ])
gene5408.cleaned[,  747 ] <- as.numeric(gene5408.cleaned[, 747 ])
gene5408.cleaned[,  748 ] <- as.numeric(gene5408.cleaned[, 748 ])
gene5408.cleaned[,  749 ] <- as.numeric(gene5408.cleaned[, 749 ])
gene5408.cleaned[,  750 ] <- as.numeric(gene5408.cleaned[, 750 ])
gene5408.cleaned[,  751 ] <- as.numeric(gene5408.cleaned[, 751 ])
gene5408.cleaned[,  752 ] <- as.numeric(gene5408.cleaned[, 752 ])
gene5408.cleaned[,  753 ] <- as.numeric(gene5408.cleaned[, 753 ])
gene5408.cleaned[,  754 ] <- as.numeric(gene5408.cleaned[, 754 ])
gene5408.cleaned[,  755 ] <- as.numeric(gene5408.cleaned[, 755 ])
gene5408.cleaned[,  756 ] <- as.numeric(gene5408.cleaned[, 756 ])
gene5408.cleaned[,  757 ] <- as.numeric(gene5408.cleaned[, 757 ])
gene5408.cleaned[,  758 ] <- as.numeric(gene5408.cleaned[, 758 ])
gene5408.cleaned[,  759 ] <- as.numeric(gene5408.cleaned[, 759 ])
gene5408.cleaned[,  760 ] <- as.numeric(gene5408.cleaned[, 760 ])
gene5408.cleaned[,  761 ] <- as.numeric(gene5408.cleaned[, 761 ])
gene5408.cleaned[,  762 ] <- as.numeric(gene5408.cleaned[, 762 ])
gene5408.cleaned[,  763 ] <- as.numeric(gene5408.cleaned[, 763 ])
gene5408.cleaned[,  764 ] <- as.numeric(gene5408.cleaned[, 764 ])
gene5408.cleaned[,  765 ] <- as.numeric(gene5408.cleaned[, 765 ])
gene5408.cleaned[,  766 ] <- as.numeric(gene5408.cleaned[, 766 ])
gene5408.cleaned[,  767 ] <- as.numeric(gene5408.cleaned[, 767 ])
gene5408.cleaned[,  768 ] <- as.numeric(gene5408.cleaned[, 768 ])
gene5408.cleaned[,  769 ] <- as.numeric(gene5408.cleaned[, 769 ])
gene5408.cleaned[,  770 ] <- as.numeric(gene5408.cleaned[, 770 ])
gene5408.cleaned[,  771 ] <- as.numeric(gene5408.cleaned[, 771 ])
gene5408.cleaned[,  772 ] <- as.numeric(gene5408.cleaned[, 772 ])
gene5408.cleaned[,  773 ] <- as.numeric(gene5408.cleaned[, 773 ])
gene5408.cleaned[,  774 ] <- as.numeric(gene5408.cleaned[, 774 ])
gene5408.cleaned[,  775 ] <- as.numeric(gene5408.cleaned[, 775 ])
gene5408.cleaned[,  776 ] <- as.numeric(gene5408.cleaned[, 776 ])
gene5408.cleaned[,  777 ] <- as.numeric(gene5408.cleaned[, 777 ])
gene5408.cleaned[,  778 ] <- as.numeric(gene5408.cleaned[, 778 ])
gene5408.cleaned[,  779 ] <- as.numeric(gene5408.cleaned[, 779 ])
gene5408.cleaned[,  780 ] <- as.numeric(gene5408.cleaned[, 780 ])
gene5408.cleaned[,  781 ] <- as.numeric(gene5408.cleaned[, 781 ])
gene5408.cleaned[,  782 ] <- as.numeric(gene5408.cleaned[, 782 ])
gene5408.cleaned[,  783 ] <- as.numeric(gene5408.cleaned[, 783 ])
gene5408.cleaned[,  784 ] <- as.numeric(gene5408.cleaned[, 784 ])
gene5408.cleaned[,  785 ] <- as.numeric(gene5408.cleaned[, 785 ])
gene5408.cleaned[,  786 ] <- as.numeric(gene5408.cleaned[, 786 ])
gene5408.cleaned[,  787 ] <- as.numeric(gene5408.cleaned[, 787 ])
gene5408.cleaned[,  788 ] <- as.numeric(gene5408.cleaned[, 788 ])
gene5408.cleaned[,  789 ] <- as.numeric(gene5408.cleaned[, 789 ])
gene5408.cleaned[,  790 ] <- as.numeric(gene5408.cleaned[, 790 ])
gene5408.cleaned[,  791 ] <- as.numeric(gene5408.cleaned[, 791 ])
gene5408.cleaned[,  792 ] <- as.numeric(gene5408.cleaned[, 792 ])
gene5408.cleaned[,  793 ] <- as.numeric(gene5408.cleaned[, 793 ])
gene5408.cleaned[,  794 ] <- as.numeric(gene5408.cleaned[, 794 ])
gene5408.cleaned[,  795 ] <- as.numeric(gene5408.cleaned[, 795 ])
gene5408.cleaned[,  796 ] <- as.numeric(gene5408.cleaned[, 796 ])
gene5408.cleaned[,  797 ] <- as.numeric(gene5408.cleaned[, 797 ])
gene5408.cleaned[,  798 ] <- as.numeric(gene5408.cleaned[, 798 ])
gene5408.cleaned[,  799 ] <- as.numeric(gene5408.cleaned[, 799 ])
gene5408.cleaned[,  800 ] <- as.numeric(gene5408.cleaned[, 800 ])
gene5408.cleaned[,  801 ] <- as.numeric(gene5408.cleaned[, 801 ])
gene5408.cleaned[,  802 ] <- as.numeric(gene5408.cleaned[, 802 ])
gene5408.cleaned[,  803 ] <- as.numeric(gene5408.cleaned[, 803 ])
gene5408.cleaned[,  804 ] <- as.numeric(gene5408.cleaned[, 804 ])
gene5408.cleaned[,  805 ] <- as.numeric(gene5408.cleaned[, 805 ])
gene5408.cleaned[,  806 ] <- as.numeric(gene5408.cleaned[, 806 ])
gene5408.cleaned[,  807 ] <- as.numeric(gene5408.cleaned[, 807 ])
gene5408.cleaned[,  808 ] <- as.numeric(gene5408.cleaned[, 808 ])
gene5408.cleaned[,  809 ] <- as.numeric(gene5408.cleaned[, 809 ])
gene5408.cleaned[,  810 ] <- as.numeric(gene5408.cleaned[, 810 ])
gene5408.cleaned[,  811 ] <- as.numeric(gene5408.cleaned[, 811 ])
gene5408.cleaned[,  812 ] <- as.numeric(gene5408.cleaned[, 812 ])
gene5408.cleaned[,  813 ] <- as.numeric(gene5408.cleaned[, 813 ])
gene5408.cleaned[,  814 ] <- as.numeric(gene5408.cleaned[, 814 ])
gene5408.cleaned[,  815 ] <- as.numeric(gene5408.cleaned[, 815 ])
gene5408.cleaned[,  816 ] <- as.numeric(gene5408.cleaned[, 816 ])
gene5408.cleaned[,  817 ] <- as.numeric(gene5408.cleaned[, 817 ])
gene5408.cleaned[,  818 ] <- as.numeric(gene5408.cleaned[, 818 ])
gene5408.cleaned[,  819 ] <- as.numeric(gene5408.cleaned[, 819 ])
gene5408.cleaned[,  820 ] <- as.numeric(gene5408.cleaned[, 820 ])
gene5408.cleaned[,  821 ] <- as.numeric(gene5408.cleaned[, 821 ])
gene5408.cleaned[,  822 ] <- as.numeric(gene5408.cleaned[, 822 ])
gene5408.cleaned[,  823 ] <- as.numeric(gene5408.cleaned[, 823 ])
gene5408.cleaned[,  824 ] <- as.numeric(gene5408.cleaned[, 824 ])
gene5408.cleaned[,  825 ] <- as.numeric(gene5408.cleaned[, 825 ])
gene5408.cleaned[,  826 ] <- as.numeric(gene5408.cleaned[, 826 ])
gene5408.cleaned[,  827 ] <- as.numeric(gene5408.cleaned[, 827 ])
gene5408.cleaned[,  828 ] <- as.numeric(gene5408.cleaned[, 828 ])
gene5408.cleaned[,  829 ] <- as.numeric(gene5408.cleaned[, 829 ])
gene5408.cleaned[,  830 ] <- as.numeric(gene5408.cleaned[, 830 ])
gene5408.cleaned[,  831 ] <- as.numeric(gene5408.cleaned[, 831 ])
gene5408.cleaned[,  832 ] <- as.numeric(gene5408.cleaned[, 832 ])
gene5408.cleaned[,  833 ] <- as.numeric(gene5408.cleaned[, 833 ])
gene5408.cleaned[,  834 ] <- as.numeric(gene5408.cleaned[, 834 ])
gene5408.cleaned[,  835 ] <- as.numeric(gene5408.cleaned[, 835 ])
gene5408.cleaned[,  836 ] <- as.numeric(gene5408.cleaned[, 836 ])
gene5408.cleaned[,  837 ] <- as.numeric(gene5408.cleaned[, 837 ])
gene5408.cleaned[,  838 ] <- as.numeric(gene5408.cleaned[, 838 ])
gene5408.cleaned[,  839 ] <- as.numeric(gene5408.cleaned[, 839 ])
gene5408.cleaned[,  840 ] <- as.numeric(gene5408.cleaned[, 840 ])
gene5408.cleaned[,  841 ] <- as.numeric(gene5408.cleaned[, 841 ])
gene5408.cleaned[,  842 ] <- as.numeric(gene5408.cleaned[, 842 ])
gene5408.cleaned[,  843 ] <- as.numeric(gene5408.cleaned[, 843 ])
gene5408.cleaned[,  844 ] <- as.numeric(gene5408.cleaned[, 844 ])
gene5408.cleaned[,  845 ] <- as.numeric(gene5408.cleaned[, 845 ])
gene5408.cleaned[,  846 ] <- as.numeric(gene5408.cleaned[, 846 ])
gene5408.cleaned[,  847 ] <- as.numeric(gene5408.cleaned[, 847 ])
gene5408.cleaned[,  848 ] <- as.numeric(gene5408.cleaned[, 848 ])
gene5408.cleaned[,  849 ] <- as.numeric(gene5408.cleaned[, 849 ])
gene5408.cleaned[,  850 ] <- as.numeric(gene5408.cleaned[, 850 ])
gene5408.cleaned[,  851 ] <- as.numeric(gene5408.cleaned[, 851 ])
gene5408.cleaned[,  852 ] <- as.numeric(gene5408.cleaned[, 852 ])
gene5408.cleaned[,  853 ] <- as.numeric(gene5408.cleaned[, 853 ])
gene5408.cleaned[,  854 ] <- as.numeric(gene5408.cleaned[, 854 ])
gene5408.cleaned[,  855 ] <- as.numeric(gene5408.cleaned[, 855 ])
gene5408.cleaned[,  856 ] <- as.numeric(gene5408.cleaned[, 856 ])
gene5408.cleaned[,  857 ] <- as.numeric(gene5408.cleaned[, 857 ])
gene5408.cleaned[,  858 ] <- as.numeric(gene5408.cleaned[, 858 ])
gene5408.cleaned[,  859 ] <- as.numeric(gene5408.cleaned[, 859 ])
gene5408.cleaned[,  860 ] <- as.numeric(gene5408.cleaned[, 860 ])
gene5408.cleaned[,  861 ] <- as.numeric(gene5408.cleaned[, 861 ])
gene5408.cleaned[,  862 ] <- as.numeric(gene5408.cleaned[, 862 ])
gene5408.cleaned[,  863 ] <- as.numeric(gene5408.cleaned[, 863 ])
gene5408.cleaned[,  864 ] <- as.numeric(gene5408.cleaned[, 864 ])
gene5408.cleaned[,  865 ] <- as.numeric(gene5408.cleaned[, 865 ])
gene5408.cleaned[,  866 ] <- as.numeric(gene5408.cleaned[, 866 ])
gene5408.cleaned[,  867 ] <- as.numeric(gene5408.cleaned[, 867 ])
gene5408.cleaned[,  868 ] <- as.numeric(gene5408.cleaned[, 868 ])
gene5408.cleaned[,  869 ] <- as.numeric(gene5408.cleaned[, 869 ])
gene5408.cleaned[,  870 ] <- as.numeric(gene5408.cleaned[, 870 ])
gene5408.cleaned[,  871 ] <- as.numeric(gene5408.cleaned[, 871 ])
gene5408.cleaned[,  872 ] <- as.numeric(gene5408.cleaned[, 872 ])
gene5408.cleaned[,  873 ] <- as.numeric(gene5408.cleaned[, 873 ])
gene5408.cleaned[,  874 ] <- as.numeric(gene5408.cleaned[, 874 ])
gene5408.cleaned[,  875 ] <- as.numeric(gene5408.cleaned[, 875 ])
gene5408.cleaned[,  876 ] <- as.numeric(gene5408.cleaned[, 876 ])
gene5408.cleaned[,  877 ] <- as.numeric(gene5408.cleaned[, 877 ])
gene5408.cleaned[,  878 ] <- as.numeric(gene5408.cleaned[, 878 ])
gene5408.cleaned[,  879 ] <- as.numeric(gene5408.cleaned[, 879 ])
gene5408.cleaned[,  880 ] <- as.numeric(gene5408.cleaned[, 880 ])
gene5408.cleaned[,  881 ] <- as.numeric(gene5408.cleaned[, 881 ])
gene5408.cleaned[,  882 ] <- as.numeric(gene5408.cleaned[, 882 ])
gene5408.cleaned[,  883 ] <- as.numeric(gene5408.cleaned[, 883 ])
gene5408.cleaned[,  884 ] <- as.numeric(gene5408.cleaned[, 884 ])
gene5408.cleaned[,  885 ] <- as.numeric(gene5408.cleaned[, 885 ])
gene5408.cleaned[,  886 ] <- as.numeric(gene5408.cleaned[, 886 ])
gene5408.cleaned[,  887 ] <- as.numeric(gene5408.cleaned[, 887 ])
gene5408.cleaned[,  888 ] <- as.numeric(gene5408.cleaned[, 888 ])
gene5408.cleaned[,  889 ] <- as.numeric(gene5408.cleaned[, 889 ])
gene5408.cleaned[,  890 ] <- as.numeric(gene5408.cleaned[, 890 ])
gene5408.cleaned[,  891 ] <- as.numeric(gene5408.cleaned[, 891 ])
gene5408.cleaned[,  892 ] <- as.numeric(gene5408.cleaned[, 892 ])
gene5408.cleaned[,  893 ] <- as.numeric(gene5408.cleaned[, 893 ])
gene5408.cleaned[,  894 ] <- as.numeric(gene5408.cleaned[, 894 ])
gene5408.cleaned[,  895 ] <- as.numeric(gene5408.cleaned[, 895 ])
gene5408.cleaned[,  896 ] <- as.numeric(gene5408.cleaned[, 896 ])
gene5408.cleaned[,  897 ] <- as.numeric(gene5408.cleaned[, 897 ])
gene5408.cleaned[,  898 ] <- as.numeric(gene5408.cleaned[, 898 ])
gene5408.cleaned[,  899 ] <- as.numeric(gene5408.cleaned[, 899 ])
gene5408.cleaned[,  900 ] <- as.numeric(gene5408.cleaned[, 900 ])
gene5408.cleaned[,  901 ] <- as.numeric(gene5408.cleaned[, 901 ])
gene5408.cleaned[,  902 ] <- as.numeric(gene5408.cleaned[, 902 ])
gene5408.cleaned[,  903 ] <- as.numeric(gene5408.cleaned[, 903 ])
gene5408.cleaned[,  904 ] <- as.numeric(gene5408.cleaned[, 904 ])
gene5408.cleaned[,  905 ] <- as.numeric(gene5408.cleaned[, 905 ])
gene5408.cleaned[,  906 ] <- as.numeric(gene5408.cleaned[, 906 ])
gene5408.cleaned[,  907 ] <- as.numeric(gene5408.cleaned[, 907 ])
gene5408.cleaned[,  908 ] <- as.numeric(gene5408.cleaned[, 908 ])
gene5408.cleaned[,  909 ] <- as.numeric(gene5408.cleaned[, 909 ])
gene5408.cleaned[,  910 ] <- as.numeric(gene5408.cleaned[, 910 ])
gene5408.cleaned[,  911 ] <- as.numeric(gene5408.cleaned[, 911 ])
gene5408.cleaned[,  912 ] <- as.numeric(gene5408.cleaned[, 912 ])
gene5408.cleaned[,  913 ] <- as.numeric(gene5408.cleaned[, 913 ])
gene5408.cleaned[,  914 ] <- as.numeric(gene5408.cleaned[, 914 ])
gene5408.cleaned[,  915 ] <- as.numeric(gene5408.cleaned[, 915 ])
gene5408.cleaned[,  916 ] <- as.numeric(gene5408.cleaned[, 916 ])
gene5408.cleaned[,  917 ] <- as.numeric(gene5408.cleaned[, 917 ])
gene5408.cleaned[,  918 ] <- as.numeric(gene5408.cleaned[, 918 ])
gene5408.cleaned[,  919 ] <- as.numeric(gene5408.cleaned[, 919 ])
gene5408.cleaned[,  920 ] <- as.numeric(gene5408.cleaned[, 920 ])
gene5408.cleaned[,  921 ] <- as.numeric(gene5408.cleaned[, 921 ])
gene5408.cleaned[,  922 ] <- as.numeric(gene5408.cleaned[, 922 ])
gene5408.cleaned[,  923 ] <- as.numeric(gene5408.cleaned[, 923 ])
gene5408.cleaned[,  924 ] <- as.numeric(gene5408.cleaned[, 924 ])
gene5408.cleaned[,  925 ] <- as.numeric(gene5408.cleaned[, 925 ])
gene5408.cleaned[,  926 ] <- as.numeric(gene5408.cleaned[, 926 ])
gene5408.cleaned[,  927 ] <- as.numeric(gene5408.cleaned[, 927 ])
gene5408.cleaned[,  928 ] <- as.numeric(gene5408.cleaned[, 928 ])
gene5408.cleaned[,  929 ] <- as.numeric(gene5408.cleaned[, 929 ])
gene5408.cleaned[,  930 ] <- as.numeric(gene5408.cleaned[, 930 ])
gene5408.cleaned[,  931 ] <- as.numeric(gene5408.cleaned[, 931 ])
gene5408.cleaned[,  932 ] <- as.numeric(gene5408.cleaned[, 932 ])
gene5408.cleaned[,  933 ] <- as.numeric(gene5408.cleaned[, 933 ])
gene5408.cleaned[,  934 ] <- as.numeric(gene5408.cleaned[, 934 ])
gene5408.cleaned[,  935 ] <- as.numeric(gene5408.cleaned[, 935 ])
gene5408.cleaned[,  936 ] <- as.numeric(gene5408.cleaned[, 936 ])
gene5408.cleaned[,  937 ] <- as.numeric(gene5408.cleaned[, 937 ])
gene5408.cleaned[,  938 ] <- as.numeric(gene5408.cleaned[, 938 ])
gene5408.cleaned[,  939 ] <- as.numeric(gene5408.cleaned[, 939 ])
gene5408.cleaned[,  940 ] <- as.numeric(gene5408.cleaned[, 940 ])
gene5408.cleaned[,  941 ] <- as.numeric(gene5408.cleaned[, 941 ])
gene5408.cleaned[,  942 ] <- as.numeric(gene5408.cleaned[, 942 ])
gene5408.cleaned[,  943 ] <- as.numeric(gene5408.cleaned[, 943 ])
gene5408.cleaned[,  944 ] <- as.numeric(gene5408.cleaned[, 944 ])
gene5408.cleaned[,  945 ] <- as.numeric(gene5408.cleaned[, 945 ])
gene5408.cleaned[,  946 ] <- as.numeric(gene5408.cleaned[, 946 ])
gene5408.cleaned[,  947 ] <- as.numeric(gene5408.cleaned[, 947 ])
gene5408.cleaned[,  948 ] <- as.numeric(gene5408.cleaned[, 948 ])
gene5408.cleaned[,  949 ] <- as.numeric(gene5408.cleaned[, 949 ])
gene5408.cleaned[,  950 ] <- as.numeric(gene5408.cleaned[, 950 ])
gene5408.cleaned[,  951 ] <- as.numeric(gene5408.cleaned[, 951 ])
gene5408.cleaned[,  952 ] <- as.numeric(gene5408.cleaned[, 952 ])
gene5408.cleaned[,  953 ] <- as.numeric(gene5408.cleaned[, 953 ])
gene5408.cleaned[,  954 ] <- as.numeric(gene5408.cleaned[, 954 ])
gene5408.cleaned[,  955 ] <- as.numeric(gene5408.cleaned[, 955 ])
gene5408.cleaned[,  956 ] <- as.numeric(gene5408.cleaned[, 956 ])
gene5408.cleaned[,  957 ] <- as.numeric(gene5408.cleaned[, 957 ])
gene5408.cleaned[,  958 ] <- as.numeric(gene5408.cleaned[, 958 ])
gene5408.cleaned[,  959 ] <- as.numeric(gene5408.cleaned[, 959 ])
gene5408.cleaned[,  960 ] <- as.numeric(gene5408.cleaned[, 960 ])
gene5408.cleaned[,  961 ] <- as.numeric(gene5408.cleaned[, 961 ])
gene5408.cleaned[,  962 ] <- as.numeric(gene5408.cleaned[, 962 ])
gene5408.cleaned[,  963 ] <- as.numeric(gene5408.cleaned[, 963 ])
gene5408.cleaned[,  964 ] <- as.numeric(gene5408.cleaned[, 964 ])
gene5408.cleaned[,  965 ] <- as.numeric(gene5408.cleaned[, 965 ])
gene5408.cleaned[,  966 ] <- as.numeric(gene5408.cleaned[, 966 ])
gene5408.cleaned[,  967 ] <- as.numeric(gene5408.cleaned[, 967 ])
gene5408.cleaned[,  968 ] <- as.numeric(gene5408.cleaned[, 968 ])
gene5408.cleaned[,  969 ] <- as.numeric(gene5408.cleaned[, 969 ])
gene5408.cleaned[,  970 ] <- as.numeric(gene5408.cleaned[, 970 ])
gene5408.cleaned[,  971 ] <- as.numeric(gene5408.cleaned[, 971 ])
gene5408.cleaned[,  972 ] <- as.numeric(gene5408.cleaned[, 972 ])
gene5408.cleaned[,  973 ] <- as.numeric(gene5408.cleaned[, 973 ])
gene5408.cleaned[,  974 ] <- as.numeric(gene5408.cleaned[, 974 ])
gene5408.cleaned[,  975 ] <- as.numeric(gene5408.cleaned[, 975 ])
gene5408.cleaned[,  976 ] <- as.numeric(gene5408.cleaned[, 976 ])
gene5408.cleaned[,  977 ] <- as.numeric(gene5408.cleaned[, 977 ])
gene5408.cleaned[,  978 ] <- as.numeric(gene5408.cleaned[, 978 ])
gene5408.cleaned[,  979 ] <- as.numeric(gene5408.cleaned[, 979 ])
gene5408.cleaned[,  980 ] <- as.numeric(gene5408.cleaned[, 980 ])
gene5408.cleaned[,  981 ] <- as.numeric(gene5408.cleaned[, 981 ])
gene5408.cleaned[,  982 ] <- as.numeric(gene5408.cleaned[, 982 ])
gene5408.cleaned[,  983 ] <- as.numeric(gene5408.cleaned[, 983 ])
gene5408.cleaned[,  984 ] <- as.numeric(gene5408.cleaned[, 984 ])
gene5408.cleaned[,  985 ] <- as.numeric(gene5408.cleaned[, 985 ])
gene5408.cleaned[,  986 ] <- as.numeric(gene5408.cleaned[, 986 ])
gene5408.cleaned[,  987 ] <- as.numeric(gene5408.cleaned[, 987 ])
gene5408.cleaned[,  988 ] <- as.numeric(gene5408.cleaned[, 988 ])
gene5408.cleaned[,  989 ] <- as.numeric(gene5408.cleaned[, 989 ])
gene5408.cleaned[,  990 ] <- as.numeric(gene5408.cleaned[, 990 ])
gene5408.cleaned[,  991 ] <- as.numeric(gene5408.cleaned[, 991 ])
gene5408.cleaned[,  992 ] <- as.numeric(gene5408.cleaned[, 992 ])
gene5408.cleaned[,  993 ] <- as.numeric(gene5408.cleaned[, 993 ])
gene5408.cleaned[,  994 ] <- as.numeric(gene5408.cleaned[, 994 ])
gene5408.cleaned[,  995 ] <- as.numeric(gene5408.cleaned[, 995 ])
gene5408.cleaned[,  996 ] <- as.numeric(gene5408.cleaned[, 996 ])
gene5408.cleaned[,  997 ] <- as.numeric(gene5408.cleaned[, 997 ])
gene5408.cleaned[,  998 ] <- as.numeric(gene5408.cleaned[, 998 ])
gene5408.cleaned[,  999 ] <- as.numeric(gene5408.cleaned[, 999 ])
gene5408.cleaned[,  1000 ] <- as.numeric(gene5408.cleaned[, 1000 ])

gene5408.cleaned[,  1001 ] <- as.numeric(gene5408.cleaned[, 1001 ])
gene5408.cleaned[,  1002 ] <- as.numeric(gene5408.cleaned[, 1002 ])
gene5408.cleaned[,  1003 ] <- as.numeric(gene5408.cleaned[, 1003 ])
gene5408.cleaned[,  1004 ] <- as.numeric(gene5408.cleaned[, 1004 ])
gene5408.cleaned[,  1005 ] <- as.numeric(gene5408.cleaned[, 1005 ])
gene5408.cleaned[,  1006 ] <- as.numeric(gene5408.cleaned[, 1006 ])
gene5408.cleaned[,  1007 ] <- as.numeric(gene5408.cleaned[, 1007 ])
gene5408.cleaned[,  1008 ] <- as.numeric(gene5408.cleaned[, 1008 ])
gene5408.cleaned[,  1009 ] <- as.numeric(gene5408.cleaned[, 1009 ])
gene5408.cleaned[,  1010 ] <- as.numeric(gene5408.cleaned[, 1010 ])
gene5408.cleaned[,  1011 ] <- as.numeric(gene5408.cleaned[, 1011 ])
gene5408.cleaned[,  1012 ] <- as.numeric(gene5408.cleaned[, 1012 ])
gene5408.cleaned[,  1013 ] <- as.numeric(gene5408.cleaned[, 1013 ])
gene5408.cleaned[,  1014 ] <- as.numeric(gene5408.cleaned[, 1014 ])
gene5408.cleaned[,  1015 ] <- as.numeric(gene5408.cleaned[, 1015 ])
gene5408.cleaned[,  1016 ] <- as.numeric(gene5408.cleaned[, 1016 ])
gene5408.cleaned[,  1017 ] <- as.numeric(gene5408.cleaned[, 1017 ])
gene5408.cleaned[,  1018 ] <- as.numeric(gene5408.cleaned[, 1018 ])
gene5408.cleaned[,  1019 ] <- as.numeric(gene5408.cleaned[, 1019 ])
gene5408.cleaned[,  1020 ] <- as.numeric(gene5408.cleaned[, 1020 ])
gene5408.cleaned[,  1021 ] <- as.numeric(gene5408.cleaned[, 1021 ])
gene5408.cleaned[,  1022 ] <- as.numeric(gene5408.cleaned[, 1022 ])
gene5408.cleaned[,  1023 ] <- as.numeric(gene5408.cleaned[, 1023 ])
gene5408.cleaned[,  1024 ] <- as.numeric(gene5408.cleaned[, 1024 ])
gene5408.cleaned[,  1025 ] <- as.numeric(gene5408.cleaned[, 1025 ])
gene5408.cleaned[,  1026 ] <- as.numeric(gene5408.cleaned[, 1026 ])
gene5408.cleaned[,  1027 ] <- as.numeric(gene5408.cleaned[, 1027 ])
gene5408.cleaned[,  1028 ] <- as.numeric(gene5408.cleaned[, 1028 ])
gene5408.cleaned[,  1029 ] <- as.numeric(gene5408.cleaned[, 1029 ])
gene5408.cleaned[,  1030 ] <- as.numeric(gene5408.cleaned[, 1030 ])
gene5408.cleaned[,  1031 ] <- as.numeric(gene5408.cleaned[, 1031 ])
gene5408.cleaned[,  1032 ] <- as.numeric(gene5408.cleaned[, 1032 ])
gene5408.cleaned[,  1033 ] <- as.numeric(gene5408.cleaned[, 1033 ])
gene5408.cleaned[,  1034 ] <- as.numeric(gene5408.cleaned[, 1034 ])
gene5408.cleaned[,  1035 ] <- as.numeric(gene5408.cleaned[, 1035 ])
gene5408.cleaned[,  1036 ] <- as.numeric(gene5408.cleaned[, 1036 ])
gene5408.cleaned[,  1037 ] <- as.numeric(gene5408.cleaned[, 1037 ])
gene5408.cleaned[,  1038 ] <- as.numeric(gene5408.cleaned[, 1038 ])
gene5408.cleaned[,  1039 ] <- as.numeric(gene5408.cleaned[, 1039 ])
gene5408.cleaned[,  1040 ] <- as.numeric(gene5408.cleaned[, 1040 ])
gene5408.cleaned[,  1041 ] <- as.numeric(gene5408.cleaned[, 1041 ])
gene5408.cleaned[,  1042 ] <- as.numeric(gene5408.cleaned[, 1042 ])
gene5408.cleaned[,  1043 ] <- as.numeric(gene5408.cleaned[, 1043 ])
gene5408.cleaned[,  1044 ] <- as.numeric(gene5408.cleaned[, 1044 ])
gene5408.cleaned[,  1045 ] <- as.numeric(gene5408.cleaned[, 1045 ])
gene5408.cleaned[,  1046 ] <- as.numeric(gene5408.cleaned[, 1046 ])
gene5408.cleaned[,  1047 ] <- as.numeric(gene5408.cleaned[, 1047 ])
gene5408.cleaned[,  1048 ] <- as.numeric(gene5408.cleaned[, 1048 ])
gene5408.cleaned[,  1049 ] <- as.numeric(gene5408.cleaned[, 1049 ])
gene5408.cleaned[,  1050 ] <- as.numeric(gene5408.cleaned[, 1050 ])
gene5408.cleaned[,  1051 ] <- as.numeric(gene5408.cleaned[, 1051 ])
gene5408.cleaned[,  1052 ] <- as.numeric(gene5408.cleaned[, 1052 ])
gene5408.cleaned[,  1053 ] <- as.numeric(gene5408.cleaned[, 1053 ])
gene5408.cleaned[,  1054 ] <- as.numeric(gene5408.cleaned[, 1054 ])
gene5408.cleaned[,  1055 ] <- as.numeric(gene5408.cleaned[, 1055 ])
gene5408.cleaned[,  1056 ] <- as.numeric(gene5408.cleaned[, 1056 ])
gene5408.cleaned[,  1057 ] <- as.numeric(gene5408.cleaned[, 1057 ])
gene5408.cleaned[,  1058 ] <- as.numeric(gene5408.cleaned[, 1058 ])
gene5408.cleaned[,  1059 ] <- as.numeric(gene5408.cleaned[, 1059 ])
gene5408.cleaned[,  1060 ] <- as.numeric(gene5408.cleaned[, 1060 ])
gene5408.cleaned[,  1061 ] <- as.numeric(gene5408.cleaned[, 1061 ])
gene5408.cleaned[,  1062 ] <- as.numeric(gene5408.cleaned[, 1062 ])
gene5408.cleaned[,  1063 ] <- as.numeric(gene5408.cleaned[, 1063 ])
gene5408.cleaned[,  1064 ] <- as.numeric(gene5408.cleaned[, 1064 ])
gene5408.cleaned[,  1065 ] <- as.numeric(gene5408.cleaned[, 1065 ])
gene5408.cleaned[,  1066 ] <- as.numeric(gene5408.cleaned[, 1066 ])
gene5408.cleaned[,  1067 ] <- as.numeric(gene5408.cleaned[, 1067 ])
gene5408.cleaned[,  1068 ] <- as.numeric(gene5408.cleaned[, 1068 ])
gene5408.cleaned[,  1069 ] <- as.numeric(gene5408.cleaned[, 1069 ])
gene5408.cleaned[,  1070 ] <- as.numeric(gene5408.cleaned[, 1070 ])
gene5408.cleaned[,  1071 ] <- as.numeric(gene5408.cleaned[, 1071 ])
gene5408.cleaned[,  1072 ] <- as.numeric(gene5408.cleaned[, 1072 ])
gene5408.cleaned[,  1073 ] <- as.numeric(gene5408.cleaned[, 1073 ])
gene5408.cleaned[,  1074 ] <- as.numeric(gene5408.cleaned[, 1074 ])
gene5408.cleaned[,  1075 ] <- as.numeric(gene5408.cleaned[, 1075 ])
gene5408.cleaned[,  1076 ] <- as.numeric(gene5408.cleaned[, 1076 ])
gene5408.cleaned[,  1077 ] <- as.numeric(gene5408.cleaned[, 1077 ])
gene5408.cleaned[,  1078 ] <- as.numeric(gene5408.cleaned[, 1078 ])
gene5408.cleaned[,  1079 ] <- as.numeric(gene5408.cleaned[, 1079 ])
gene5408.cleaned[,  1080 ] <- as.numeric(gene5408.cleaned[, 1080 ])
gene5408.cleaned[,  1081 ] <- as.numeric(gene5408.cleaned[, 1081 ])
gene5408.cleaned[,  1082 ] <- as.numeric(gene5408.cleaned[, 1082 ])
gene5408.cleaned[,  1083 ] <- as.numeric(gene5408.cleaned[, 1083 ])
gene5408.cleaned[,  1084 ] <- as.numeric(gene5408.cleaned[, 1084 ])
gene5408.cleaned[,  1085 ] <- as.numeric(gene5408.cleaned[, 1085 ])
gene5408.cleaned[,  1086 ] <- as.numeric(gene5408.cleaned[, 1086 ])
gene5408.cleaned[,  1087 ] <- as.numeric(gene5408.cleaned[, 1087 ])
gene5408.cleaned[,  1088 ] <- as.numeric(gene5408.cleaned[, 1088 ])
gene5408.cleaned[,  1089 ] <- as.numeric(gene5408.cleaned[, 1089 ])
gene5408.cleaned[,  1090 ] <- as.numeric(gene5408.cleaned[, 1090 ])
gene5408.cleaned[,  1091 ] <- as.numeric(gene5408.cleaned[, 1091 ])
gene5408.cleaned[,  1092 ] <- as.numeric(gene5408.cleaned[, 1092 ])
gene5408.cleaned[,  1093 ] <- as.numeric(gene5408.cleaned[, 1093 ])
gene5408.cleaned[,  1094 ] <- as.numeric(gene5408.cleaned[, 1094 ])
gene5408.cleaned[,  1095 ] <- as.numeric(gene5408.cleaned[, 1095 ])
gene5408.cleaned[,  1096 ] <- as.numeric(gene5408.cleaned[, 1096 ])
gene5408.cleaned[,  1097 ] <- as.numeric(gene5408.cleaned[, 1097 ])
gene5408.cleaned[,  1098 ] <- as.numeric(gene5408.cleaned[, 1098 ])
gene5408.cleaned[,  1099 ] <- as.numeric(gene5408.cleaned[, 1099 ])
gene5408.cleaned[,  1100 ] <- as.numeric(gene5408.cleaned[, 1100 ])
gene5408.cleaned[,  1101 ] <- as.numeric(gene5408.cleaned[, 1101 ])
gene5408.cleaned[,  1102 ] <- as.numeric(gene5408.cleaned[, 1102 ])
gene5408.cleaned[,  1103 ] <- as.numeric(gene5408.cleaned[, 1103 ])
gene5408.cleaned[,  1104 ] <- as.numeric(gene5408.cleaned[, 1104 ])
gene5408.cleaned[,  1105 ] <- as.numeric(gene5408.cleaned[, 1105 ])
gene5408.cleaned[,  1106 ] <- as.numeric(gene5408.cleaned[, 1106 ])
gene5408.cleaned[,  1107 ] <- as.numeric(gene5408.cleaned[, 1107 ])
gene5408.cleaned[,  1108 ] <- as.numeric(gene5408.cleaned[, 1108 ])
gene5408.cleaned[,  1109 ] <- as.numeric(gene5408.cleaned[, 1109 ])
gene5408.cleaned[,  1110 ] <- as.numeric(gene5408.cleaned[, 1110 ])
gene5408.cleaned[,  1111 ] <- as.numeric(gene5408.cleaned[, 1111 ])
gene5408.cleaned[,  1112 ] <- as.numeric(gene5408.cleaned[, 1112 ])
gene5408.cleaned[,  1113 ] <- as.numeric(gene5408.cleaned[, 1113 ])
gene5408.cleaned[,  1114 ] <- as.numeric(gene5408.cleaned[, 1114 ])
gene5408.cleaned[,  1115 ] <- as.numeric(gene5408.cleaned[, 1115 ])
gene5408.cleaned[,  1116 ] <- as.numeric(gene5408.cleaned[, 1116 ])
gene5408.cleaned[,  1117 ] <- as.numeric(gene5408.cleaned[, 1117 ])
gene5408.cleaned[,  1118 ] <- as.numeric(gene5408.cleaned[, 1118 ])
gene5408.cleaned[,  1119 ] <- as.numeric(gene5408.cleaned[, 1119 ])
gene5408.cleaned[,  1120 ] <- as.numeric(gene5408.cleaned[, 1120 ])
gene5408.cleaned[,  1121 ] <- as.numeric(gene5408.cleaned[, 1121 ])
gene5408.cleaned[,  1122 ] <- as.numeric(gene5408.cleaned[, 1122 ])
gene5408.cleaned[,  1123 ] <- as.numeric(gene5408.cleaned[, 1123 ])
gene5408.cleaned[,  1124 ] <- as.numeric(gene5408.cleaned[, 1124 ])
gene5408.cleaned[,  1125 ] <- as.numeric(gene5408.cleaned[, 1125 ])
gene5408.cleaned[,  1126 ] <- as.numeric(gene5408.cleaned[, 1126 ])
gene5408.cleaned[,  1127 ] <- as.numeric(gene5408.cleaned[, 1127 ])
gene5408.cleaned[,  1128 ] <- as.numeric(gene5408.cleaned[, 1128 ])
gene5408.cleaned[,  1129 ] <- as.numeric(gene5408.cleaned[, 1129 ])
gene5408.cleaned[,  1130 ] <- as.numeric(gene5408.cleaned[, 1130 ])
gene5408.cleaned[,  1131 ] <- as.numeric(gene5408.cleaned[, 1131 ])
gene5408.cleaned[,  1132 ] <- as.numeric(gene5408.cleaned[, 1132 ])
gene5408.cleaned[,  1133 ] <- as.numeric(gene5408.cleaned[, 1133 ])
gene5408.cleaned[,  1134 ] <- as.numeric(gene5408.cleaned[, 1134 ])
gene5408.cleaned[,  1135 ] <- as.numeric(gene5408.cleaned[, 1135 ])
gene5408.cleaned[,  1136 ] <- as.numeric(gene5408.cleaned[, 1136 ])
gene5408.cleaned[,  1137 ] <- as.numeric(gene5408.cleaned[, 1137 ])
gene5408.cleaned[,  1138 ] <- as.numeric(gene5408.cleaned[, 1138 ])
gene5408.cleaned[,  1139 ] <- as.numeric(gene5408.cleaned[, 1139 ])
gene5408.cleaned[,  1140 ] <- as.numeric(gene5408.cleaned[, 1140 ])
gene5408.cleaned[,  1141 ] <- as.numeric(gene5408.cleaned[, 1141 ])
gene5408.cleaned[,  1142 ] <- as.numeric(gene5408.cleaned[, 1142 ])
gene5408.cleaned[,  1143 ] <- as.numeric(gene5408.cleaned[, 1143 ])
gene5408.cleaned[,  1144 ] <- as.numeric(gene5408.cleaned[, 1144 ])
gene5408.cleaned[,  1145 ] <- as.numeric(gene5408.cleaned[, 1145 ])
gene5408.cleaned[,  1146 ] <- as.numeric(gene5408.cleaned[, 1146 ])
gene5408.cleaned[,  1147 ] <- as.numeric(gene5408.cleaned[, 1147 ])
gene5408.cleaned[,  1148 ] <- as.numeric(gene5408.cleaned[, 1148 ])
gene5408.cleaned[,  1149 ] <- as.numeric(gene5408.cleaned[, 1149 ])
gene5408.cleaned[,  1150 ] <- as.numeric(gene5408.cleaned[, 1150 ])
gene5408.cleaned[,  1151 ] <- as.numeric(gene5408.cleaned[, 1151 ])
gene5408.cleaned[,  1152 ] <- as.numeric(gene5408.cleaned[, 1152 ])
gene5408.cleaned[,  1153 ] <- as.numeric(gene5408.cleaned[, 1153 ])
gene5408.cleaned[,  1154 ] <- as.numeric(gene5408.cleaned[, 1154 ])
gene5408.cleaned[,  1155 ] <- as.numeric(gene5408.cleaned[, 1155 ])
gene5408.cleaned[,  1156 ] <- as.numeric(gene5408.cleaned[, 1156 ])
gene5408.cleaned[,  1157 ] <- as.numeric(gene5408.cleaned[, 1157 ])
gene5408.cleaned[,  1158 ] <- as.numeric(gene5408.cleaned[, 1158 ])
gene5408.cleaned[,  1159 ] <- as.numeric(gene5408.cleaned[, 1159 ])
gene5408.cleaned[,  1160 ] <- as.numeric(gene5408.cleaned[, 1160 ])
gene5408.cleaned[,  1161 ] <- as.numeric(gene5408.cleaned[, 1161 ])
gene5408.cleaned[,  1162 ] <- as.numeric(gene5408.cleaned[, 1162 ])
gene5408.cleaned[,  1163 ] <- as.numeric(gene5408.cleaned[, 1163 ])
gene5408.cleaned[,  1164 ] <- as.numeric(gene5408.cleaned[, 1164 ])
gene5408.cleaned[,  1165 ] <- as.numeric(gene5408.cleaned[, 1165 ])
gene5408.cleaned[,  1166 ] <- as.numeric(gene5408.cleaned[, 1166 ])
gene5408.cleaned[,  1167 ] <- as.numeric(gene5408.cleaned[, 1167 ])
gene5408.cleaned[,  1168 ] <- as.numeric(gene5408.cleaned[, 1168 ])
gene5408.cleaned[,  1169 ] <- as.numeric(gene5408.cleaned[, 1169 ])
gene5408.cleaned[,  1170 ] <- as.numeric(gene5408.cleaned[, 1170 ])
gene5408.cleaned[,  1171 ] <- as.numeric(gene5408.cleaned[, 1171 ])
gene5408.cleaned[,  1172 ] <- as.numeric(gene5408.cleaned[, 1172 ])
gene5408.cleaned[,  1173 ] <- as.numeric(gene5408.cleaned[, 1173 ])
gene5408.cleaned[,  1174 ] <- as.numeric(gene5408.cleaned[, 1174 ])
gene5408.cleaned[,  1175 ] <- as.numeric(gene5408.cleaned[, 1175 ])
gene5408.cleaned[,  1176 ] <- as.numeric(gene5408.cleaned[, 1176 ])
gene5408.cleaned[,  1177 ] <- as.numeric(gene5408.cleaned[, 1177 ])
gene5408.cleaned[,  1178 ] <- as.numeric(gene5408.cleaned[, 1178 ])
gene5408.cleaned[,  1179 ] <- as.numeric(gene5408.cleaned[, 1179 ])
gene5408.cleaned[,  1180 ] <- as.numeric(gene5408.cleaned[, 1180 ])
gene5408.cleaned[,  1181 ] <- as.numeric(gene5408.cleaned[, 1181 ])
gene5408.cleaned[,  1182 ] <- as.numeric(gene5408.cleaned[, 1182 ])
gene5408.cleaned[,  1183 ] <- as.numeric(gene5408.cleaned[, 1183 ])
gene5408.cleaned[,  1184 ] <- as.numeric(gene5408.cleaned[, 1184 ])
gene5408.cleaned[,  1185 ] <- as.numeric(gene5408.cleaned[, 1185 ])
gene5408.cleaned[,  1186 ] <- as.numeric(gene5408.cleaned[, 1186 ])
gene5408.cleaned[,  1187 ] <- as.numeric(gene5408.cleaned[, 1187 ])
gene5408.cleaned[,  1188 ] <- as.numeric(gene5408.cleaned[, 1188 ])
gene5408.cleaned[,  1189 ] <- as.numeric(gene5408.cleaned[, 1189 ])
gene5408.cleaned[,  1190 ] <- as.numeric(gene5408.cleaned[, 1190 ])
gene5408.cleaned[,  1191 ] <- as.numeric(gene5408.cleaned[, 1191 ])
gene5408.cleaned[,  1192 ] <- as.numeric(gene5408.cleaned[, 1192 ])
gene5408.cleaned[,  1193 ] <- as.numeric(gene5408.cleaned[, 1193 ])
gene5408.cleaned[,  1194 ] <- as.numeric(gene5408.cleaned[, 1194 ])
gene5408.cleaned[,  1195 ] <- as.numeric(gene5408.cleaned[, 1195 ])
gene5408.cleaned[,  1196 ] <- as.numeric(gene5408.cleaned[, 1196 ])
gene5408.cleaned[,  1197 ] <- as.numeric(gene5408.cleaned[, 1197 ])
gene5408.cleaned[,  1198 ] <- as.numeric(gene5408.cleaned[, 1198 ])
gene5408.cleaned[,  1199 ] <- as.numeric(gene5408.cleaned[, 1199 ])
gene5408.cleaned[,  1200 ] <- as.numeric(gene5408.cleaned[, 1200 ])
gene5408.cleaned[,  1201 ] <- as.numeric(gene5408.cleaned[, 1201 ])
gene5408.cleaned[,  1202 ] <- as.numeric(gene5408.cleaned[, 1202 ])
gene5408.cleaned[,  1203 ] <- as.numeric(gene5408.cleaned[, 1203 ])
gene5408.cleaned[,  1204 ] <- as.numeric(gene5408.cleaned[, 1204 ])
gene5408.cleaned[,  1205 ] <- as.numeric(gene5408.cleaned[, 1205 ])
gene5408.cleaned[,  1206 ] <- as.numeric(gene5408.cleaned[, 1206 ])
gene5408.cleaned[,  1207 ] <- as.numeric(gene5408.cleaned[, 1207 ])
gene5408.cleaned[,  1208 ] <- as.numeric(gene5408.cleaned[, 1208 ])
gene5408.cleaned[,  1209 ] <- as.numeric(gene5408.cleaned[, 1209 ])
gene5408.cleaned[,  1210 ] <- as.numeric(gene5408.cleaned[, 1210 ])
gene5408.cleaned[,  1211 ] <- as.numeric(gene5408.cleaned[, 1211 ])
gene5408.cleaned[,  1212 ] <- as.numeric(gene5408.cleaned[, 1212 ])
gene5408.cleaned[,  1213 ] <- as.numeric(gene5408.cleaned[, 1213 ])
gene5408.cleaned[,  1214 ] <- as.numeric(gene5408.cleaned[, 1214 ])
gene5408.cleaned[,  1215 ] <- as.numeric(gene5408.cleaned[, 1215 ])
gene5408.cleaned[,  1216 ] <- as.numeric(gene5408.cleaned[, 1216 ])
gene5408.cleaned[,  1217 ] <- as.numeric(gene5408.cleaned[, 1217 ])
gene5408.cleaned[,  1218 ] <- as.numeric(gene5408.cleaned[, 1218 ])
gene5408.cleaned[,  1219 ] <- as.numeric(gene5408.cleaned[, 1219 ])
gene5408.cleaned[,  1220 ] <- as.numeric(gene5408.cleaned[, 1220 ])
gene5408.cleaned[,  1221 ] <- as.numeric(gene5408.cleaned[, 1221 ])
gene5408.cleaned[,  1222 ] <- as.numeric(gene5408.cleaned[, 1222 ])
gene5408.cleaned[,  1223 ] <- as.numeric(gene5408.cleaned[, 1223 ])
gene5408.cleaned[,  1224 ] <- as.numeric(gene5408.cleaned[, 1224 ])
gene5408.cleaned[,  1225 ] <- as.numeric(gene5408.cleaned[, 1225 ])
gene5408.cleaned[,  1226 ] <- as.numeric(gene5408.cleaned[, 1226 ])
gene5408.cleaned[,  1227 ] <- as.numeric(gene5408.cleaned[, 1227 ])
gene5408.cleaned[,  1228 ] <- as.numeric(gene5408.cleaned[, 1228 ])
gene5408.cleaned[,  1229 ] <- as.numeric(gene5408.cleaned[, 1229 ])
gene5408.cleaned[,  1230 ] <- as.numeric(gene5408.cleaned[, 1230 ])
gene5408.cleaned[,  1231 ] <- as.numeric(gene5408.cleaned[, 1231 ])
gene5408.cleaned[,  1232 ] <- as.numeric(gene5408.cleaned[, 1232 ])
gene5408.cleaned[,  1233 ] <- as.numeric(gene5408.cleaned[, 1233 ])
gene5408.cleaned[,  1234 ] <- as.numeric(gene5408.cleaned[, 1234 ])
gene5408.cleaned[,  1235 ] <- as.numeric(gene5408.cleaned[, 1235 ])
gene5408.cleaned[,  1236 ] <- as.numeric(gene5408.cleaned[, 1236 ])
gene5408.cleaned[,  1237 ] <- as.numeric(gene5408.cleaned[, 1237 ])
gene5408.cleaned[,  1238 ] <- as.numeric(gene5408.cleaned[, 1238 ])
gene5408.cleaned[,  1239 ] <- as.numeric(gene5408.cleaned[, 1239 ])
gene5408.cleaned[,  1240 ] <- as.numeric(gene5408.cleaned[, 1240 ])
gene5408.cleaned[,  1241 ] <- as.numeric(gene5408.cleaned[, 1241 ])
gene5408.cleaned[,  1242 ] <- as.numeric(gene5408.cleaned[, 1242 ])
gene5408.cleaned[,  1243 ] <- as.numeric(gene5408.cleaned[, 1243 ])
gene5408.cleaned[,  1244 ] <- as.numeric(gene5408.cleaned[, 1244 ])
gene5408.cleaned[,  1245 ] <- as.numeric(gene5408.cleaned[, 1245 ])
gene5408.cleaned[,  1246 ] <- as.numeric(gene5408.cleaned[, 1246 ])
gene5408.cleaned[,  1247 ] <- as.numeric(gene5408.cleaned[, 1247 ])
gene5408.cleaned[,  1248 ] <- as.numeric(gene5408.cleaned[, 1248 ])
gene5408.cleaned[,  1249 ] <- as.numeric(gene5408.cleaned[, 1249 ])
gene5408.cleaned[,  1250 ] <- as.numeric(gene5408.cleaned[, 1250 ])
gene5408.cleaned[,  1251 ] <- as.numeric(gene5408.cleaned[, 1251 ])
gene5408.cleaned[,  1252 ] <- as.numeric(gene5408.cleaned[, 1252 ])
gene5408.cleaned[,  1253 ] <- as.numeric(gene5408.cleaned[, 1253 ])
gene5408.cleaned[,  1254 ] <- as.numeric(gene5408.cleaned[, 1254 ])
gene5408.cleaned[,  1255 ] <- as.numeric(gene5408.cleaned[, 1255 ])
gene5408.cleaned[,  1256 ] <- as.numeric(gene5408.cleaned[, 1256 ])
gene5408.cleaned[,  1257 ] <- as.numeric(gene5408.cleaned[, 1257 ])
gene5408.cleaned[,  1258 ] <- as.numeric(gene5408.cleaned[, 1258 ])
gene5408.cleaned[,  1259 ] <- as.numeric(gene5408.cleaned[, 1259 ])
gene5408.cleaned[,  1260 ] <- as.numeric(gene5408.cleaned[, 1260 ])
gene5408.cleaned[,  1261 ] <- as.numeric(gene5408.cleaned[, 1261 ])
gene5408.cleaned[,  1262 ] <- as.numeric(gene5408.cleaned[, 1262 ])
gene5408.cleaned[,  1263 ] <- as.numeric(gene5408.cleaned[, 1263 ])
gene5408.cleaned[,  1264 ] <- as.numeric(gene5408.cleaned[, 1264 ])
gene5408.cleaned[,  1265 ] <- as.numeric(gene5408.cleaned[, 1265 ])
gene5408.cleaned[,  1266 ] <- as.numeric(gene5408.cleaned[, 1266 ])
gene5408.cleaned[,  1267 ] <- as.numeric(gene5408.cleaned[, 1267 ])
gene5408.cleaned[,  1268 ] <- as.numeric(gene5408.cleaned[, 1268 ])
gene5408.cleaned[,  1269 ] <- as.numeric(gene5408.cleaned[, 1269 ])
gene5408.cleaned[,  1270 ] <- as.numeric(gene5408.cleaned[, 1270 ])
gene5408.cleaned[,  1271 ] <- as.numeric(gene5408.cleaned[, 1271 ])
gene5408.cleaned[,  1272 ] <- as.numeric(gene5408.cleaned[, 1272 ])
gene5408.cleaned[,  1273 ] <- as.numeric(gene5408.cleaned[, 1273 ])
gene5408.cleaned[,  1274 ] <- as.numeric(gene5408.cleaned[, 1274 ])
gene5408.cleaned[,  1275 ] <- as.numeric(gene5408.cleaned[, 1275 ])
gene5408.cleaned[,  1276 ] <- as.numeric(gene5408.cleaned[, 1276 ])
gene5408.cleaned[,  1277 ] <- as.numeric(gene5408.cleaned[, 1277 ])
gene5408.cleaned[,  1278 ] <- as.numeric(gene5408.cleaned[, 1278 ])
gene5408.cleaned[,  1279 ] <- as.numeric(gene5408.cleaned[, 1279 ])
gene5408.cleaned[,  1280 ] <- as.numeric(gene5408.cleaned[, 1280 ])
gene5408.cleaned[,  1281 ] <- as.numeric(gene5408.cleaned[, 1281 ])
gene5408.cleaned[,  1282 ] <- as.numeric(gene5408.cleaned[, 1282 ])
gene5408.cleaned[,  1283 ] <- as.numeric(gene5408.cleaned[, 1283 ])
gene5408.cleaned[,  1284 ] <- as.numeric(gene5408.cleaned[, 1284 ])
gene5408.cleaned[,  1285 ] <- as.numeric(gene5408.cleaned[, 1285 ])
gene5408.cleaned[,  1286 ] <- as.numeric(gene5408.cleaned[, 1286 ])
gene5408.cleaned[,  1287 ] <- as.numeric(gene5408.cleaned[, 1287 ])
gene5408.cleaned[,  1288 ] <- as.numeric(gene5408.cleaned[, 1288 ])
gene5408.cleaned[,  1289 ] <- as.numeric(gene5408.cleaned[, 1289 ])
gene5408.cleaned[,  1290 ] <- as.numeric(gene5408.cleaned[, 1290 ])
gene5408.cleaned[,  1291 ] <- as.numeric(gene5408.cleaned[, 1291 ])
gene5408.cleaned[,  1292 ] <- as.numeric(gene5408.cleaned[, 1292 ])
gene5408.cleaned[,  1293 ] <- as.numeric(gene5408.cleaned[, 1293 ])
gene5408.cleaned[,  1294 ] <- as.numeric(gene5408.cleaned[, 1294 ])
gene5408.cleaned[,  1295 ] <- as.numeric(gene5408.cleaned[, 1295 ])
gene5408.cleaned[,  1296 ] <- as.numeric(gene5408.cleaned[, 1296 ])
gene5408.cleaned[,  1297 ] <- as.numeric(gene5408.cleaned[, 1297 ])
gene5408.cleaned[,  1298 ] <- as.numeric(gene5408.cleaned[, 1298 ])
gene5408.cleaned[,  1299 ] <- as.numeric(gene5408.cleaned[, 1299 ])
gene5408.cleaned[,  1300 ] <- as.numeric(gene5408.cleaned[, 1300 ])
gene5408.cleaned[,  1301 ] <- as.numeric(gene5408.cleaned[, 1301 ])
gene5408.cleaned[,  1302 ] <- as.numeric(gene5408.cleaned[, 1302 ])
gene5408.cleaned[,  1303 ] <- as.numeric(gene5408.cleaned[, 1303 ])
gene5408.cleaned[,  1304 ] <- as.numeric(gene5408.cleaned[, 1304 ])
gene5408.cleaned[,  1305 ] <- as.numeric(gene5408.cleaned[, 1305 ])
gene5408.cleaned[,  1306 ] <- as.numeric(gene5408.cleaned[, 1306 ])
gene5408.cleaned[,  1307 ] <- as.numeric(gene5408.cleaned[, 1307 ])
gene5408.cleaned[,  1308 ] <- as.numeric(gene5408.cleaned[, 1308 ])
gene5408.cleaned[,  1309 ] <- as.numeric(gene5408.cleaned[, 1309 ])
gene5408.cleaned[,  1310 ] <- as.numeric(gene5408.cleaned[, 1310 ])
gene5408.cleaned[,  1311 ] <- as.numeric(gene5408.cleaned[, 1311 ])
gene5408.cleaned[,  1312 ] <- as.numeric(gene5408.cleaned[, 1312 ])
gene5408.cleaned[,  1313 ] <- as.numeric(gene5408.cleaned[, 1313 ])
gene5408.cleaned[,  1314 ] <- as.numeric(gene5408.cleaned[, 1314 ])
gene5408.cleaned[,  1315 ] <- as.numeric(gene5408.cleaned[, 1315 ])
gene5408.cleaned[,  1316 ] <- as.numeric(gene5408.cleaned[, 1316 ])
gene5408.cleaned[,  1317 ] <- as.numeric(gene5408.cleaned[, 1317 ])
gene5408.cleaned[,  1318 ] <- as.numeric(gene5408.cleaned[, 1318 ])
gene5408.cleaned[,  1319 ] <- as.numeric(gene5408.cleaned[, 1319 ])
gene5408.cleaned[,  1320 ] <- as.numeric(gene5408.cleaned[, 1320 ])
gene5408.cleaned[,  1321 ] <- as.numeric(gene5408.cleaned[, 1321 ])
gene5408.cleaned[,  1322 ] <- as.numeric(gene5408.cleaned[, 1322 ])
gene5408.cleaned[,  1323 ] <- as.numeric(gene5408.cleaned[, 1323 ])
gene5408.cleaned[,  1324 ] <- as.numeric(gene5408.cleaned[, 1324 ])
gene5408.cleaned[,  1325 ] <- as.numeric(gene5408.cleaned[, 1325 ])
gene5408.cleaned[,  1326 ] <- as.numeric(gene5408.cleaned[, 1326 ])
gene5408.cleaned[,  1327 ] <- as.numeric(gene5408.cleaned[, 1327 ])
gene5408.cleaned[,  1328 ] <- as.numeric(gene5408.cleaned[, 1328 ])
gene5408.cleaned[,  1329 ] <- as.numeric(gene5408.cleaned[, 1329 ])
gene5408.cleaned[,  1330 ] <- as.numeric(gene5408.cleaned[, 1330 ])
gene5408.cleaned[,  1331 ] <- as.numeric(gene5408.cleaned[, 1331 ])
gene5408.cleaned[,  1332 ] <- as.numeric(gene5408.cleaned[, 1332 ])
gene5408.cleaned[,  1333 ] <- as.numeric(gene5408.cleaned[, 1333 ])
gene5408.cleaned[,  1334 ] <- as.numeric(gene5408.cleaned[, 1334 ])
gene5408.cleaned[,  1335 ] <- as.numeric(gene5408.cleaned[, 1335 ])
gene5408.cleaned[,  1336 ] <- as.numeric(gene5408.cleaned[, 1336 ])
gene5408.cleaned[,  1337 ] <- as.numeric(gene5408.cleaned[, 1337 ])
gene5408.cleaned[,  1338 ] <- as.numeric(gene5408.cleaned[, 1338 ])
gene5408.cleaned[,  1339 ] <- as.numeric(gene5408.cleaned[, 1339 ])
gene5408.cleaned[,  1340 ] <- as.numeric(gene5408.cleaned[, 1340 ])
gene5408.cleaned[,  1341 ] <- as.numeric(gene5408.cleaned[, 1341 ])
gene5408.cleaned[,  1342 ] <- as.numeric(gene5408.cleaned[, 1342 ])
gene5408.cleaned[,  1343 ] <- as.numeric(gene5408.cleaned[, 1343 ])
gene5408.cleaned[,  1344 ] <- as.numeric(gene5408.cleaned[, 1344 ])
gene5408.cleaned[,  1345 ] <- as.numeric(gene5408.cleaned[, 1345 ])
gene5408.cleaned[,  1346 ] <- as.numeric(gene5408.cleaned[, 1346 ])
gene5408.cleaned[,  1347 ] <- as.numeric(gene5408.cleaned[, 1347 ])
gene5408.cleaned[,  1348 ] <- as.numeric(gene5408.cleaned[, 1348 ])
gene5408.cleaned[,  1349 ] <- as.numeric(gene5408.cleaned[, 1349 ])
gene5408.cleaned[,  1350 ] <- as.numeric(gene5408.cleaned[, 1350 ])
gene5408.cleaned[,  1351 ] <- as.numeric(gene5408.cleaned[, 1351 ])
gene5408.cleaned[,  1352 ] <- as.numeric(gene5408.cleaned[, 1352 ])
gene5408.cleaned[,  1353 ] <- as.numeric(gene5408.cleaned[, 1353 ])
gene5408.cleaned[,  1354 ] <- as.numeric(gene5408.cleaned[, 1354 ])
gene5408.cleaned[,  1355 ] <- as.numeric(gene5408.cleaned[, 1355 ])
gene5408.cleaned[,  1356 ] <- as.numeric(gene5408.cleaned[, 1356 ])
gene5408.cleaned[,  1357 ] <- as.numeric(gene5408.cleaned[, 1357 ])
gene5408.cleaned[,  1358 ] <- as.numeric(gene5408.cleaned[, 1358 ])
gene5408.cleaned[,  1359 ] <- as.numeric(gene5408.cleaned[, 1359 ])
gene5408.cleaned[,  1360 ] <- as.numeric(gene5408.cleaned[, 1360 ])
gene5408.cleaned[,  1361 ] <- as.numeric(gene5408.cleaned[, 1361 ])
gene5408.cleaned[,  1362 ] <- as.numeric(gene5408.cleaned[, 1362 ])
gene5408.cleaned[,  1363 ] <- as.numeric(gene5408.cleaned[, 1363 ])
gene5408.cleaned[,  1364 ] <- as.numeric(gene5408.cleaned[, 1364 ])
gene5408.cleaned[,  1365 ] <- as.numeric(gene5408.cleaned[, 1365 ])
gene5408.cleaned[,  1366 ] <- as.numeric(gene5408.cleaned[, 1366 ])
gene5408.cleaned[,  1367 ] <- as.numeric(gene5408.cleaned[, 1367 ])
gene5408.cleaned[,  1368 ] <- as.numeric(gene5408.cleaned[, 1368 ])
gene5408.cleaned[,  1369 ] <- as.numeric(gene5408.cleaned[, 1369 ])
gene5408.cleaned[,  1370 ] <- as.numeric(gene5408.cleaned[, 1370 ])
gene5408.cleaned[,  1371 ] <- as.numeric(gene5408.cleaned[, 1371 ])
gene5408.cleaned[,  1372 ] <- as.numeric(gene5408.cleaned[, 1372 ])
gene5408.cleaned[,  1373 ] <- as.numeric(gene5408.cleaned[, 1373 ])
gene5408.cleaned[,  1374 ] <- as.numeric(gene5408.cleaned[, 1374 ])
gene5408.cleaned[,  1375 ] <- as.numeric(gene5408.cleaned[, 1375 ])
gene5408.cleaned[,  1376 ] <- as.numeric(gene5408.cleaned[, 1376 ])
gene5408.cleaned[,  1377 ] <- as.numeric(gene5408.cleaned[, 1377 ])
gene5408.cleaned[,  1378 ] <- as.numeric(gene5408.cleaned[, 1378 ])
gene5408.cleaned[,  1379 ] <- as.numeric(gene5408.cleaned[, 1379 ])
gene5408.cleaned[,  1380 ] <- as.numeric(gene5408.cleaned[, 1380 ])
gene5408.cleaned[,  1381 ] <- as.numeric(gene5408.cleaned[, 1381 ])
gene5408.cleaned[,  1382 ] <- as.numeric(gene5408.cleaned[, 1382 ])
gene5408.cleaned[,  1383 ] <- as.numeric(gene5408.cleaned[, 1383 ])
gene5408.cleaned[,  1384 ] <- as.numeric(gene5408.cleaned[, 1384 ])
gene5408.cleaned[,  1385 ] <- as.numeric(gene5408.cleaned[, 1385 ])
gene5408.cleaned[,  1386 ] <- as.numeric(gene5408.cleaned[, 1386 ])
gene5408.cleaned[,  1387 ] <- as.numeric(gene5408.cleaned[, 1387 ])
gene5408.cleaned[,  1388 ] <- as.numeric(gene5408.cleaned[, 1388 ])
gene5408.cleaned[,  1389 ] <- as.numeric(gene5408.cleaned[, 1389 ])
gene5408.cleaned[,  1390 ] <- as.numeric(gene5408.cleaned[, 1390 ])
gene5408.cleaned[,  1391 ] <- as.numeric(gene5408.cleaned[, 1391 ])
gene5408.cleaned[,  1392 ] <- as.numeric(gene5408.cleaned[, 1392 ])
gene5408.cleaned[,  1393 ] <- as.numeric(gene5408.cleaned[, 1393 ])
gene5408.cleaned[,  1394 ] <- as.numeric(gene5408.cleaned[, 1394 ])
gene5408.cleaned[,  1395 ] <- as.numeric(gene5408.cleaned[, 1395 ])
gene5408.cleaned[,  1396 ] <- as.numeric(gene5408.cleaned[, 1396 ])
gene5408.cleaned[,  1397 ] <- as.numeric(gene5408.cleaned[, 1397 ])
gene5408.cleaned[,  1398 ] <- as.numeric(gene5408.cleaned[, 1398 ])
gene5408.cleaned[,  1399 ] <- as.numeric(gene5408.cleaned[, 1399 ])
gene5408.cleaned[,  1400 ] <- as.numeric(gene5408.cleaned[, 1400 ])
gene5408.cleaned[,  1401 ] <- as.numeric(gene5408.cleaned[, 1401 ])
gene5408.cleaned[,  1402 ] <- as.numeric(gene5408.cleaned[, 1402 ])
gene5408.cleaned[,  1403 ] <- as.numeric(gene5408.cleaned[, 1403 ])
gene5408.cleaned[,  1404 ] <- as.numeric(gene5408.cleaned[, 1404 ])
gene5408.cleaned[,  1405 ] <- as.numeric(gene5408.cleaned[, 1405 ])
gene5408.cleaned[,  1406 ] <- as.numeric(gene5408.cleaned[, 1406 ])
gene5408.cleaned[,  1407 ] <- as.numeric(gene5408.cleaned[, 1407 ])
gene5408.cleaned[,  1408 ] <- as.numeric(gene5408.cleaned[, 1408 ])
gene5408.cleaned[,  1409 ] <- as.numeric(gene5408.cleaned[, 1409 ])
gene5408.cleaned[,  1410 ] <- as.numeric(gene5408.cleaned[, 1410 ])
gene5408.cleaned[,  1411 ] <- as.numeric(gene5408.cleaned[, 1411 ])
gene5408.cleaned[,  1412 ] <- as.numeric(gene5408.cleaned[, 1412 ])
gene5408.cleaned[,  1413 ] <- as.numeric(gene5408.cleaned[, 1413 ])
gene5408.cleaned[,  1414 ] <- as.numeric(gene5408.cleaned[, 1414 ])
gene5408.cleaned[,  1415 ] <- as.numeric(gene5408.cleaned[, 1415 ])
gene5408.cleaned[,  1416 ] <- as.numeric(gene5408.cleaned[, 1416 ])
gene5408.cleaned[,  1417 ] <- as.numeric(gene5408.cleaned[, 1417 ])
gene5408.cleaned[,  1418 ] <- as.numeric(gene5408.cleaned[, 1418 ])
gene5408.cleaned[,  1419 ] <- as.numeric(gene5408.cleaned[, 1419 ])
gene5408.cleaned[,  1420 ] <- as.numeric(gene5408.cleaned[, 1420 ])
gene5408.cleaned[,  1421 ] <- as.numeric(gene5408.cleaned[, 1421 ])
gene5408.cleaned[,  1422 ] <- as.numeric(gene5408.cleaned[, 1422 ])
gene5408.cleaned[,  1423 ] <- as.numeric(gene5408.cleaned[, 1423 ])
gene5408.cleaned[,  1424 ] <- as.numeric(gene5408.cleaned[, 1424 ])
gene5408.cleaned[,  1425 ] <- as.numeric(gene5408.cleaned[, 1425 ])
gene5408.cleaned[,  1426 ] <- as.numeric(gene5408.cleaned[, 1426 ])
gene5408.cleaned[,  1427 ] <- as.numeric(gene5408.cleaned[, 1427 ])
gene5408.cleaned[,  1428 ] <- as.numeric(gene5408.cleaned[, 1428 ])
gene5408.cleaned[,  1429 ] <- as.numeric(gene5408.cleaned[, 1429 ])
gene5408.cleaned[,  1430 ] <- as.numeric(gene5408.cleaned[, 1430 ])
gene5408.cleaned[,  1431 ] <- as.numeric(gene5408.cleaned[, 1431 ])
gene5408.cleaned[,  1432 ] <- as.numeric(gene5408.cleaned[, 1432 ])
gene5408.cleaned[,  1433 ] <- as.numeric(gene5408.cleaned[, 1433 ])
gene5408.cleaned[,  1434 ] <- as.numeric(gene5408.cleaned[, 1434 ])
gene5408.cleaned[,  1435 ] <- as.numeric(gene5408.cleaned[, 1435 ])
gene5408.cleaned[,  1436 ] <- as.numeric(gene5408.cleaned[, 1436 ])
gene5408.cleaned[,  1437 ] <- as.numeric(gene5408.cleaned[, 1437 ])
gene5408.cleaned[,  1438 ] <- as.numeric(gene5408.cleaned[, 1438 ])
gene5408.cleaned[,  1439 ] <- as.numeric(gene5408.cleaned[, 1439 ])
gene5408.cleaned[,  1440 ] <- as.numeric(gene5408.cleaned[, 1440 ])
gene5408.cleaned[,  1441 ] <- as.numeric(gene5408.cleaned[, 1441 ])
gene5408.cleaned[,  1442 ] <- as.numeric(gene5408.cleaned[, 1442 ])
gene5408.cleaned[,  1443 ] <- as.numeric(gene5408.cleaned[, 1443 ])
gene5408.cleaned[,  1444 ] <- as.numeric(gene5408.cleaned[, 1444 ])
gene5408.cleaned[,  1445 ] <- as.numeric(gene5408.cleaned[, 1445 ])
gene5408.cleaned[,  1446 ] <- as.numeric(gene5408.cleaned[, 1446 ])
gene5408.cleaned[,  1447 ] <- as.numeric(gene5408.cleaned[, 1447 ])
gene5408.cleaned[,  1448 ] <- as.numeric(gene5408.cleaned[, 1448 ])
gene5408.cleaned[,  1449 ] <- as.numeric(gene5408.cleaned[, 1449 ])
gene5408.cleaned[,  1450 ] <- as.numeric(gene5408.cleaned[, 1450 ])
gene5408.cleaned[,  1451 ] <- as.numeric(gene5408.cleaned[, 1451 ])
gene5408.cleaned[,  1452 ] <- as.numeric(gene5408.cleaned[, 1452 ])
gene5408.cleaned[,  1453 ] <- as.numeric(gene5408.cleaned[, 1453 ])
gene5408.cleaned[,  1454 ] <- as.numeric(gene5408.cleaned[, 1454 ])
gene5408.cleaned[,  1455 ] <- as.numeric(gene5408.cleaned[, 1455 ])
gene5408.cleaned[,  1456 ] <- as.numeric(gene5408.cleaned[, 1456 ])
gene5408.cleaned[,  1457 ] <- as.numeric(gene5408.cleaned[, 1457 ])
gene5408.cleaned[,  1458 ] <- as.numeric(gene5408.cleaned[, 1458 ])
gene5408.cleaned[,  1459 ] <- as.numeric(gene5408.cleaned[, 1459 ])
gene5408.cleaned[,  1460 ] <- as.numeric(gene5408.cleaned[, 1460 ])
gene5408.cleaned[,  1461 ] <- as.numeric(gene5408.cleaned[, 1461 ])
gene5408.cleaned[,  1462 ] <- as.numeric(gene5408.cleaned[, 1462 ])
gene5408.cleaned[,  1463 ] <- as.numeric(gene5408.cleaned[, 1463 ])
gene5408.cleaned[,  1464 ] <- as.numeric(gene5408.cleaned[, 1464 ])
gene5408.cleaned[,  1465 ] <- as.numeric(gene5408.cleaned[, 1465 ])
gene5408.cleaned[,  1466 ] <- as.numeric(gene5408.cleaned[, 1466 ])
gene5408.cleaned[,  1467 ] <- as.numeric(gene5408.cleaned[, 1467 ])
gene5408.cleaned[,  1468 ] <- as.numeric(gene5408.cleaned[, 1468 ])
gene5408.cleaned[,  1469 ] <- as.numeric(gene5408.cleaned[, 1469 ])
gene5408.cleaned[,  1470 ] <- as.numeric(gene5408.cleaned[, 1470 ])
gene5408.cleaned[,  1471 ] <- as.numeric(gene5408.cleaned[, 1471 ])
gene5408.cleaned[,  1472 ] <- as.numeric(gene5408.cleaned[, 1472 ])
gene5408.cleaned[,  1473 ] <- as.numeric(gene5408.cleaned[, 1473 ])
gene5408.cleaned[,  1474 ] <- as.numeric(gene5408.cleaned[, 1474 ])
gene5408.cleaned[,  1475 ] <- as.numeric(gene5408.cleaned[, 1475 ])
gene5408.cleaned[,  1476 ] <- as.numeric(gene5408.cleaned[, 1476 ])
gene5408.cleaned[,  1477 ] <- as.numeric(gene5408.cleaned[, 1477 ])
gene5408.cleaned[,  1478 ] <- as.numeric(gene5408.cleaned[, 1478 ])
gene5408.cleaned[,  1479 ] <- as.numeric(gene5408.cleaned[, 1479 ])
gene5408.cleaned[,  1480 ] <- as.numeric(gene5408.cleaned[, 1480 ])
gene5408.cleaned[,  1481 ] <- as.numeric(gene5408.cleaned[, 1481 ])
gene5408.cleaned[,  1482 ] <- as.numeric(gene5408.cleaned[, 1482 ])
gene5408.cleaned[,  1483 ] <- as.numeric(gene5408.cleaned[, 1483 ])
gene5408.cleaned[,  1484 ] <- as.numeric(gene5408.cleaned[, 1484 ])
gene5408.cleaned[,  1485 ] <- as.numeric(gene5408.cleaned[, 1485 ])
gene5408.cleaned[,  1486 ] <- as.numeric(gene5408.cleaned[, 1486 ])
gene5408.cleaned[,  1487 ] <- as.numeric(gene5408.cleaned[, 1487 ])
gene5408.cleaned[,  1488 ] <- as.numeric(gene5408.cleaned[, 1488 ])
gene5408.cleaned[,  1489 ] <- as.numeric(gene5408.cleaned[, 1489 ])
gene5408.cleaned[,  1490 ] <- as.numeric(gene5408.cleaned[, 1490 ])
gene5408.cleaned[,  1491 ] <- as.numeric(gene5408.cleaned[, 1491 ])
gene5408.cleaned[,  1492 ] <- as.numeric(gene5408.cleaned[, 1492 ])
gene5408.cleaned[,  1493 ] <- as.numeric(gene5408.cleaned[, 1493 ])
gene5408.cleaned[,  1494 ] <- as.numeric(gene5408.cleaned[, 1494 ])
gene5408.cleaned[,  1495 ] <- as.numeric(gene5408.cleaned[, 1495 ])
gene5408.cleaned[,  1496 ] <- as.numeric(gene5408.cleaned[, 1496 ])
gene5408.cleaned[,  1497 ] <- as.numeric(gene5408.cleaned[, 1497 ])
gene5408.cleaned[,  1498 ] <- as.numeric(gene5408.cleaned[, 1498 ])
gene5408.cleaned[,  1499 ] <- as.numeric(gene5408.cleaned[, 1499 ])
gene5408.cleaned[,  1500 ] <- as.numeric(gene5408.cleaned[, 1500 ])
gene5408.cleaned[,  1501 ] <- as.numeric(gene5408.cleaned[, 1501 ])
gene5408.cleaned[,  1502 ] <- as.numeric(gene5408.cleaned[, 1502 ])
gene5408.cleaned[,  1503 ] <- as.numeric(gene5408.cleaned[, 1503 ])
gene5408.cleaned[,  1504 ] <- as.numeric(gene5408.cleaned[, 1504 ])
gene5408.cleaned[,  1505 ] <- as.numeric(gene5408.cleaned[, 1505 ])
gene5408.cleaned[,  1506 ] <- as.numeric(gene5408.cleaned[, 1506 ])
gene5408.cleaned[,  1507 ] <- as.numeric(gene5408.cleaned[, 1507 ])
gene5408.cleaned[,  1508 ] <- as.numeric(gene5408.cleaned[, 1508 ])
gene5408.cleaned[,  1509 ] <- as.numeric(gene5408.cleaned[, 1509 ])
gene5408.cleaned[,  1510 ] <- as.numeric(gene5408.cleaned[, 1510 ])
gene5408.cleaned[,  1511 ] <- as.numeric(gene5408.cleaned[, 1511 ])
gene5408.cleaned[,  1512 ] <- as.numeric(gene5408.cleaned[, 1512 ])
gene5408.cleaned[,  1513 ] <- as.numeric(gene5408.cleaned[, 1513 ])
gene5408.cleaned[,  1514 ] <- as.numeric(gene5408.cleaned[, 1514 ])
gene5408.cleaned[,  1515 ] <- as.numeric(gene5408.cleaned[, 1515 ])
gene5408.cleaned[,  1516 ] <- as.numeric(gene5408.cleaned[, 1516 ])
gene5408.cleaned[,  1517 ] <- as.numeric(gene5408.cleaned[, 1517 ])
gene5408.cleaned[,  1518 ] <- as.numeric(gene5408.cleaned[, 1518 ])
gene5408.cleaned[,  1519 ] <- as.numeric(gene5408.cleaned[, 1519 ])
gene5408.cleaned[,  1520 ] <- as.numeric(gene5408.cleaned[, 1520 ])
gene5408.cleaned[,  1521 ] <- as.numeric(gene5408.cleaned[, 1521 ])
gene5408.cleaned[,  1522 ] <- as.numeric(gene5408.cleaned[, 1522 ])
gene5408.cleaned[,  1523 ] <- as.numeric(gene5408.cleaned[, 1523 ])
gene5408.cleaned[,  1524 ] <- as.numeric(gene5408.cleaned[, 1524 ])
gene5408.cleaned[,  1525 ] <- as.numeric(gene5408.cleaned[, 1525 ])
gene5408.cleaned[,  1526 ] <- as.numeric(gene5408.cleaned[, 1526 ])
gene5408.cleaned[,  1527 ] <- as.numeric(gene5408.cleaned[, 1527 ])
gene5408.cleaned[,  1528 ] <- as.numeric(gene5408.cleaned[, 1528 ])
gene5408.cleaned[,  1529 ] <- as.numeric(gene5408.cleaned[, 1529 ])
gene5408.cleaned[,  1530 ] <- as.numeric(gene5408.cleaned[, 1530 ])
gene5408.cleaned[,  1531 ] <- as.numeric(gene5408.cleaned[, 1531 ])
gene5408.cleaned[,  1532 ] <- as.numeric(gene5408.cleaned[, 1532 ])
gene5408.cleaned[,  1533 ] <- as.numeric(gene5408.cleaned[, 1533 ])
gene5408.cleaned[,  1534 ] <- as.numeric(gene5408.cleaned[, 1534 ])
gene5408.cleaned[,  1535 ] <- as.numeric(gene5408.cleaned[, 1535 ])
gene5408.cleaned[,  1536 ] <- as.numeric(gene5408.cleaned[, 1536 ])
gene5408.cleaned[,  1537 ] <- as.numeric(gene5408.cleaned[, 1537 ])
gene5408.cleaned[,  1538 ] <- as.numeric(gene5408.cleaned[, 1538 ])
gene5408.cleaned[,  1539 ] <- as.numeric(gene5408.cleaned[, 1539 ])
gene5408.cleaned[,  1540 ] <- as.numeric(gene5408.cleaned[, 1540 ])
gene5408.cleaned[,  1541 ] <- as.numeric(gene5408.cleaned[, 1541 ])
gene5408.cleaned[,  1542 ] <- as.numeric(gene5408.cleaned[, 1542 ])
gene5408.cleaned[,  1543 ] <- as.numeric(gene5408.cleaned[, 1543 ])
gene5408.cleaned[,  1544 ] <- as.numeric(gene5408.cleaned[, 1544 ])
gene5408.cleaned[,  1545 ] <- as.numeric(gene5408.cleaned[, 1545 ])
gene5408.cleaned[,  1546 ] <- as.numeric(gene5408.cleaned[, 1546 ])
gene5408.cleaned[,  1547 ] <- as.numeric(gene5408.cleaned[, 1547 ])
gene5408.cleaned[,  1548 ] <- as.numeric(gene5408.cleaned[, 1548 ])
gene5408.cleaned[,  1549 ] <- as.numeric(gene5408.cleaned[, 1549 ])
gene5408.cleaned[,  1550 ] <- as.numeric(gene5408.cleaned[, 1550 ])
gene5408.cleaned[,  1551 ] <- as.numeric(gene5408.cleaned[, 1551 ])
gene5408.cleaned[,  1552 ] <- as.numeric(gene5408.cleaned[, 1552 ])
gene5408.cleaned[,  1553 ] <- as.numeric(gene5408.cleaned[, 1553 ])
gene5408.cleaned[,  1554 ] <- as.numeric(gene5408.cleaned[, 1554 ])
gene5408.cleaned[,  1555 ] <- as.numeric(gene5408.cleaned[, 1555 ])
gene5408.cleaned[,  1556 ] <- as.numeric(gene5408.cleaned[, 1556 ])
gene5408.cleaned[,  1557 ] <- as.numeric(gene5408.cleaned[, 1557 ])
gene5408.cleaned[,  1558 ] <- as.numeric(gene5408.cleaned[, 1558 ])
gene5408.cleaned[,  1559 ] <- as.numeric(gene5408.cleaned[, 1559 ])
gene5408.cleaned[,  1560 ] <- as.numeric(gene5408.cleaned[, 1560 ])
gene5408.cleaned[,  1561 ] <- as.numeric(gene5408.cleaned[, 1561 ])
gene5408.cleaned[,  1562 ] <- as.numeric(gene5408.cleaned[, 1562 ])
gene5408.cleaned[,  1563 ] <- as.numeric(gene5408.cleaned[, 1563 ])
gene5408.cleaned[,  1564 ] <- as.numeric(gene5408.cleaned[, 1564 ])
gene5408.cleaned[,  1565 ] <- as.numeric(gene5408.cleaned[, 1565 ])
gene5408.cleaned[,  1566 ] <- as.numeric(gene5408.cleaned[, 1566 ])
gene5408.cleaned[,  1567 ] <- as.numeric(gene5408.cleaned[, 1567 ])
gene5408.cleaned[,  1568 ] <- as.numeric(gene5408.cleaned[, 1568 ])
gene5408.cleaned[,  1569 ] <- as.numeric(gene5408.cleaned[, 1569 ])
gene5408.cleaned[,  1570 ] <- as.numeric(gene5408.cleaned[, 1570 ])
gene5408.cleaned[,  1571 ] <- as.numeric(gene5408.cleaned[, 1571 ])
gene5408.cleaned[,  1572 ] <- as.numeric(gene5408.cleaned[, 1572 ])
gene5408.cleaned[,  1573 ] <- as.numeric(gene5408.cleaned[, 1573 ])
gene5408.cleaned[,  1574 ] <- as.numeric(gene5408.cleaned[, 1574 ])
gene5408.cleaned[,  1575 ] <- as.numeric(gene5408.cleaned[, 1575 ])
gene5408.cleaned[,  1576 ] <- as.numeric(gene5408.cleaned[, 1576 ])
gene5408.cleaned[,  1577 ] <- as.numeric(gene5408.cleaned[, 1577 ])
gene5408.cleaned[,  1578 ] <- as.numeric(gene5408.cleaned[, 1578 ])
gene5408.cleaned[,  1579 ] <- as.numeric(gene5408.cleaned[, 1579 ])
gene5408.cleaned[,  1580 ] <- as.numeric(gene5408.cleaned[, 1580 ])
gene5408.cleaned[,  1581 ] <- as.numeric(gene5408.cleaned[, 1581 ])
gene5408.cleaned[,  1582 ] <- as.numeric(gene5408.cleaned[, 1582 ])
gene5408.cleaned[,  1583 ] <- as.numeric(gene5408.cleaned[, 1583 ])
gene5408.cleaned[,  1584 ] <- as.numeric(gene5408.cleaned[, 1584 ])
gene5408.cleaned[,  1585 ] <- as.numeric(gene5408.cleaned[, 1585 ])
gene5408.cleaned[,  1586 ] <- as.numeric(gene5408.cleaned[, 1586 ])
gene5408.cleaned[,  1587 ] <- as.numeric(gene5408.cleaned[, 1587 ])
gene5408.cleaned[,  1588 ] <- as.numeric(gene5408.cleaned[, 1588 ])
gene5408.cleaned[,  1589 ] <- as.numeric(gene5408.cleaned[, 1589 ])
gene5408.cleaned[,  1590 ] <- as.numeric(gene5408.cleaned[, 1590 ])
gene5408.cleaned[,  1591 ] <- as.numeric(gene5408.cleaned[, 1591 ])
gene5408.cleaned[,  1592 ] <- as.numeric(gene5408.cleaned[, 1592 ])
gene5408.cleaned[,  1593 ] <- as.numeric(gene5408.cleaned[, 1593 ])
gene5408.cleaned[,  1594 ] <- as.numeric(gene5408.cleaned[, 1594 ])
gene5408.cleaned[,  1595 ] <- as.numeric(gene5408.cleaned[, 1595 ])
gene5408.cleaned[,  1596 ] <- as.numeric(gene5408.cleaned[, 1596 ])
gene5408.cleaned[,  1597 ] <- as.numeric(gene5408.cleaned[, 1597 ])
gene5408.cleaned[,  1598 ] <- as.numeric(gene5408.cleaned[, 1598 ])
gene5408.cleaned[,  1599 ] <- as.numeric(gene5408.cleaned[, 1599 ])
gene5408.cleaned[,  1600 ] <- as.numeric(gene5408.cleaned[, 1600 ])
gene5408.cleaned[,  1601 ] <- as.numeric(gene5408.cleaned[, 1601 ])
gene5408.cleaned[,  1602 ] <- as.numeric(gene5408.cleaned[, 1602 ])
gene5408.cleaned[,  1603 ] <- as.numeric(gene5408.cleaned[, 1603 ])
gene5408.cleaned[,  1604 ] <- as.numeric(gene5408.cleaned[, 1604 ])
gene5408.cleaned[,  1605 ] <- as.numeric(gene5408.cleaned[, 1605 ])
gene5408.cleaned[,  1606 ] <- as.numeric(gene5408.cleaned[, 1606 ])
gene5408.cleaned[,  1607 ] <- as.numeric(gene5408.cleaned[, 1607 ])
gene5408.cleaned[,  1608 ] <- as.numeric(gene5408.cleaned[, 1608 ])
gene5408.cleaned[,  1609 ] <- as.numeric(gene5408.cleaned[, 1609 ])
gene5408.cleaned[,  1610 ] <- as.numeric(gene5408.cleaned[, 1610 ])
gene5408.cleaned[,  1611 ] <- as.numeric(gene5408.cleaned[, 1611 ])
gene5408.cleaned[,  1612 ] <- as.numeric(gene5408.cleaned[, 1612 ])
gene5408.cleaned[,  1613 ] <- as.numeric(gene5408.cleaned[, 1613 ])
gene5408.cleaned[,  1614 ] <- as.numeric(gene5408.cleaned[, 1614 ])
gene5408.cleaned[,  1615 ] <- as.numeric(gene5408.cleaned[, 1615 ])
gene5408.cleaned[,  1616 ] <- as.numeric(gene5408.cleaned[, 1616 ])
gene5408.cleaned[,  1617 ] <- as.numeric(gene5408.cleaned[, 1617 ])
gene5408.cleaned[,  1618 ] <- as.numeric(gene5408.cleaned[, 1618 ])
gene5408.cleaned[,  1619 ] <- as.numeric(gene5408.cleaned[, 1619 ])
gene5408.cleaned[,  1620 ] <- as.numeric(gene5408.cleaned[, 1620 ])
gene5408.cleaned[,  1621 ] <- as.numeric(gene5408.cleaned[, 1621 ])
gene5408.cleaned[,  1622 ] <- as.numeric(gene5408.cleaned[, 1622 ])
gene5408.cleaned[,  1623 ] <- as.numeric(gene5408.cleaned[, 1623 ])
gene5408.cleaned[,  1624 ] <- as.numeric(gene5408.cleaned[, 1624 ])
gene5408.cleaned[,  1625 ] <- as.numeric(gene5408.cleaned[, 1625 ])
gene5408.cleaned[,  1626 ] <- as.numeric(gene5408.cleaned[, 1626 ])
gene5408.cleaned[,  1627 ] <- as.numeric(gene5408.cleaned[, 1627 ])
gene5408.cleaned[,  1628 ] <- as.numeric(gene5408.cleaned[, 1628 ])
gene5408.cleaned[,  1629 ] <- as.numeric(gene5408.cleaned[, 1629 ])
gene5408.cleaned[,  1630 ] <- as.numeric(gene5408.cleaned[, 1630 ])
gene5408.cleaned[,  1631 ] <- as.numeric(gene5408.cleaned[, 1631 ])
gene5408.cleaned[,  1632 ] <- as.numeric(gene5408.cleaned[, 1632 ])
gene5408.cleaned[,  1633 ] <- as.numeric(gene5408.cleaned[, 1633 ])
gene5408.cleaned[,  1634 ] <- as.numeric(gene5408.cleaned[, 1634 ])
gene5408.cleaned[,  1635 ] <- as.numeric(gene5408.cleaned[, 1635 ])
gene5408.cleaned[,  1636 ] <- as.numeric(gene5408.cleaned[, 1636 ])
gene5408.cleaned[,  1637 ] <- as.numeric(gene5408.cleaned[, 1637 ])
gene5408.cleaned[,  1638 ] <- as.numeric(gene5408.cleaned[, 1638 ])
gene5408.cleaned[,  1639 ] <- as.numeric(gene5408.cleaned[, 1639 ])
gene5408.cleaned[,  1640 ] <- as.numeric(gene5408.cleaned[, 1640 ])
gene5408.cleaned[,  1641 ] <- as.numeric(gene5408.cleaned[, 1641 ])
gene5408.cleaned[,  1642 ] <- as.numeric(gene5408.cleaned[, 1642 ])
gene5408.cleaned[,  1643 ] <- as.numeric(gene5408.cleaned[, 1643 ])
gene5408.cleaned[,  1644 ] <- as.numeric(gene5408.cleaned[, 1644 ])
gene5408.cleaned[,  1645 ] <- as.numeric(gene5408.cleaned[, 1645 ])
gene5408.cleaned[,  1646 ] <- as.numeric(gene5408.cleaned[, 1646 ])
gene5408.cleaned[,  1647 ] <- as.numeric(gene5408.cleaned[, 1647 ])
gene5408.cleaned[,  1648 ] <- as.numeric(gene5408.cleaned[, 1648 ])
gene5408.cleaned[,  1649 ] <- as.numeric(gene5408.cleaned[, 1649 ])
gene5408.cleaned[,  1650 ] <- as.numeric(gene5408.cleaned[, 1650 ])
gene5408.cleaned[,  1651 ] <- as.numeric(gene5408.cleaned[, 1651 ])
gene5408.cleaned[,  1652 ] <- as.numeric(gene5408.cleaned[, 1652 ])
gene5408.cleaned[,  1653 ] <- as.numeric(gene5408.cleaned[, 1653 ])
gene5408.cleaned[,  1654 ] <- as.numeric(gene5408.cleaned[, 1654 ])
gene5408.cleaned[,  1655 ] <- as.numeric(gene5408.cleaned[, 1655 ])
gene5408.cleaned[,  1656 ] <- as.numeric(gene5408.cleaned[, 1656 ])
gene5408.cleaned[,  1657 ] <- as.numeric(gene5408.cleaned[, 1657 ])
gene5408.cleaned[,  1658 ] <- as.numeric(gene5408.cleaned[, 1658 ])
gene5408.cleaned[,  1659 ] <- as.numeric(gene5408.cleaned[, 1659 ])
gene5408.cleaned[,  1660 ] <- as.numeric(gene5408.cleaned[, 1660 ])
gene5408.cleaned[,  1661 ] <- as.numeric(gene5408.cleaned[, 1661 ])
gene5408.cleaned[,  1662 ] <- as.numeric(gene5408.cleaned[, 1662 ])
gene5408.cleaned[,  1663 ] <- as.numeric(gene5408.cleaned[, 1663 ])
gene5408.cleaned[,  1664 ] <- as.numeric(gene5408.cleaned[, 1664 ])
gene5408.cleaned[,  1665 ] <- as.numeric(gene5408.cleaned[, 1665 ])
gene5408.cleaned[,  1666 ] <- as.numeric(gene5408.cleaned[, 1666 ])
gene5408.cleaned[,  1667 ] <- as.numeric(gene5408.cleaned[, 1667 ])
gene5408.cleaned[,  1668 ] <- as.numeric(gene5408.cleaned[, 1668 ])
gene5408.cleaned[,  1669 ] <- as.numeric(gene5408.cleaned[, 1669 ])
gene5408.cleaned[,  1670 ] <- as.numeric(gene5408.cleaned[, 1670 ])
gene5408.cleaned[,  1671 ] <- as.numeric(gene5408.cleaned[, 1671 ])
gene5408.cleaned[,  1672 ] <- as.numeric(gene5408.cleaned[, 1672 ])
gene5408.cleaned[,  1673 ] <- as.numeric(gene5408.cleaned[, 1673 ])
gene5408.cleaned[,  1674 ] <- as.numeric(gene5408.cleaned[, 1674 ])
gene5408.cleaned[,  1675 ] <- as.numeric(gene5408.cleaned[, 1675 ])
gene5408.cleaned[,  1676 ] <- as.numeric(gene5408.cleaned[, 1676 ])
gene5408.cleaned[,  1677 ] <- as.numeric(gene5408.cleaned[, 1677 ])
gene5408.cleaned[,  1678 ] <- as.numeric(gene5408.cleaned[, 1678 ])
gene5408.cleaned[,  1679 ] <- as.numeric(gene5408.cleaned[, 1679 ])
gene5408.cleaned[,  1680 ] <- as.numeric(gene5408.cleaned[, 1680 ])
gene5408.cleaned[,  1681 ] <- as.numeric(gene5408.cleaned[, 1681 ])
gene5408.cleaned[,  1682 ] <- as.numeric(gene5408.cleaned[, 1682 ])
gene5408.cleaned[,  1683 ] <- as.numeric(gene5408.cleaned[, 1683 ])
gene5408.cleaned[,  1684 ] <- as.numeric(gene5408.cleaned[, 1684 ])
gene5408.cleaned[,  1685 ] <- as.numeric(gene5408.cleaned[, 1685 ])
gene5408.cleaned[,  1686 ] <- as.numeric(gene5408.cleaned[, 1686 ])
gene5408.cleaned[,  1687 ] <- as.numeric(gene5408.cleaned[, 1687 ])
gene5408.cleaned[,  1688 ] <- as.numeric(gene5408.cleaned[, 1688 ])
gene5408.cleaned[,  1689 ] <- as.numeric(gene5408.cleaned[, 1689 ])
gene5408.cleaned[,  1690 ] <- as.numeric(gene5408.cleaned[, 1690 ])
gene5408.cleaned[,  1691 ] <- as.numeric(gene5408.cleaned[, 1691 ])
gene5408.cleaned[,  1692 ] <- as.numeric(gene5408.cleaned[, 1692 ])
gene5408.cleaned[,  1693 ] <- as.numeric(gene5408.cleaned[, 1693 ])
gene5408.cleaned[,  1694 ] <- as.numeric(gene5408.cleaned[, 1694 ])
gene5408.cleaned[,  1695 ] <- as.numeric(gene5408.cleaned[, 1695 ])
gene5408.cleaned[,  1696 ] <- as.numeric(gene5408.cleaned[, 1696 ])
gene5408.cleaned[,  1697 ] <- as.numeric(gene5408.cleaned[, 1697 ])
gene5408.cleaned[,  1698 ] <- as.numeric(gene5408.cleaned[, 1698 ])
gene5408.cleaned[,  1699 ] <- as.numeric(gene5408.cleaned[, 1699 ])
gene5408.cleaned[,  1700 ] <- as.numeric(gene5408.cleaned[, 1700 ])
gene5408.cleaned[,  1701 ] <- as.numeric(gene5408.cleaned[, 1701 ])
gene5408.cleaned[,  1702 ] <- as.numeric(gene5408.cleaned[, 1702 ])
gene5408.cleaned[,  1703 ] <- as.numeric(gene5408.cleaned[, 1703 ])
gene5408.cleaned[,  1704 ] <- as.numeric(gene5408.cleaned[, 1704 ])
gene5408.cleaned[,  1705 ] <- as.numeric(gene5408.cleaned[, 1705 ])
gene5408.cleaned[,  1706 ] <- as.numeric(gene5408.cleaned[, 1706 ])
gene5408.cleaned[,  1707 ] <- as.numeric(gene5408.cleaned[, 1707 ])
gene5408.cleaned[,  1708 ] <- as.numeric(gene5408.cleaned[, 1708 ])
gene5408.cleaned[,  1709 ] <- as.numeric(gene5408.cleaned[, 1709 ])
gene5408.cleaned[,  1710 ] <- as.numeric(gene5408.cleaned[, 1710 ])
gene5408.cleaned[,  1711 ] <- as.numeric(gene5408.cleaned[, 1711 ])
gene5408.cleaned[,  1712 ] <- as.numeric(gene5408.cleaned[, 1712 ])
gene5408.cleaned[,  1713 ] <- as.numeric(gene5408.cleaned[, 1713 ])
gene5408.cleaned[,  1714 ] <- as.numeric(gene5408.cleaned[, 1714 ])
gene5408.cleaned[,  1715 ] <- as.numeric(gene5408.cleaned[, 1715 ])
gene5408.cleaned[,  1716 ] <- as.numeric(gene5408.cleaned[, 1716 ])
gene5408.cleaned[,  1717 ] <- as.numeric(gene5408.cleaned[, 1717 ])
gene5408.cleaned[,  1718 ] <- as.numeric(gene5408.cleaned[, 1718 ])
gene5408.cleaned[,  1719 ] <- as.numeric(gene5408.cleaned[, 1719 ])
gene5408.cleaned[,  1720 ] <- as.numeric(gene5408.cleaned[, 1720 ])
gene5408.cleaned[,  1721 ] <- as.numeric(gene5408.cleaned[, 1721 ])
gene5408.cleaned[,  1722 ] <- as.numeric(gene5408.cleaned[, 1722 ])
gene5408.cleaned[,  1723 ] <- as.numeric(gene5408.cleaned[, 1723 ])
gene5408.cleaned[,  1724 ] <- as.numeric(gene5408.cleaned[, 1724 ])
gene5408.cleaned[,  1725 ] <- as.numeric(gene5408.cleaned[, 1725 ])
gene5408.cleaned[,  1726 ] <- as.numeric(gene5408.cleaned[, 1726 ])
gene5408.cleaned[,  1727 ] <- as.numeric(gene5408.cleaned[, 1727 ])
gene5408.cleaned[,  1728 ] <- as.numeric(gene5408.cleaned[, 1728 ])
gene5408.cleaned[,  1729 ] <- as.numeric(gene5408.cleaned[, 1729 ])
gene5408.cleaned[,  1730 ] <- as.numeric(gene5408.cleaned[, 1730 ])
gene5408.cleaned[,  1731 ] <- as.numeric(gene5408.cleaned[, 1731 ])
gene5408.cleaned[,  1732 ] <- as.numeric(gene5408.cleaned[, 1732 ])
gene5408.cleaned[,  1733 ] <- as.numeric(gene5408.cleaned[, 1733 ])
gene5408.cleaned[,  1734 ] <- as.numeric(gene5408.cleaned[, 1734 ])
gene5408.cleaned[,  1735 ] <- as.numeric(gene5408.cleaned[, 1735 ])
gene5408.cleaned[,  1736 ] <- as.numeric(gene5408.cleaned[, 1736 ])
gene5408.cleaned[,  1737 ] <- as.numeric(gene5408.cleaned[, 1737 ])
gene5408.cleaned[,  1738 ] <- as.numeric(gene5408.cleaned[, 1738 ])
gene5408.cleaned[,  1739 ] <- as.numeric(gene5408.cleaned[, 1739 ])
gene5408.cleaned[,  1740 ] <- as.numeric(gene5408.cleaned[, 1740 ])
gene5408.cleaned[,  1741 ] <- as.numeric(gene5408.cleaned[, 1741 ])
gene5408.cleaned[,  1742 ] <- as.numeric(gene5408.cleaned[, 1742 ])
gene5408.cleaned[,  1743 ] <- as.numeric(gene5408.cleaned[, 1743 ])
gene5408.cleaned[,  1744 ] <- as.numeric(gene5408.cleaned[, 1744 ])
gene5408.cleaned[,  1745 ] <- as.numeric(gene5408.cleaned[, 1745 ])
gene5408.cleaned[,  1746 ] <- as.numeric(gene5408.cleaned[, 1746 ])
gene5408.cleaned[,  1747 ] <- as.numeric(gene5408.cleaned[, 1747 ])
gene5408.cleaned[,  1748 ] <- as.numeric(gene5408.cleaned[, 1748 ])
gene5408.cleaned[,  1749 ] <- as.numeric(gene5408.cleaned[, 1749 ])
gene5408.cleaned[,  1750 ] <- as.numeric(gene5408.cleaned[, 1750 ])
gene5408.cleaned[,  1751 ] <- as.numeric(gene5408.cleaned[, 1751 ])
gene5408.cleaned[,  1752 ] <- as.numeric(gene5408.cleaned[, 1752 ])
gene5408.cleaned[,  1753 ] <- as.numeric(gene5408.cleaned[, 1753 ])
gene5408.cleaned[,  1754 ] <- as.numeric(gene5408.cleaned[, 1754 ])
gene5408.cleaned[,  1755 ] <- as.numeric(gene5408.cleaned[, 1755 ])
gene5408.cleaned[,  1756 ] <- as.numeric(gene5408.cleaned[, 1756 ])
gene5408.cleaned[,  1757 ] <- as.numeric(gene5408.cleaned[, 1757 ])
gene5408.cleaned[,  1758 ] <- as.numeric(gene5408.cleaned[, 1758 ])
gene5408.cleaned[,  1759 ] <- as.numeric(gene5408.cleaned[, 1759 ])
gene5408.cleaned[,  1760 ] <- as.numeric(gene5408.cleaned[, 1760 ])
gene5408.cleaned[,  1761 ] <- as.numeric(gene5408.cleaned[, 1761 ])
gene5408.cleaned[,  1762 ] <- as.numeric(gene5408.cleaned[, 1762 ])
gene5408.cleaned[,  1763 ] <- as.numeric(gene5408.cleaned[, 1763 ])
gene5408.cleaned[,  1764 ] <- as.numeric(gene5408.cleaned[, 1764 ])
gene5408.cleaned[,  1765 ] <- as.numeric(gene5408.cleaned[, 1765 ])
gene5408.cleaned[,  1766 ] <- as.numeric(gene5408.cleaned[, 1766 ])
gene5408.cleaned[,  1767 ] <- as.numeric(gene5408.cleaned[, 1767 ])
gene5408.cleaned[,  1768 ] <- as.numeric(gene5408.cleaned[, 1768 ])
gene5408.cleaned[,  1769 ] <- as.numeric(gene5408.cleaned[, 1769 ])
gene5408.cleaned[,  1770 ] <- as.numeric(gene5408.cleaned[, 1770 ])
gene5408.cleaned[,  1771 ] <- as.numeric(gene5408.cleaned[, 1771 ])
gene5408.cleaned[,  1772 ] <- as.numeric(gene5408.cleaned[, 1772 ])
gene5408.cleaned[,  1773 ] <- as.numeric(gene5408.cleaned[, 1773 ])
gene5408.cleaned[,  1774 ] <- as.numeric(gene5408.cleaned[, 1774 ])
gene5408.cleaned[,  1775 ] <- as.numeric(gene5408.cleaned[, 1775 ])
gene5408.cleaned[,  1776 ] <- as.numeric(gene5408.cleaned[, 1776 ])
gene5408.cleaned[,  1777 ] <- as.numeric(gene5408.cleaned[, 1777 ])
gene5408.cleaned[,  1778 ] <- as.numeric(gene5408.cleaned[, 1778 ])
gene5408.cleaned[,  1779 ] <- as.numeric(gene5408.cleaned[, 1779 ])
gene5408.cleaned[,  1780 ] <- as.numeric(gene5408.cleaned[, 1780 ])
gene5408.cleaned[,  1781 ] <- as.numeric(gene5408.cleaned[, 1781 ])
gene5408.cleaned[,  1782 ] <- as.numeric(gene5408.cleaned[, 1782 ])
gene5408.cleaned[,  1783 ] <- as.numeric(gene5408.cleaned[, 1783 ])
gene5408.cleaned[,  1784 ] <- as.numeric(gene5408.cleaned[, 1784 ])
gene5408.cleaned[,  1785 ] <- as.numeric(gene5408.cleaned[, 1785 ])
gene5408.cleaned[,  1786 ] <- as.numeric(gene5408.cleaned[, 1786 ])
gene5408.cleaned[,  1787 ] <- as.numeric(gene5408.cleaned[, 1787 ])
gene5408.cleaned[,  1788 ] <- as.numeric(gene5408.cleaned[, 1788 ])
gene5408.cleaned[,  1789 ] <- as.numeric(gene5408.cleaned[, 1789 ])
gene5408.cleaned[,  1790 ] <- as.numeric(gene5408.cleaned[, 1790 ])
gene5408.cleaned[,  1791 ] <- as.numeric(gene5408.cleaned[, 1791 ])
gene5408.cleaned[,  1792 ] <- as.numeric(gene5408.cleaned[, 1792 ])
gene5408.cleaned[,  1793 ] <- as.numeric(gene5408.cleaned[, 1793 ])
gene5408.cleaned[,  1794 ] <- as.numeric(gene5408.cleaned[, 1794 ])
gene5408.cleaned[,  1795 ] <- as.numeric(gene5408.cleaned[, 1795 ])
gene5408.cleaned[,  1796 ] <- as.numeric(gene5408.cleaned[, 1796 ])
gene5408.cleaned[, 1797 ] <- as.numeric(gene5408.cleaned[, 1797 ])
gene5408.cleaned[,  1798 ] <- as.numeric(gene5408.cleaned[, 1798 ])
gene5408.cleaned[,  1799 ] <- as.numeric(gene5408.cleaned[, 1799 ])
gene5408.cleaned[,  1800 ] <- as.numeric(gene5408.cleaned[, 1800 ])
gene5408.cleaned[,  1801 ] <- as.numeric(gene5408.cleaned[, 1801 ])
gene5408.cleaned[,  1802 ] <- as.numeric(gene5408.cleaned[, 1802 ])
gene5408.cleaned[,  1803 ] <- as.numeric(gene5408.cleaned[, 1803 ])
gene5408.cleaned[,  1804 ] <- as.numeric(gene5408.cleaned[, 1804 ])
gene5408.cleaned[,  1805 ] <- as.numeric(gene5408.cleaned[, 1805 ])
gene5408.cleaned[,  1806 ] <- as.numeric(gene5408.cleaned[, 1806 ])
gene5408.cleaned[,  1807 ] <- as.numeric(gene5408.cleaned[, 1807 ])
gene5408.cleaned[,  1808 ] <- as.numeric(gene5408.cleaned[, 1808 ])
gene5408.cleaned[,  1809 ] <- as.numeric(gene5408.cleaned[, 1809 ])
gene5408.cleaned[,  1810 ] <- as.numeric(gene5408.cleaned[, 1810 ])
gene5408.cleaned[,  1811 ] <- as.numeric(gene5408.cleaned[, 1811 ])
gene5408.cleaned[,  1812 ] <- as.numeric(gene5408.cleaned[, 1812 ])
gene5408.cleaned[,  1813 ] <- as.numeric(gene5408.cleaned[, 1813 ])
gene5408.cleaned[,  1814 ] <- as.numeric(gene5408.cleaned[, 1814 ])
gene5408.cleaned[,  1815 ] <- as.numeric(gene5408.cleaned[, 1815 ])
gene5408.cleaned[,  1816 ] <- as.numeric(gene5408.cleaned[, 1816 ])
gene5408.cleaned[,  1817 ] <- as.numeric(gene5408.cleaned[, 1817 ])
gene5408.cleaned[,  1818 ] <- as.numeric(gene5408.cleaned[, 1818 ])
gene5408.cleaned[,  1819 ] <- as.numeric(gene5408.cleaned[, 1819 ])
gene5408.cleaned[,  1820 ] <- as.numeric(gene5408.cleaned[, 1820 ])
gene5408.cleaned[,  1821 ] <- as.numeric(gene5408.cleaned[, 1821 ])
gene5408.cleaned[,  1822 ] <- as.numeric(gene5408.cleaned[, 1822 ])
gene5408.cleaned[,  1823 ] <- as.numeric(gene5408.cleaned[, 1823 ])
gene5408.cleaned[,  1824 ] <- as.numeric(gene5408.cleaned[, 1824 ])
gene5408.cleaned[,  1825 ] <- as.numeric(gene5408.cleaned[, 1825 ])
gene5408.cleaned[,  1826 ] <- as.numeric(gene5408.cleaned[, 1826 ])
gene5408.cleaned[,  1827 ] <- as.numeric(gene5408.cleaned[, 1827 ])
gene5408.cleaned[,  1828 ] <- as.numeric(gene5408.cleaned[, 1828 ])
gene5408.cleaned[,  1829 ] <- as.numeric(gene5408.cleaned[, 1829 ])
gene5408.cleaned[,  1830 ] <- as.numeric(gene5408.cleaned[, 1830 ])
gene5408.cleaned[,  1831 ] <- as.numeric(gene5408.cleaned[, 1831 ])
gene5408.cleaned[,  1832 ] <- as.numeric(gene5408.cleaned[, 1832 ])
gene5408.cleaned[,  1833 ] <- as.numeric(gene5408.cleaned[, 1833 ])
gene5408.cleaned[,  1834 ] <- as.numeric(gene5408.cleaned[, 1834 ])
gene5408.cleaned[,  1835 ] <- as.numeric(gene5408.cleaned[, 1835 ])
gene5408.cleaned[,  1836 ] <- as.numeric(gene5408.cleaned[, 1836 ])
gene5408.cleaned[,  1837 ] <- as.numeric(gene5408.cleaned[, 1837 ])
gene5408.cleaned[,  1838 ] <- as.numeric(gene5408.cleaned[, 1838 ])
gene5408.cleaned[,  1839 ] <- as.numeric(gene5408.cleaned[, 1839 ])
gene5408.cleaned[,  1840 ] <- as.numeric(gene5408.cleaned[, 1840 ])
gene5408.cleaned[,  1841 ] <- as.numeric(gene5408.cleaned[, 1841 ])
gene5408.cleaned[,  1842 ] <- as.numeric(gene5408.cleaned[, 1842 ])
gene5408.cleaned[,  1843 ] <- as.numeric(gene5408.cleaned[, 1843 ])
gene5408.cleaned[,  1844 ] <- as.numeric(gene5408.cleaned[, 1844 ])
gene5408.cleaned[,  1845 ] <- as.numeric(gene5408.cleaned[, 1845 ])
gene5408.cleaned[,  1846 ] <- as.numeric(gene5408.cleaned[, 1846 ])
gene5408.cleaned[,  1847 ] <- as.numeric(gene5408.cleaned[, 1847 ])
gene5408.cleaned[,  1848 ] <- as.numeric(gene5408.cleaned[, 1848 ])
gene5408.cleaned[,  1849 ] <- as.numeric(gene5408.cleaned[, 1849 ])
gene5408.cleaned[,  1850 ] <- as.numeric(gene5408.cleaned[, 1850 ])
gene5408.cleaned[,  1851 ] <- as.numeric(gene5408.cleaned[, 1851 ])
gene5408.cleaned[,  1852 ] <- as.numeric(gene5408.cleaned[, 1852 ])
gene5408.cleaned[,  1853 ] <- as.numeric(gene5408.cleaned[, 1853 ])
gene5408.cleaned[,  1854 ] <- as.numeric(gene5408.cleaned[, 1854 ])
gene5408.cleaned[,  1855 ] <- as.numeric(gene5408.cleaned[, 1855 ])
gene5408.cleaned[,  1856 ] <- as.numeric(gene5408.cleaned[, 1856 ])
gene5408.cleaned[,  1857 ] <- as.numeric(gene5408.cleaned[, 1857 ])
gene5408.cleaned[,  1858 ] <- as.numeric(gene5408.cleaned[, 1858 ])
gene5408.cleaned[,  1859 ] <- as.numeric(gene5408.cleaned[, 1859 ])
gene5408.cleaned[,  1860 ] <- as.numeric(gene5408.cleaned[, 1860 ])
gene5408.cleaned[,  1861 ] <- as.numeric(gene5408.cleaned[, 1861 ])
gene5408.cleaned[,  1862 ] <- as.numeric(gene5408.cleaned[, 1862 ])
gene5408.cleaned[,  1863 ] <- as.numeric(gene5408.cleaned[, 1863 ])
gene5408.cleaned[,  1864 ] <- as.numeric(gene5408.cleaned[, 1864 ])
gene5408.cleaned[,  1865 ] <- as.numeric(gene5408.cleaned[, 1865 ])
gene5408.cleaned[,  1866 ] <- as.numeric(gene5408.cleaned[, 1866 ])
gene5408.cleaned[,  1867 ] <- as.numeric(gene5408.cleaned[, 1867 ])
gene5408.cleaned[,  1868 ] <- as.numeric(gene5408.cleaned[, 1868 ])
gene5408.cleaned[,  1869 ] <- as.numeric(gene5408.cleaned[, 1869 ])
gene5408.cleaned[,  1870 ] <- as.numeric(gene5408.cleaned[, 1870 ])
gene5408.cleaned[,  1871 ] <- as.numeric(gene5408.cleaned[, 1871 ])
gene5408.cleaned[,  1872 ] <- as.numeric(gene5408.cleaned[, 1872 ])
gene5408.cleaned[,  1873 ] <- as.numeric(gene5408.cleaned[, 1873 ])
gene5408.cleaned[,  1874 ] <- as.numeric(gene5408.cleaned[, 1874 ])
gene5408.cleaned[,  1875 ] <- as.numeric(gene5408.cleaned[, 1875 ])
gene5408.cleaned[,  1876 ] <- as.numeric(gene5408.cleaned[, 1876 ])
gene5408.cleaned[,  1877 ] <- as.numeric(gene5408.cleaned[, 1877 ])
gene5408.cleaned[,  1878 ] <- as.numeric(gene5408.cleaned[, 1878 ])
gene5408.cleaned[,  1879 ] <- as.numeric(gene5408.cleaned[, 1879 ])
gene5408.cleaned[,  1880 ] <- as.numeric(gene5408.cleaned[, 1880 ])
gene5408.cleaned[,  1881 ] <- as.numeric(gene5408.cleaned[, 1881 ])
gene5408.cleaned[,  1882 ] <- as.numeric(gene5408.cleaned[, 1882 ])
gene5408.cleaned[,  1883 ] <- as.numeric(gene5408.cleaned[, 1883 ])
gene5408.cleaned[,  1884 ] <- as.numeric(gene5408.cleaned[, 1884 ])
gene5408.cleaned[,  1885 ] <- as.numeric(gene5408.cleaned[, 1885 ])
gene5408.cleaned[,  1886 ] <- as.numeric(gene5408.cleaned[, 1886 ])
gene5408.cleaned[,  1887 ] <- as.numeric(gene5408.cleaned[, 1887 ])
gene5408.cleaned[,  1888 ] <- as.numeric(gene5408.cleaned[, 1888 ])
gene5408.cleaned[,  1889 ] <- as.numeric(gene5408.cleaned[, 1889 ])
gene5408.cleaned[,  1890 ] <- as.numeric(gene5408.cleaned[, 1890 ])
gene5408.cleaned[,  1891 ] <- as.numeric(gene5408.cleaned[, 1891 ])
gene5408.cleaned[,  1892 ] <- as.numeric(gene5408.cleaned[, 1892 ])
gene5408.cleaned[,  1893 ] <- as.numeric(gene5408.cleaned[, 1893 ])
gene5408.cleaned[,  1894 ] <- as.numeric(gene5408.cleaned[, 1894 ])
gene5408.cleaned[,  1895 ] <- as.numeric(gene5408.cleaned[, 1895 ])
gene5408.cleaned[,  1896 ] <- as.numeric(gene5408.cleaned[, 1896 ])
gene5408.cleaned[,  1897 ] <- as.numeric(gene5408.cleaned[, 1897 ])
gene5408.cleaned[,  1898 ] <- as.numeric(gene5408.cleaned[, 1898 ])
gene5408.cleaned[,  1899 ] <- as.numeric(gene5408.cleaned[, 1899 ])
gene5408.cleaned[,  1900 ] <- as.numeric(gene5408.cleaned[, 1900 ])
gene5408.cleaned[,  1901 ] <- as.numeric(gene5408.cleaned[, 1901 ])
gene5408.cleaned[,  1902 ] <- as.numeric(gene5408.cleaned[, 1902 ])
gene5408.cleaned[,  1903 ] <- as.numeric(gene5408.cleaned[, 1903 ])
gene5408.cleaned[,  1904 ] <- as.numeric(gene5408.cleaned[, 1904 ])
gene5408.cleaned[,  1905 ] <- as.numeric(gene5408.cleaned[, 1905 ])
gene5408.cleaned[,  1906 ] <- as.numeric(gene5408.cleaned[, 1906 ])
gene5408.cleaned[,  1907 ] <- as.numeric(gene5408.cleaned[, 1907 ])
gene5408.cleaned[,  1908 ] <- as.numeric(gene5408.cleaned[, 1908 ])
gene5408.cleaned[,  1909 ] <- as.numeric(gene5408.cleaned[, 1909 ])
gene5408.cleaned[,  1910 ] <- as.numeric(gene5408.cleaned[, 1910 ])
gene5408.cleaned[,  1911 ] <- as.numeric(gene5408.cleaned[, 1911 ])
gene5408.cleaned[,  1912 ] <- as.numeric(gene5408.cleaned[, 1912 ])
gene5408.cleaned[,  1913 ] <- as.numeric(gene5408.cleaned[, 1913 ])
gene5408.cleaned[,  1914 ] <- as.numeric(gene5408.cleaned[, 1914 ])
gene5408.cleaned[,  1915 ] <- as.numeric(gene5408.cleaned[, 1915 ])
gene5408.cleaned[,  1916 ] <- as.numeric(gene5408.cleaned[, 1916 ])
gene5408.cleaned[,  1917 ] <- as.numeric(gene5408.cleaned[, 1917 ])
gene5408.cleaned[,  1918 ] <- as.numeric(gene5408.cleaned[, 1918 ])
gene5408.cleaned[,  1919 ] <- as.numeric(gene5408.cleaned[, 1919 ])
gene5408.cleaned[,  1920 ] <- as.numeric(gene5408.cleaned[, 1920 ])
gene5408.cleaned[,  1921 ] <- as.numeric(gene5408.cleaned[, 1921 ])
gene5408.cleaned[,  1922 ] <- as.numeric(gene5408.cleaned[, 1922 ])
gene5408.cleaned[,  1923 ] <- as.numeric(gene5408.cleaned[, 1923 ])
gene5408.cleaned[,  1924 ] <- as.numeric(gene5408.cleaned[, 1924 ])
gene5408.cleaned[,  1925 ] <- as.numeric(gene5408.cleaned[, 1925 ])
gene5408.cleaned[,  1926 ] <- as.numeric(gene5408.cleaned[, 1926 ])
gene5408.cleaned[,  1927 ] <- as.numeric(gene5408.cleaned[, 1927 ])
gene5408.cleaned[,  1928 ] <- as.numeric(gene5408.cleaned[, 1928 ])
gene5408.cleaned[,  1929 ] <- as.numeric(gene5408.cleaned[, 1929 ])
gene5408.cleaned[,  1930 ] <- as.numeric(gene5408.cleaned[, 1930 ])
gene5408.cleaned[,  1931 ] <- as.numeric(gene5408.cleaned[, 1931 ])
gene5408.cleaned[,  1932 ] <- as.numeric(gene5408.cleaned[, 1932 ])
gene5408.cleaned[,  1933 ] <- as.numeric(gene5408.cleaned[, 1933 ])
gene5408.cleaned[,  1934 ] <- as.numeric(gene5408.cleaned[, 1934 ])
gene5408.cleaned[,  1935 ] <- as.numeric(gene5408.cleaned[, 1935 ])
gene5408.cleaned[,  1936 ] <- as.numeric(gene5408.cleaned[, 1936 ])
gene5408.cleaned[,  1937 ] <- as.numeric(gene5408.cleaned[, 1937 ])
gene5408.cleaned[,  1938 ] <- as.numeric(gene5408.cleaned[, 1938 ])
gene5408.cleaned[,  1939 ] <- as.numeric(gene5408.cleaned[, 1939 ])
gene5408.cleaned[,  1940 ] <- as.numeric(gene5408.cleaned[, 1940 ])
gene5408.cleaned[,  1941 ] <- as.numeric(gene5408.cleaned[, 1941 ])
gene5408.cleaned[,  1942 ] <- as.numeric(gene5408.cleaned[, 1942 ])
gene5408.cleaned[,  1943 ] <- as.numeric(gene5408.cleaned[, 1943 ])
gene5408.cleaned[,  1944 ] <- as.numeric(gene5408.cleaned[, 1944 ])
gene5408.cleaned[,  1945 ] <- as.numeric(gene5408.cleaned[, 1945 ])
gene5408.cleaned[,  1946 ] <- as.numeric(gene5408.cleaned[, 1946 ])
gene5408.cleaned[,  1947 ] <- as.numeric(gene5408.cleaned[, 1947 ])
gene5408.cleaned[,  1948 ] <- as.numeric(gene5408.cleaned[, 1948 ])
gene5408.cleaned[,  1949 ] <- as.numeric(gene5408.cleaned[, 1949 ])
gene5408.cleaned[,  1950 ] <- as.numeric(gene5408.cleaned[, 1950 ])
gene5408.cleaned[,  1951 ] <- as.numeric(gene5408.cleaned[, 1951 ])
gene5408.cleaned[,  1952 ] <- as.numeric(gene5408.cleaned[, 1952 ])
gene5408.cleaned[,  1953 ] <- as.numeric(gene5408.cleaned[, 1953 ])
gene5408.cleaned[,  1954 ] <- as.numeric(gene5408.cleaned[, 1954 ])
gene5408.cleaned[,  1955 ] <- as.numeric(gene5408.cleaned[, 1955 ])
gene5408.cleaned[,  1956 ] <- as.numeric(gene5408.cleaned[, 1956 ])
gene5408.cleaned[,  1957 ] <- as.numeric(gene5408.cleaned[, 1957 ])
gene5408.cleaned[,  1958 ] <- as.numeric(gene5408.cleaned[, 1958 ])
gene5408.cleaned[,  1959 ] <- as.numeric(gene5408.cleaned[, 1959 ])
gene5408.cleaned[,  1960 ] <- as.numeric(gene5408.cleaned[, 1960 ])
gene5408.cleaned[,  1961 ] <- as.numeric(gene5408.cleaned[, 1961 ])
gene5408.cleaned[,  1962 ] <- as.numeric(gene5408.cleaned[, 1962 ])
gene5408.cleaned[,  1963 ] <- as.numeric(gene5408.cleaned[, 1963 ])
gene5408.cleaned[,  1964 ] <- as.numeric(gene5408.cleaned[, 1964 ])
gene5408.cleaned[,  1965 ] <- as.numeric(gene5408.cleaned[, 1965 ])
gene5408.cleaned[,  1966 ] <- as.numeric(gene5408.cleaned[, 1966 ])
gene5408.cleaned[,  1967 ] <- as.numeric(gene5408.cleaned[, 1967 ])
gene5408.cleaned[,  1968 ] <- as.numeric(gene5408.cleaned[, 1968 ])
gene5408.cleaned[,  1969 ] <- as.numeric(gene5408.cleaned[, 1969 ])
gene5408.cleaned[,  1970 ] <- as.numeric(gene5408.cleaned[, 1970 ])
gene5408.cleaned[,  1971 ] <- as.numeric(gene5408.cleaned[, 1971 ])
gene5408.cleaned[,  1972 ] <- as.numeric(gene5408.cleaned[, 1972 ])
gene5408.cleaned[,  1973 ] <- as.numeric(gene5408.cleaned[, 1973 ])
gene5408.cleaned[,  1974 ] <- as.numeric(gene5408.cleaned[, 1974 ])
gene5408.cleaned[,  1975 ] <- as.numeric(gene5408.cleaned[, 1975 ])
gene5408.cleaned[,  1976 ] <- as.numeric(gene5408.cleaned[, 1976 ])
gene5408.cleaned[,  1977 ] <- as.numeric(gene5408.cleaned[, 1977 ])
gene5408.cleaned[,  1978 ] <- as.numeric(gene5408.cleaned[, 1978 ])
gene5408.cleaned[,  1979 ] <- as.numeric(gene5408.cleaned[, 1979 ])
gene5408.cleaned[,  1980 ] <- as.numeric(gene5408.cleaned[, 1980 ])
gene5408.cleaned[,  1981 ] <- as.numeric(gene5408.cleaned[, 1981 ])
gene5408.cleaned[,  1982 ] <- as.numeric(gene5408.cleaned[, 1982 ])
gene5408.cleaned[,  1983 ] <- as.numeric(gene5408.cleaned[, 1983 ])
gene5408.cleaned[,  1984 ] <- as.numeric(gene5408.cleaned[, 1984 ])
gene5408.cleaned[,  1985 ] <- as.numeric(gene5408.cleaned[, 1985 ])
gene5408.cleaned[,  1986 ] <- as.numeric(gene5408.cleaned[, 1986 ])
gene5408.cleaned[,  1987 ] <- as.numeric(gene5408.cleaned[, 1987 ])
gene5408.cleaned[,  1988 ] <- as.numeric(gene5408.cleaned[, 1988 ])
gene5408.cleaned[,  1989 ] <- as.numeric(gene5408.cleaned[, 1989 ])
gene5408.cleaned[,  1990 ] <- as.numeric(gene5408.cleaned[, 1990 ])
gene5408.cleaned[,  1991 ] <- as.numeric(gene5408.cleaned[, 1991 ])
gene5408.cleaned[,  1992 ] <- as.numeric(gene5408.cleaned[, 1992 ])
gene5408.cleaned[,  1993 ] <- as.numeric(gene5408.cleaned[, 1993 ])
gene5408.cleaned[,  1994 ] <- as.numeric(gene5408.cleaned[, 1994 ])
gene5408.cleaned[,  1995 ] <- as.numeric(gene5408.cleaned[, 1995 ])
gene5408.cleaned[,  1996 ] <- as.numeric(gene5408.cleaned[, 1996 ])
gene5408.cleaned[,  1997 ] <- as.numeric(gene5408.cleaned[, 1997 ])
gene5408.cleaned[,  1998 ] <- as.numeric(gene5408.cleaned[, 1998 ])
gene5408.cleaned[,  1999 ] <- as.numeric(gene5408.cleaned[, 1999 ])
gene5408.cleaned[,  2000 ] <- as.numeric(gene5408.cleaned[, 2000 ])
gene5408.cleaned[,  2001 ] <- as.numeric(gene5408.cleaned[, 2001 ])

```


TRAINING/TESTING SPLIT (2000 Features)

```{r}
#split into testing and training

o <- sample(dim(gene5408.cleaned)[1],8000)
gene5408_train <- gene5408.cleaned[o,]
test_trial <- gene5408.cleaned[-o,]
```

LINEAR DISCRIMINANT ANALYSIS (2000 Features)

```{r}
#Linear discriminant analysis

lda1 <- gene_noquest[1:10,1]


```

K-NEAREST NEIGHBORS (2000 Features)

```{r}
#K-nearest neighbors

lda1 <- gene_noquest[1:10,1]

```

PRINCIPAL COMPONENT ANALYSIS (2000 Features)

```{r}
#Principal component analysis

lda1 <- gene_noquest[1:10,1]


```

TOP 10 GENES (2000 Features)

```{r}
#Top 10 genes

lda1 <- gene_noquest[1:10,1]

```

LDA AND KNN WITH TOP 10 GENES (2000 Features)

POST-PCA DIMENSIONALITY REDUCTION

```{r}
#Post-PCA dimensionality reduction

lda1 <- gene_noquest[1:10,1]
```


